### 2019-08-22 docs/detailed-example.Rmd
Updtes to doco and add getFilterValues function

---
title: "AIMS DataPlatform R Client Notebook Example"
output: html_notebook
---

This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index) to see what that means.

Similar to our previous example we want to run a plot on a series, lets discover a series to plot.

```{r}
library(aimsdataplatform)
getFilterValues('10.25845/5c09bf93f315d', 'series')
```

The benefits to choosing a data series is that it comes from one location and parameter type, making the data easy to plot.  If we did not choose a data series from the *AIMS Weather* data set we might have to specify additional parameters to ensure the data is as expected.

After deciding on a series we plug the series id into a `getAllData` function:

```{r}
results <- getAllData('10.25845/5c09bf93f315d', filters=list('series'=4067, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
```

Now the results have been stored in the `results` we can attempt to plot.

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value)
```

Ok we have a plot, fairly unpleasant looking, that should be a line chart.

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l')
```

Lets add some proper labels:

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature")
```

Finally lets make the colour green and add a main title.

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Yongala NRS Buoy Air Temperature", col='green')
```

And add another series:

```{r}
results2 <- getData(aimsWeather, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
```

Now a legend to distinguish data sets

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
legend("bottomright", c("Yongala NRS Buoy", "Bramble Cay"), fill=c("green", "blue"))
```

Finally citations can be added to our document with the following code:

```{r}
results$citation
results2$citation
```

Bibliography
------------

1. `r results$citation`

2. `r results2$citation`

### 2019-08-22 R/aimsdataplatform.R

@@ -12,7 +12,7 @@ aimsTemperatureLoggers <- "10.25845/5b4eb0f9bb848"
 # Get some data and return a data frame
 getData <- function(doi, filters=NULL, baseEndPoint=defaultBaseEndPoint, apiKey=NULL) {
   endPoint <- paste(baseEndPoint, doi, "data", sep="/")
-  dataRequest <- GET(endPoint, add_headers("X-Api-Key"=getApiKey(apiKey)), query=filters)
+  dataRequest <- GET(endPoint, add_headers("X-Api-Key"=findApiKey(apiKey)), query=filters)
   if (http_error(dataRequest)) {
     warning(paste("Error", http_status(dataRequest), content(dataRequest)))
   } else {
@@ -29,7 +29,7 @@ getNextData <- function(url, apiKey=NULL) {
   parsed_url <- parse_url(url)
   # Unfortunately need to remove plus sign if not decoded properly
   parsed_url$query$cursor <- gsub("\\+", " ", parsed_url$query$cursor)
-  dataRequest <- GET(parsed_url, add_headers("X-Api-Key"=getApiKey(apiKey)))
+  dataRequest <- GET(parsed_url, add_headers("X-Api-Key"=findApiKey(apiKey)))
   if (http_error(dataRequest)) {
     warning(paste("Error", http_status(dataRequest), content(dataRequest)))
   } else {
@@ -69,6 +69,18 @@ getAllData <- function(doi, filters=NULL, baseEndPoint=defaultBaseEndPoint, apiK
   return(results)
 }
 
+getFilterValues <- function(doi, filterName, baseEndPoint = defaultBaseEndPoint) {
+  endPoint <- paste(baseEndPoint, doi, filterName, sep="/")
+  dataRequest <- GET(endPoint)
+  if (http_error(dataRequest)) {
+    warning(paste("Error", http_status(dataRequest), content(dataRequest)))
+  } else {
+    jsonResponse <- content(dataRequest, "text", encoding = "UTF-8")
+    results <- fromJSON(jsonResponse, simplifyDataFrame = TRUE)
+    return(results)
+  }
+}
+
 updateFormat <- function(results) {
   if ("links" %in% names(results) && "next" %in% names(results$links)) {
     results$links$nextPage <- results$links$'next'
@@ -79,7 +91,7 @@ updateFormat <- function(results) {
   return(results)
 }
 
[…]

### 2019-08-22 docs/detailed-example.Rmd
Update docs
Update links

@@
 ---
+[Back](index)
 
-This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index) to see what that means.
+This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.
 
 Similar to our previous example we want to run a plot on a series, lets discover a series to plot.
+If you are running this notebook in [R Studio](https://www.rstudio.com/) you can click on the green arrow inside each code block to run it.
 

### 2019-08-26 docs/detailed-example.Rmd
Updates to examples

@@
 
-This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.
+This example assumes you have obtained an *AIMS DataPlatform API Key*.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.
 
@@
 If we did not choose a data series from the *AIMS Weather* data set we might have to specify additional parameters to ensure the data is as expected.
+__Please note that in all code smaples below you should enter your own API Key in the field that says `my-api-key`.__
 
@@
 ```{r}
-results <- getAllData('10.25845/5c09bf93f315d', filters=list('series'=4067, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
+results <- getAllData('10.25845/5c09bf93f315d', apiKey='my-api-key', filters=list('series'=4067, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
 ```
@@
 ```{r}
-results2 <- getData(aimsWeather, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
+results2 <- getAllData('10.25845/5c09bf93f315d', apiKey='my-api-key', filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
 plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')

### 2019-08-26 docs/detailed-example.Rmd
Update detailed example

--- 2019-08-22 docs/detailed-example.Rmd
@@
 ---
+
 [Back](index)
 
-This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.
+This example assumes you have obtained an *AIMS DataPlatform API Key*.
+See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.
+To download and run this example interactively in *R Studio* click on `Code -> Download Rmd` in the top right corner of this document.
 
@@
 If we did not choose a data series from the *AIMS Weather* data set we might have to specify additional parameters to ensure the data is as expected.
+__Please note that in all code smaples below you should enter your own API Key in the field that says `api-key-for-r-notebook`.__
 
@@
 ```{r}
-results <- getAllData('10.25845/5c09bf93f315d', filters=list('series'=4067, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
+results <- getAllData('10.25845/5c09bf93f315d', apiKey='api-key-for-r-notebook', filters=list('series'=4067, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
 ```
@@
 ```{r}
-results2 <- getData(aimsWeather, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
+results2 <- getAllData('10.25845/5c09bf93f315d', apiKey='api-key-for-r-notebook', filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
 plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')

### 2019-09-03 docs/detailed-example.Rmd
Update notebook

--- 2019-08-22 docs/detailed-example.Rmd
@@
 ---
-title: "AIMS DataPlatform R Client Notebook Example"
+title: "AIMS Data Platform R Client Notebook Example"
 output: html_notebook
 ---
+
 [Back](index)
 
-This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.
+This example assumes you have obtained an *AIMS Data Platform API Key*.
+See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.
+To download and run this example interactively in *R Studio* click on `Code -> Download Rmd` in the top right corner of this document.
 
-Similar to our previous example we want to run a plot on a series, lets discover a series to plot.
-If you are running this notebook in [R Studio](https://www.rstudio.com/) you can click on the green arrow inside each code block to run it.
+Once you have obtained your API Key past it in the following code chunk and it will be used throughout this tutorial:
 
 ```{r}
+#       ==> paste your key here
+MY_API_KEY <- "api-key-for-r-notebook"
+
+```
+
+Install R Client
+----------------
+
+*AIMS Data Platform R Client* can be installed directly from [github](https://github.com/aims/data-platform-r) using the following code:
+
+```{r}
+
+install.packages("devtools")
+devtools::install_git("https://github.com/AIMS/data-platform-r")
 library(aimsdataplatform)
+
+```
+
+Discover a dataset
+------------------
+
+Suppose we want to query a data series and plot it then the procedure might be:
+1. Examine documentation and establish query filters
+2. Perform data download using `getData`
+3. Use R `plot` to create a chart
+
+We decide to query the [AIMS Weather](https://aims.github.io/data-platform/weather) data set based on a data series, then we are guaranteed of getting information from one site for one metric.
+
+To discover a data set we look up the filter values available for a series:
+
+```{r}
 getFilterValues('10.25845/5c09bf93f315d', 'series')
@@
 
-After deciding on a series we plug the series id into a `getAllData` function:
+Finally our filters might look like the following:
+
+Variable  | Value                  | Description
+----------|------------------------|-------------------------------------------------------
+dio       | 10.25845/5c09bf93f315d | DOI for AIMS Weather found [here](https://aims.github.io/data-platform)
+series    | 64                     | Found [here](https://aims.github.io/data-platform/weather/series), Davies Reef Air Temperature data series
+from-date | '2018-01-01'           | We want to start charting on 1/1/2018
+thru-date | '2018-01-10'           | We are plotting 10 days of data
+
+Query and Plot Dataset
+----------------------
+
+After deciding on query parameters we plug the series id into a `getData` function:
 
 ```{r}
-results <- getAllData('10.25845/5c09bf93f315d', filters=list('series'=4067, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
+results <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=64, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
 ```
@@
 plot(results$dataFrame$time, results$dataFrame$qc_value)
+#axis(1, results$dataFrame$time, format(results$dataFrame$time, "%b %d"), las=2)
 ```
 
-Ok we have a plot, fairly unpleasant looking, that should be a line chart.
+Ok we have a plot, fairly unpleasant looking, that should be a line chart, also we should fix the time labels by putting the X values into an axis command:
 
@@
 plot(results$dataFrame$time, results$dataFrame$qc_value, type='l')
+
 ```
@@
 ```{r}
-plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature")
+plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature")
 ```
@@
 ```{r}
-plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Yongala NRS Buoy Air Temperature", col='green')
+plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Davies Reef Platform Air Temperature in 2018", col='green')
 ```
@@
 ```{r}
-results2 <- getData(aimsWeather, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
-plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
+results2 <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
+plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
 lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
@@
 ```{r}
-plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
+plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
 lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
-legend("bottomright", c("Yongala NRS Buoy", "Bramble Cay"), fill=c("green", "blue"))
+legend("bottomright", c("Davies Reef", "Bramble Cay"), fill=c("green", "blue"))
 ```

### 2019-09-03 docs/detailed-example.Rmd
Tidy up

@@
 ```{r}
-#       ==> paste your key here
+# paste your key where it says api-key-for-r-notebook
 MY_API_KEY <- "api-key-for-r-notebook"
@@
 ```{r}
-
 install.packages("devtools")
@@
 results <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=64, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
+
 ```
@@
 plot(results$dataFrame$time, results$dataFrame$qc_value)
-#axis(1, results$dataFrame$time, format(results$dataFrame$time, "%b %d"), las=2)
+
 ```
@@
 plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature")
+
 ```
@@
 plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Davies Reef Platform Air Temperature in 2018", col='green')
+
 ```
@@
 lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
+
 ```
@@
 legend("bottomright", c("Davies Reef", "Bramble Cay"), fill=c("green", "blue"))
+
 ```
@@
 results2$citation
+
 ```

### 2019-09-03 docs/detailed-example.Rmd
Fix typo

@@
 ----------|------------------------|-------------------------------------------------------
-dio       | 10.25845/5c09bf93f315d | DOI for AIMS Weather found [here](https://aims.github.io/data-platform)
+doi       | 10.25845/5c09bf93f315d | DOI for AIMS Weather found [here](https://aims.github.io/data-platform)
 series    | 64                     | Found [here](https://aims.github.io/data-platform/weather/series), Davies Reef Air Temperature data series

### 2019-11-07 docs/10.25845/5c09bf93f315d/example-1.Rmd
Updates

--- 2019-09-03 docs/detailed-example.Rmd
@@
 Suppose we want to query a data series and plot it then the procedure might be:
+
 1. Examine documentation and establish query filters
@@
 
-Finally our filters might look like the following:
+Finally our values and filters might look like the following:
 
@@
 
-Now the results have been stored in the `results` we can attempt to plot.
+Now the results have been stored in the `results` object we can attempt to plot.
 
@@
 
-Ok we have a plot, fairly unpleasant looking, that should be a line chart, also we should fix the time labels by putting the X values into an axis command:
+Ok we have a plot, fairly unpleasant looking, that should be a line chart:
 
@@
 ```{r}
-plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature")
+plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Date", ylab="Air Temperature")
 
@@
 ```{r}
-plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Davies Reef Platform Air Temperature in 2018", col='green')
+plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Date", ylab="Air Temperature", main="Davies Reef Platform Air Temperature", col='green')
 
@@
 results2 <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
-plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
+plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Date", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
 lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
@@
 ```{r}
-plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
+plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Date", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
 lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")

### 2019-11-07 docs/10.25845/5c09bf93f315d/example-1.Rmd
Updates

@@
 
-This example assumes you have obtained an *AIMS Data Platform API Key*.
-See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.
+This example assumes you have obtained an [AIMS Data Platform API Key](https://aims.github.io/data-platform/key-request).
+Further details about key usage can be found [here](https://aims.github.io/data-platform-r/index#usage-of-aims-dataplatform-api-key)
+
 To download and run this example interactively in *R Studio* click on `Code -> Download Rmd` in the top right corner of this document.

### 2020-05-01 README.Rmd
added package logo to README

---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/figures/",
  dev = "png",
  dpi = 150,
  fig.asp = 0.8,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center"
)
```

<img src="inst/figures/logo.png" width = 120 alt="dataaimsr Logo"/>

AIMS Data Platform R Client
==========================

__AIMS Data Platform R Client__ will provide easy access to data sets for R applications to the [AIMS Data Platform API](https://aims.github.io/data-platform).

Usage of AIMS Data Platform API Key
----------------------------------

__AIMS Data Platform__ requires an API Key for requests, [get a key here.](https://aims.github.io/data-platform/key-request)

The API Key can be passed to each function as an additional `apiKey='XXXX'` argument, however it is preferred that API Keys are not stored in code.

If the environment variable `AIMS_DATA_PLATFORM_API_KEY` is stored in the user's `.Renviron` file then that will be loaded and used automatically.  In that case the users `.Renviron` file might look like:

```
AIMS_DATAPLATFORM_API_KEY=XXXXXXXXXXXXX

```
The `.Renviron` file is usually stored in each users home directory.

### Possible .Renviron file locations

System     | .Renviron file locations
-----------|-------------------------
MS Windows | `C:\Users\<username>\.Renviron`  or `C:\Users\<username>\Documents\.Renviron`
Linux      | `/home/<username>/.Renviron`

Installation
------------

At this stage __AIMS Data Platform R Client__ is not hosted on CRAN R package network.
An alternative method of installation is to use the R `devtools` package.

R `devtools` can be installed using the following command:

```
install.packages("devtools")
```

After `devtools` has been installed the __AIMS Data Platform R Client__ can be installed directly
from GitHub using the following command:

```
devtools::install_git("https://github.com/AIMS/data-platform-r")
```

This command will also install 2 dependencies `httr` and `jsonlite`.

Available Data Sets
-------------------

The __AIMS Data Platform API__ is a *REST API* providing *JSON* formatted data.  Documentation about available data sets can be found on the [AIMS Data Platfom API](https://aims.github.io/data-platform).

Detailed Example
----------------

[A more detailed example of the R package usage on the weather dataset page.](10.25845/5c09bf93f315d/example-1.nb.html)  This is an [R Studio](https://www.rstudio.com/) Notebook and can be used interactively from *R Studio*.  __Note that you need to have an AIMS Data Platform API Key available to run this detailed example.__

Further information about the __AIMS DataPlatform R Client__ and __AIMS DataPlatform API__ can be seen on the [project page](https://aims.github.io/data-platform-r).

This library is provided for use under the Creative Commons by Attribution license ([CC BY 3.0](https://creativecommons.org/licenses/by/3.0/au/legalcode)) by the AIMS Datacentre for the [Austrailian Institute of Marine Science](https://www.aims.gov.au)

### 2020-05-01 R/aimsdataplatform.R
changed package name

@@ -88,7 +88,7 @@ request_process <- function(dt_req, next_page = FALSE) {
 #' 
 #' @importFrom httr GET add_headers
 page_data_get <- function(doi, filters = NULL, api_key = NULL) {
-  base_end_pt <- getOption("aimsdataplatform.base_end_point")
+  base_end_pt <- getOption("dataaimsr.base_end_point")
   end_pt <- paste(base_end_pt, doi, "data", sep = "/")
   dt_req <- GET(end_pt,
                 add_headers("X-Api-Key" = api_key_find(api_key)),
@@ -141,10 +141,10 @@ next_page_data_get <- function(url, api_key = NULL) {
 #' 
 #' @examples
 #' \dontrun{
-#' library(aimsdataplatform)
+#' library(dataaimsr)
 #' # assumes that user already has API key saved to
 #' # .Renviron
-#' weather  <-  getOption("aimsdataplatform.weather")
+#' weather  <-  getOption("dataaimsr.weather")
 #' results <- aims_data_get(weather,
 #'                     api_key = NULL,
 #'                     filters = list('series' = 64,
@@ -194,15 +194,15 @@ aims_data_get <- function(doi, filters = NULL, ...) {
 #' 
 #' @examples
 #' \dontrun{
-#' library(aimsdataplatform)
-#' weather  <-  getOption("aimsdataplatform.weather")
+#' library(dataaimsr)
+#' weather  <-  getOption("dataaimsr.weather")
 #' filter_values_get(weather, filter_name = "series")
 #' }
 #' 
 #' @export
 #' @importFrom httr GET http_error
 filter_values_get <- function(doi, filter_name) {
-  base_end_pt <- getOption("aimsdataplatform.base_end_point")
+  base_end_pt <- getOption("dataaimsr.base_end_point")
   end_pt <- paste(base_end_pt, doi, filter_name, sep = "/")
   dt_req <- GET(end_pt)
   if (http_error(dt_req)) {
@@ -231,7 +231,7 @@ format_update <- function(results) {
     results$links$next_page <- results$links$"next"
     results$links$"next" <- NULL
   }
-  date_format <- getOption("aimsdataplatform.date_format")
+  date_format <- getOption("dataaimsr.date_format")
   results$results$time <- as.POSIXct(strptime(results$results$time,
                                               format = date_format,
                                               tz = "UTC"))

### 2020-05-01 R/zzz.R

@@ -1,10 +1,10 @@
 .onLoad  <-  function(libname, pkgname) {
   op  <-  options()
   aims_op  <-  list(
-    aimsdataplatform.base_end_point = "https://api.aims.gov.au/data/v1.0",
-    aimsdataplatform.date_format = "%Y-%m-%dT%H:%M:%OS",
-    aimsdataplatform.weather = "10.25845/5c09bf93f315d",
-    aimsdataplatform.temp_loggers = "10.25845/5b4eb0f9bb848"
+    dataaimsr.base_end_point = "https://api.aims.gov.au/data/v1.0",
+    dataaimsr.date_format = "%Y-%m-%dT%H:%M:%OS",
+    dataaimsr.weather = "10.25845/5c09bf93f315d",
+    dataaimsr.temp_loggers = "10.25845/5b4eb0f9bb848"
   )
   toset <- !(names(aims_op) %in% names(op))
   if (any(toset)) {

### 2020-05-01 README.Rmd
increased logo size
typos

@@
 
-<img src="inst/figures/logo.png" width = 120 alt="dataaimsr Logo"/>
+<img src="inst/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
 
@@
 
-The API Key can be passed to each function as an additional `apiKey='XXXX'` argument, however it is preferred that API Keys are not stored in code.
+The API Key can be passed to the package functions as an additional `api_key = 'XXXX'` argument, however it is preferred that API Keys are not stored in code.
 
@@
 
-[A more detailed example of the R package usage on the weather dataset page.](10.25845/5c09bf93f315d/example-1.nb.html)  This is an [R Studio](https://www.rstudio.com/) Notebook and can be used interactively from *R Studio*.
+[A more detailed example of the R package usage on the weather dataset page.](10.25845/5c09bf93f315d/example-1.nb.html)  This is an [RStudio](https://www.rstudio.com/) Notebook and can be used interactively from [RStudio](https://www.rstudio.com/).
 __Note that you need to have an AIMS Data Platform API Key available to run this detailed example.__

### 2020-05-07 R/dataaimsr.R
lots of fixes to functions, and massive improvement on documentation

@@ -1,31 +1,39 @@
-#' Title here
+#' \code{\link[httr]{GET}} error handler
 #' 
-#' General description here
+#' Displays error status
 #' 
-#' @param dt_req Description of parameter
+#' @param dt_req An URL \code{\link[httr]{GET}} output
 #' 
-#' @details Details about this function.
+#' @details This function retrieves the 
+#' status and content of \code{dt_req} via the 
+#' \pkg{httr} package.
 #' 
-#' @return A warning message which retrieves the \pkg{httr}
-#'   status and content from \code{dt_req}.
+#' @return A \code{\link[base]{character}} vector conveying the error message.
 #' 
 #' @author AIMS Datacentre \email{adc@aims.gov.au}
 #' 
 #' @importFrom httr http_status content
-request_warning <- function(dt_req) {
-  warning(paste("Error", http_status(dt_req),
+error_handle <- function(dt_req) {
+  stop(paste("Error", http_status(dt_req),
                 content(dt_req)))
 }
 
-#' Title here
+#' \code{\link[jsonlite]{fromJSON}} data request
 #' 
-#' General description here
+#' Wrapper function
 #' 
-#' @inheritParams request_warning
+#' @inheritParams error_handle
 #' 
-#' @details Details about this function.
+#' @details This function submits a \code{dt_req} 
+#' data request via \code{\link[jsonlite]{fromJSON}}.
 #' 
-#' @return A \code{\link[jsonlite]{fromJSON}} simplified \code{data.frame}.
+#' @return A \code{\link[jsonlite]{fromJSON}} \code{\link[base]{list}} 
+#' containing four elements: 
+#' \code{metadata}: a \href{https://www.doi.org/}{DOI} link
+#' containing the metadata record for the data series; 
+#' \code{citation}: the citation information for the particular dataset; 
+#' \code{links}: the link from which the data query was retrieved;
+#' \code{data}: an output \code{\link[base]{data.frame}}.
 #' 
 #' @author AIMS Datacentre \email{adc@aims.gov.au}
 #' 
@@ -36,53 +44,104 @@ json_results  <-  function(dt_req) {
     fromJSON(json_resp, simplifyDataFrame = TRUE)
 }
 
-#' Title here
+#' Format \code{\link{json_results}} output
 #' 
-#' General description here
+#' Wrapper function
 #' 
-#' @inheritParams request_warning
+#' @inheritParams error_handle
 #' 
-#' @param next_page Description of parameter
[…]

### 2020-05-07 R/zzz.R

@@ -2,9 +2,10 @@
   op  <-  options()
   aims_op  <-  list(
     dataaimsr.base_end_point = "https://api.aims.gov.au/data/v1.0",
-    dataaimsr.date_format = "%Y-%m-%dT%H:%M:%OS",
     dataaimsr.weather = "10.25845/5c09bf93f315d",
-    dataaimsr.temp_loggers = "10.25845/5b4eb0f9bb848"
+    dataaimsr.temp_loggers = "10.25845/5b4eb0f9bb848",
+    dataaimsr.date_format = c("10.25845/5c09bf93f315d" = "%Y-%m-%dT%H:%M:%OS",
+                              "10.25845/5b4eb0f9bb848" = "%Y-%m-%d %H:%M:%OS")
   )
   toset <- !(names(aims_op) %in% names(op))
   if (any(toset)) {

### 2020-05-07 README.Rmd
basic pkgdown structure

@@
 ---
-output:
-  md_document:
-    variant: markdown_github
+output: github_document
 ---
@@
 
-```{r, include=FALSE}
+```{r, include = FALSE}
 stopifnot(require(knitr))
@@
   comment = "#>",
-  fig.path = "inst/figures/",
-  dev = "png",
-  dpi = 150,
-  fig.asp = 0.8,
-  fig.width = 5,
-  out.width = "60%",
-  fig.align = "center"
+  fig.path = "man/figures/README-",
+  out.width = "100%"
 )
@@
 
-<img src="inst/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
+<img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
 
@@
 
-If the environment variable `AIMS_DATA_PLATFORM_API_KEY` is stored in the user's `.Renviron` file then that will be loaded and used automatically.
+If the environment variable `AIMS_DATAPLATFORM_API_KEY` is stored in the user's `.Renviron` file then that will be loaded and used automatically.
 In that case the users `.Renviron` file might look like:
@@
 System        | .Renviron file locations
------------|-------------------------
+--------------|-------------------------
 MS Windows    | `C:\Users\<username>\.Renviron`  or `C:\Users\<username>\Documents\.Renviron`
-Linux      | `/home/<username>/.Renviron`
+Linux / MacOs | `/home/<username>/.Renviron`
 
@@
 ```
-devtools::install_git("https://github.com/AIMS/data-platform-r")
+devtools::install_github("https://github.com/AIMS/data-platform-r")
 ```
@@
 
-Detailed Example
+Further Information
 ----------------
-
-[A more detailed example of the R package usage on the weather dataset page.](10.25845/5c09bf93f315d/example-1.nb.html)  This is an [RStudio](https://www.rstudio.com/) Notebook and can be used interactively from [RStudio](https://www.rstudio.com/).
-__Note that you need to have an AIMS Data Platform API Key available to run this detailed example.__
 

### 2020-05-07 README.Rmd
added github actions
added lifecycle badge

@@
 <img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
+
+<!-- badges: start -->
+[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
+<!-- badges: end -->
 
@@
 
-```
+```{r, eval = FALSE}
 install.packages("devtools")
@@
 
-```
+```{r, eval = FALSE}
 devtools::install_github("https://github.com/AIMS/data-platform-r")

### 2020-05-07 README.Rmd
more badges

--- 2020-05-07 README.Rmd
@@
 
+```{r, echo = FALSE}
+version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
+version <- gsub('-', '.', version)
+```
+
 <img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
+
+<!-- badges: start -->
+[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
+"[![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)"
+[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
+<!-- badges: end -->
 

### 2020-05-07 README.Rmd
typo

--- 2020-05-07 README.Rmd
@@
 
+```{r, echo = FALSE}
+version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
+version <- gsub('-', '.', version)
+```
+
 <img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
+
+<!-- badges: start -->
+[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
+[![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)
+[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
+<!-- badges: end -->
 

### 2020-05-07 README.Rmd
change to badge style

--- 2020-05-07 README.Rmd
@@
 
+```{r, echo = FALSE}
+version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
+version <- gsub('-', '.', version)
+```
+
 <img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
@@
 [![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
+[![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)
+[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
 <!-- badges: end -->

### 2020-05-07 README.Rmd
simplified readme style

@@
 
-<img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
+# dataaimsr <img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
 
@@
 
-AIMS Data Platform R Client
-==========================
+## Overview
 
-__AIMS Data Platform R Client__ will provide easy access to data sets for R applications to the [AIMS Data Platform API](https://aims.github.io/data-platform).
+`dataaimsr` is the **AIMS Data Platform R Client** will provide easy access to data sets for R applications to the [AIMS Data Platform API](https://aims.github.io/data-platform).
 
-Usage of AIMS Data Platform API Key
-----------------------------------
+### Usage of AIMS Data Platform API Key
 
-__AIMS Data Platform__ requires an API Key for requests, [get a key here.](https://aims.github.io/data-platform/key-request)
+**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://aims.github.io/data-platform/key-request)
 
@@
 AIMS_DATAPLATFORM_API_KEY=XXXXXXXXXXXXX
+```
 
-```
 The `.Renviron` file is usually stored in each users home directory.
@@
 
-Installation
-------------
+### Installation
 
-At this stage __AIMS Data Platform R Client__ is not hosted on CRAN R package network.
+At this stage **AIMS Data Platform R Client** is not hosted on CRAN R package network.
 An alternative method of installation is to use the R `devtools` package.
@@
 
-After `devtools` has been installed the __AIMS Data Platform R Client__ can be installed directly
+After `devtools` has been installed the **AIMS Data Platform R Client** can be installed directly
 from GitHub using the following command:
@@
 
-Available Data Sets
--------------------
+### Available Data Sets
 
-The __AIMS Data Platform API__ is a *REST API* providing *JSON* formatted data.
+The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data.
 Documentation about available data sets can be found on the [AIMS Data Platfom API](https://aims.github.io/data-platform).
 
-Further Information
-----------------
+### Further Information
 
-Further information about the __AIMS DataPlatform R Client__ and __AIMS DataPlatform API__ can be seen on the [project page](https://aims.github.io/data-platform-r).
+Further information about the **AIMS DataPlatform R Client** and **AIMS DataPlatform API** can be seen on the [project page](https://aims.github.io/data-platform-r).
 

### 2020-05-08 README.Rmd
more cosmetic changes
added new doi retrieving function; implemented more changes to vignette

@@
 
-# dataaimsr <img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>
+# dataaimsr <img src="man/figures/logo.png" width = 180 alt="dataaimsr Logo" align="right" />
 
@@
 
-`dataaimsr` is the **AIMS Data Platform R Client** will provide easy access to data sets for R applications to the [AIMS Data Platform API](https://aims.github.io/data-platform).
+`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://aims.github.io/data-platform).
 
@@
 
-The API Key can be passed to the package functions as an additional `api_key = 'XXXX'` argument, however it is preferred that API Keys are not stored in code.
+The API Key can be passed to the package functions as an additional `api_key = 'XXXX'` argument, however it is preferred that API Keys are not stored permanently in your machine.
 
@@
 
-At this stage **AIMS Data Platform R Client** is not hosted on CRAN R package network.
+At this stage `dataaimsr` is not hosted on CRAN R package network.
 An alternative method of installation is to use the R `devtools` package.
@@
 
-After `devtools` has been installed the **AIMS Data Platform R Client** can be installed directly
-from GitHub using the following command:
+After `devtools` has been installed `dataaimsr` can be installed directly from GitHub using the following command:
 
@@
 The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data.
-Documentation about available data sets can be found on the [AIMS Data Platfom API](https://aims.github.io/data-platform).
+Documentation about available data sets can be found on the [AIMS Data Platform API](https://aims.github.io/data-platform).
 
@@
 
-Further information about the **AIMS DataPlatform R Client** and **AIMS DataPlatform API** can be seen on the [project page](https://aims.github.io/data-platform-r).
+Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://aims.github.io/data-platform-r).
 
-This library is provided for use under the Creative Commons by Attribution license ([CC BY 3.0](https://creativecommons.org/licenses/by/3.0/au/legalcode)) by the AIMS Datacentre for the [Austrailian Institute of Marine Science](https://www.aims.gov.au)
+This library is provided for use under the Creative Commons by Attribution license ([CC BY 3.0](https://creativecommons.org/licenses/by/3.0/au/legalcode)) by the AIMS Datacentre for the [Australian Institute of Marine Science](https://www.aims.gov.au)

### 2020-05-08 R/dataaimsr.R

@@ -422,3 +422,30 @@ api_key_find <- function(api_key) {
     api_key
   }
 }
+
+#' AIMS Dataset DOI retriever
+#' 
+#' Returns DOI for a given dataset
+#' 
+#' @param target A \code{\link[base]{character}} vector of length 1 
+#' specifying the dataset. Only \code{weather} or 
+#' \code{temp_loggers} are currently allowed.
+#' #' 
+#' @return A \code{\link[base]{character}} vector 
+#' containing the dataset DOI string.
+#' 
+#' @author AIMS Datacentre \email{adc@aims.gov.au}
+#' @export
+#' @examples
+#' \dontrun{
+#' library(dataaimsr)
+#' weather_doi  <-  aims_data_doi_get('weather')
+#' ssts_doi  <-  aims_data_doi_get('temp_loggers')
+#' }
+aims_data_doi_get  <-  function(target) {
+  if (!(target %in% c("weather", "temp_loggers"))) {
+    stop("Wrong type of data target, only \"weather\"",
+         "or \"temp_loggers\" are allowed")
+  }
+  getOption(paste0("dataaimsr.", target))
+}

### 2020-05-08 README.Rmd
small change to readme

@@
 --------------|-------------------------
-MS Windows    | `C:\Users\<username>\.Renviron`  or `C:\Users\<username>\Documents\.Renviron`
-Linux / MacOs | `/home/<username>/.Renviron`
+MS Windows    | <code>C:\Users\&lt;username&gt;\.Renviron</code>  or <code>C:\Users\&lt;username&gt;\Documents\.Renviron</code>
+Linux / MacOs | <code>/home/&lt;username&gt;/.Renviron</code>
 

### 2020-05-08 README.Rmd
fixed forward and backslashes on html code block

--- 2020-05-08 README.Rmd
@@
 --------------|-------------------------
-MS Windows    | `C:\Users\<username>\.Renviron`  or `C:\Users\<username>\Documents\.Renviron`
-Linux / MacOs | `/home/<username>/.Renviron`
+MS Windows    | <code>C:&#92;Users&#92;&#8249;username&#8250;&#92;.Renviron</code>  or <code>C:&#92;Users&#92;&#8249;username&#8250;&#92;Documents&#92;.Renviron</code>
+Linux / MacOs | <code>&#47;home&#47;&#8249;username&#8250;&#47;.Renviron</code>
 

### 2020-05-11 README.Rmd
small changes to rEADME

@@
   comment = "#>",
-  fig.path = "man/figures/README-",
+  fig.path = "man/figures/",
   out.width = "100%"
@@
 ```{r, eval = FALSE}
-devtools::install_github("https://github.com/AIMS/data-platform-r")
+devtools::install_github("https://github.com/AIMS/dataaimsr")
 ```

### 2020-05-11 README.Rmd
added pkgdown badge

@@
 [![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
+![pkgdown](https://github.com/AIMS/data-platform-r/workflows/pkgdown/badge.svg)
 [![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)

### 2020-05-11 README.Rmd
added license and info about our package logos

@@
 
-### Usage of AIMS Data Platform API Key
+## Usage of AIMS Data Platform API Key
 
@@
 
-### Possible .Renviron file locations
+## Possible .Renviron file locations
 
@@
 
-### Installation
+## Installation
 
@@
 
-### Available Data Sets
+## Available Data Sets
 
@@
 
-### Further Information
+## Further Information
 
@@
 This library is provided for use under the Creative Commons by Attribution license ([CC BY 3.0](https://creativecommons.org/licenses/by/3.0/au/legalcode)) by the AIMS Datacentre for the [Australian Institute of Marine Science](https://www.aims.gov.au)
+
+## AIMS R package logos
+
+Our R package logos use a watercolour map of Australia, obtained with the [ggmap](https://cran.r-project.org/web/packages/ggmap/) R package, which downloads original map tiles provided by [Stamen Design](http://stamen.com), under [CC BY 3.0](http://creativecommons.org/licenses/by/3.0), with data from [OpenStreetMap](http://openstreetmap.org), under [CC BY SA](http://creativecommons.org/licenses/by-sa/3.0).

### 2020-05-26 README.Rmd
renamed package and functions

@@
 [![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
-[![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
-![pkgdown](https://github.com/AIMS/data-platform-r/workflows/pkgdown/badge.svg)
+[![R build status](https://github.com/AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/dataaimsr/actions)
+![pkgdown](https://github.com/AIMS/dataaimsr/workflows/pkgdown/badge.svg)
 [![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)
@@
 
-Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://aims.github.io/data-platform-r).
+Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://aims.github.io/dataaimsr).
 

### 2020-05-26 R/dataaimsr.R

@@ -13,7 +13,7 @@
 #' @author AIMS Datacentre \email{adc@aims.gov.au}
 #' 
 #' @importFrom httr http_status content
-error_handle <- function(dt_req) {
+handle_error <- function(dt_req) {
   stop(paste("Error", http_status(dt_req),
                 content(dt_req)))
 }
@@ -22,7 +22,7 @@ error_handle <- function(dt_req) {
 #' 
 #' Wrapper function
 #' 
-#' @inheritParams error_handle
+#' @inheritParams handle_error
 #' 
 #' @details This function submits a \code{dt_req} 
 #' data request via \code{\link[jsonlite]{fromJSON}}.
@@ -48,12 +48,12 @@ json_results  <-  function(dt_req) {
 #' 
 #' Wrapper function
 #' 
-#' @inheritParams error_handle
+#' @inheritParams handle_error
 #' 
 #' @param next_page Logical. Is this a multi-url request?
 #' 
 #' @param ... Additional arguments to be passed to internal function
-#' \code{\link{format_update}}
+#' \code{\link{update_format}}
 #' 
 #' @details This function checks for errors in \code{dt_req} 
 #' data request and processes result via 
@@ -70,15 +70,15 @@ json_results  <-  function(dt_req) {
 #' @author AIMS Datacentre \email{adc@aims.gov.au}
 #' 
 #' @importFrom httr http_error
-request_process <- function(dt_req, next_page = FALSE, ...) {
+process_request <- function(dt_req, next_page = FALSE, ...) {
   if (http_error(dt_req)) {
-    error_handle(dt_req)
+    handle_error(dt_req)
   } else {
     results <- json_results(dt_req)
     if (next_page && length(results$results) == 0) {
       warning("No more data")
     } else {
-      results <- format_update(results, ...)
+      results <- update_format(results, ...)
       if (!next_page) {
         message(paste("Cite this data as:", results$citation))
       }
@@ -117,7 +117,7 @@ request_process <- function(dt_req, next_page = FALSE, ...) {
 #' [Weather](https://aims.github.io/data-platform/weather/index) and 
 #' [Sea Water Temperature Loggers](https://aims.github.io/data-platform/temperature-loggers/index). 
 #' They are searched internally via unique DOI identifiers which 
-#' can be obtained by the function \code{\link{aims_data_doi_get}} (see Examples).
[…]

### 2020-05-26 README.Rmd
updated license badge

@@
 ![pkgdown](https://github.com/AIMS/dataaimsr/workflows/pkgdown/badge.svg)
-[![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)
+[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
 [![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)

### 2020-05-26 README.Rmd
updated license info on readme

@@
 
-This library is provided for use under the Creative Commons by Attribution license ([CC BY 3.0](https://creativecommons.org/licenses/by/3.0/au/legalcode)) by the AIMS Datacentre for the [Australian Institute of Marine Science](https://www.aims.gov.au)
+`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](http://opensource.org/licenses/MIT)).
 

### 2020-05-27 README.Rmd
updated lifecycle to experimental, with warning on readme

@@
 <!-- badges: start -->
-[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
 [![R build status](https://github.com/AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/dataaimsr/actions)
@@
 <!-- badges: end -->
+
+## Warning
+
+**This package and its API dependency are a work in progress. So we advise not installing this package just yet as many of the functionalities may change or simply become deprecated.**
 

### 2020-07-14 README.Rmd
link fix

@@
 
-Our R package logos use a watercolour map of Australia, obtained with the [ggmap](https://cran.r-project.org/web/packages/ggmap/) R package, which downloads original map tiles provided by [Stamen Design](http://stamen.com), under [CC BY 3.0](http://creativecommons.org/licenses/by/3.0), with data from [OpenStreetMap](http://openstreetmap.org), under [CC BY SA](http://creativecommons.org/licenses/by-sa/3.0).
+Our R package logos use a watercolour map of Australia, obtained with the [ggmap](https://CRAN.R-project.org/package=ggmap) R package, which downloads original map tiles provided by [Stamen Design](http://stamen.com), under [CC BY 3.0](http://creativecommons.org/licenses/by/3.0), with data from [OpenStreetMap](http://openstreetmap.org), under [CC BY SA](http://creativecommons.org/licenses/by-sa/3.0).

### 2020-09-07 README.Rmd
transfer of links to open-AIMS

@@
 ```{r, echo = FALSE}
-version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
-version <- gsub('-', '.', version)
+version <- as.vector(read.dcf("DESCRIPTION")[, "Version"])
+version <- gsub("-", ".", version)
 ```
@@
 <!-- badges: start -->
-[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
-[![R build status](https://github.com/AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/dataaimsr/actions)
-![pkgdown](https://github.com/AIMS/dataaimsr/workflows/pkgdown/badge.svg)
+[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![R build status](https://github.com/open-AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/open-AIMS/dataaimsr/actions)
+![pkgdown](https://github.com/open-AIMS/dataaimsr/workflows/pkgdown/badge.svg)
 [![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
 [![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
+[![Ask Us Anything
+\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/open-AIMS/dataaimsr/issues/new)
+![Open Source
+Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
 <!-- badges: end -->
@@
 
-`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://aims.github.io/data-platform).
+`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-aims.github.io/data-platform).
 
@@
 
-**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://aims.github.io/data-platform/key-request)
+**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://open-aims.github.io/data-platform/key-request)
 
-The API Key can be passed to the package functions as an additional `api_key = 'XXXX'` argument, however it is preferred that API Keys are not stored permanently in your machine.
+The API Key can be passed to the package functions as an additional `api_key = "XXXX"` argument, however it is preferred that API Keys are not stored permanently in your machine.
 
@@
 ```{r, eval = FALSE}
-devtools::install_github("https://github.com/AIMS/dataaimsr")
+devtools::install_github("https://github.com/open-AIMS/dataaimsr")
 ```
@@
 The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data.
-Documentation about available data sets can be found on the [AIMS Data Platform API](https://aims.github.io/data-platform).
+Documentation about available data sets can be found on the [AIMS Data Platform API](https://open-aims.github.io/data-platform).
 
@@
 
-Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://aims.github.io/dataaimsr).
+Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://open-aims.github.io/dataaimsr).
 

### 2020-11-11 R/dataaimsr.R
expose_attributes has output for different datasets; improved examples and links between expose_attributes and aims_data

@@ -3,49 +3,87 @@
 #' Expose available query filters which are allowed to be parsed either
 #' via argument \code{summary} or \code{filters} in \code{\link{aims_data}}
 #' 
-#' @param verbose Should explanations be printed to screen? Defaults to TRUE.
-#' @param ... unused.
+#' @param doi A \href{https://www.doi.org/}{Digital Object Identifier}
+#' for a chosen \href{https://open-aims.github.io/data-platform}{AIMS data series}
 #' 
 #' @details Use this function to learn which summary modes and
-#' filters are allowed. The summary option is only available to
-#' the temperature logger data. Future versions will implement the
-#' same feature for the weather station data.
+#' filters are allowed.
+#' 
+#' We are working on implementing summary visualisation methods for weather
+#' station data. So, for the moment, the options below are only available
+#' for temperature logger data. Two options are available:
+#' 
+#' \itemize{
+#'    \item{summary-by-series}{Expose summary for all available series;
+#'          a series is a continuing time-series, i.e. a collection of
+#'          deployments measuring the same parameter at the same site.
+#'          For temperature loggers, series is synonymous with sub-site.
+#'          For weather stations, it is the combination of sub-site and
+#'          parameter.}
+#'    \item{summary-by-deployment}{Expose summary for all available
+#'          deployments.}
+#' }
+#' 
+#' Currently we are working on standardising all filter names
+#' across datasets. However, for the moment they might differ depending on
+#' whether the user is downloading temperature logger data or weather station
+#' data. Below the valid parameter names should be read as
+#' temperature-logger / weather-station (NA means that the particular filter
+#' name is not available for the dataset.
+#' 
+#' \itemize{
+#'    \item{site/site-name}{Filter by a particular site.}
+#'    \item{subsite/NA}{Filter by a particular subsite.}
+#'    \item{series/series_name}{Filter by a particular series.}
+#'    \item{parameter/parameter}{Parameter of interest. Only used for weather
+#'          station data.}
+#'    \item{min_lat/min-latitude}{Minimum latitude; used to filter by a lat-lon box.}
+#'    \item{max_lat/max-latitude}{Maximum latitude; used to filter by a lat-lon box.}
[…]

### 2020-11-11 R/zzz.R

@@ -5,7 +5,7 @@
     dataaimsr.weather = "10.25845/5c09bf93f315d",
     dataaimsr.temp_loggers = "10.25845/5b4eb0f9bb848",
     dataaimsr.version = c("10.25845/5c09bf93f315d" = "/v1.0",
-                              "10.25845/5b4eb0f9bb848" = "-v2.0"    )
+                          "10.25845/5b4eb0f9bb848" = "-v2.0")
   )
   toset <- !(names(aims_op) %in% names(op))
   if (any(toset)) {

### 2020-11-11 R/dataaimsr.R
improved documentation

@@ -219,6 +219,13 @@ make_base_end_pt <- function(doi, aims_version = NA) {
 #' @param api_key An AIMS Data Platform 
 #' \href{https://open-aims.github.io/data-platform/key-request}{API Key}
 #' 
+#' @param summary Should summary tables be printed instead of full data?
+#' Details in ?\code{\link{expose_attributes}}
+#' 
+#' @param aims_version A \code{\link[base]{character}} string
+#' defining the version of database. Must be "/v1.0" or "-v2.0".
+#' If none is provided, then "-v2.0" (the most recent) is used.
+#' 
 #' @param verbose Should links be printed to screen? Used for debugging only
 #' 
 #' @details The AIMS Data Platform R Client provides easy access to 
@@ -329,6 +336,7 @@ page_data <- function(doi, filters = NULL, api_key = NULL,
 #' @author AIMS Datacentre \email{adc@aims.gov.au}
 #' 
 #' @importFrom httr GET add_headers
+#' @importFrom utils URLencode
 next_page_data <- function(url, api_key = NULL, ...) {
   url <- gsub("+", "%2B", URLencode(url), fixed = TRUE)
   dt_req <- GET(url,
@@ -476,8 +484,12 @@ next_page_data <- function(url, api_key = NULL, ...) {
 #' range(cdata_b$time)
 #' 
 #' # 6. downloads summarised temperature data
-#' # for all sites
-#' # within a defined date range
+#' # for all sites that contain data
+#' # within a defined date range; note that
+#' # from_date and thru_date column in the output
+#' # contain the entire coverage of the series
+#' # and does not necessarily correspond to the
+#' # input from_date and thru_date
 #' sdata <- aims_data(ssts_doi,
 #'                    api_key = NULL,
 #'                    summary = "summary-by-series",
@@ -553,6 +565,10 @@ aims_data <- function(doi, filters = NULL, ...) {
 #' @param filter_name A \code{\link[base]{character}} string containing the name of
 #' the filter. Must be "sites" or "series". It could also be "parameters" for the
 #' weather data (i.e. doi = aims_data_doi("weather")).
+#' 
+#' @param aims_version A \code{\link[base]{character}} string
+#' defining the version of database. Must be "/v1.0" or "-v2.0".
+#' If none is provided, then "-v2.0" (the most recent) is used.
 #' 
 #' @return Either a \code{\link[base]{data.frame}} or a \code{\link[base]{character}} vector.
 #' 

### 2020-11-12 README.Rmd
dropped the usage of word client-replaced it with package

@@
 
-`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-aims.github.io/data-platform).
+`dataaimsr` is the **AIMS Data Platform R package**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-aims.github.io/data-platform).
 

### 2020-11-12 R/dataaimsr.R
intro vignette finished

@@ -700,8 +700,8 @@ find_api_key <- function(api_key) {
 #' @examples
 #' \dontrun{
 #' library(dataaimsr)
-#' weather_doi <- aims_data_doi('weather')
-#' ssts_doi <- aims_data_doi('temp_loggers')
+#' weather_doi <- aims_data_doi("weather")
+#' ssts_doi <- aims_data_doi("temp_loggers")
 #' }
 #' 
 #' @export

### 2021-02-10 R/dataaimsr.R
updated package to conform with new changes on API, bumped version

@@ -1,18 +1,17 @@
 #' Expose available query filters
-#' 
+#'
 #' Expose available query filters which are allowed to be parsed either
 #' via argument \code{summary} or \code{filters} in \code{\link{aims_data}}
-#' 
-#' @param doi A \href{https://www.doi.org/}{Digital Object Identifier}
-#' for a chosen \href{https://open-aims.github.io/data-platform}{AIMS data series}
-#' 
+#'
+#' @inheritParams aims_data
+#'
 #' @details Use this function to learn which summary modes and
 #' filters are allowed.
-#' 
+#'
 #' We are working on implementing summary visualisation methods for weather
 #' station data. So, for the moment, the options below are only available
 #' for temperature logger data. Two options are available:
-#' 
+#'
 #' \itemize{
 #'    \item{summary-by-series}{Expose summary for all available series;
 #'          a series is a continuing time-series, i.e. a collection of
@@ -23,30 +22,34 @@
 #'    \item{summary-by-deployment}{Expose summary for all available
 #'          deployments.}
 #' }
-#' 
-#' Currently we are working on standardising all filter names
-#' across datasets. However, for the moment they might differ depending on
-#' whether the user is downloading temperature logger data or weather station
-#' data. Below the valid parameter names should be read as
-#' temperature-logger / weather-station (NA means that the particular filter
-#' name is not available for the dataset.
-#' 
+#'
+#' We offer a list of valid filter names:
+#'
 #' \itemize{
-#'    \item{site/site-name}{Filter by a particular site.}
-#'    \item{subsite/NA}{Filter by a particular subsite.}
-#'    \item{series/series_name}{Filter by a particular series.}
-#'    \item{parameter/parameter}{Parameter of interest. Only used for weather
-#'          station data.}
-#'    \item{min_lat/min-latitude}{Minimum latitude; used to filter by a lat-lon box.}
-#'    \item{max_lat/max-latitude}{Maximum latitude; used to filter by a lat-lon box.}
-#'    \item{min_lon/min-longitude}{Minimum longitude; used to filter by a lat-lon box.}
-#'    \item{max_lon/max-longitude}{Maximum longitude; used to filter by a lat-lon box.}
-#'    \item{from_date/from-date}{Filter from time (string of format YYYY-MM-DD).}
[…]

### 2021-02-10 R/zzz.R

@@ -4,7 +4,7 @@
     dataaimsr.base_end_point = "https://api.aims.gov.au/data",
     dataaimsr.weather = "10.25845/5c09bf93f315d",
     dataaimsr.temp_loggers = "10.25845/5b4eb0f9bb848",
-    dataaimsr.version = c("10.25845/5c09bf93f315d" = "/v1.0",
+    dataaimsr.version = c("10.25845/5c09bf93f315d" = "-v2.0",
                           "10.25845/5b4eb0f9bb848" = "-v2.0")
   )
   toset <- !(names(aims_op) %in% names(op))

### 2021-02-11 tests/testthat.R
added tests skeleton

@@ -1,0 +1,4 @@
+library(testthat)
+library(dataaimsr)
+
+test_check("dataaimsr")

### 2021-02-11 paper/paper.Rmd
added paper skeleton

---
title: 'dataaimsr: A Client for the Australian Institute of Marine Science Data Platform API which provides easy access to AIMS Data Platform'
tags:
  - R
  - sea surface temperature
  - weather stations
  - long-term environmental monitoring
  - Australia
  - API
authors:
  - name: Diego R. Barneche
    orcid: 0000-0002-4568-2362
    affiliation: "1, 2"
  - name: Greg Coleman
    affiliation: "3"
  - name: Jeffrey L. Sheehan
    affiliation: "3"
  - name: Duncan Fermor
    affiliation: "3"
  - name: Murray Logan
    affiliation: "3"
  - name: Mark Rehbein
    affiliation: "3"
affiliations:
 - name: Australian Institute of Marine Science, Crawley, WA 6009, Australia
   index: 1
 - names: The Indian Ocean Marine Research Centre, The University of Western Australia, Crawley, WA 6009, Australia
   index: 2
 - name: Australian Institute of Marine Science, Townsville, Qld 4810, Australia
   index: 3

citation_author: Barneche et al.
date: "`r Sys.Date()`"
bibliography: paper.bib
output:
  my_modified_joss:
    fig_caption: yes
csl: apa.csl
journal: JOSS
---

# Summary

# Background and Statement of need

# Technical details and Usage

## Temperature-logger dataset

### Summary methods

### Datasets

## Weather station datasets

### Summary methods

### Datasets

# Future directions

# Acknowledgements

The development of `dataimsr` was supported by ... Names to be added to the list.

# References

### 2021-02-11 paper/render.R

@@ -1,0 +1,25 @@
+library(rmarkdown)
+library(rticles)
+
+my_modified_joss <- function(journal = "JOSS", keep_md = TRUE,
+                             latex_engine = "xelatex", ...) {
+  rmarkdown::pandoc_available("2.2", TRUE)
+  logo_path <- rticles:::find_resource("joss", paste0(journal, "-logo.png"))
+  journalname <- ifelse(journal == "JOSS", "Journal of Open Source Software",
+                        "Journal of Open Source Education")
+  template <- rticles:::find_resource("joss", "template.tex")
+  p_args <- c("-V", paste0("logo_path=", logo_path), "-V",
+              paste0("journal_name=", journalname), "-V", "graphics=true")
+  fmt <- bookdown::pdf_book(latex_engine = latex_engine, keep_md = keep_md,
+                            pandoc_args = p_args, template = template, ...)
+  fmt$inherits <- "pdf_book"
+  fmt
+}
+
+render_paper <- function() {
+  rmarkdown::render(input = "paper/paper.Rmd", output_dir = "paper",
+                    intermediates_dir = "paper", clean = TRUE)
+  system("rm paper/paper.log")
+}
+
+render_paper()

### 2021-02-11 README.Rmd
codecov badge on README

--- 2020-09-07 README.Rmd
@@
 [![R build status](https://github.com/open-AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/open-AIMS/dataaimsr/actions)
+[![Codecov test coverage](https://codecov.io/gh/open-AIMS/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/open-AIMS/dataaimsr?branch=master)
 ![pkgdown](https://github.com/open-AIMS/dataaimsr/workflows/pkgdown/badge.svg)
@@
 
-`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-aims.github.io/data-platform).
+`dataaimsr` is the **AIMS Data Platform R package**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-AIMS.github.io/data-platform).
 
@@
 
-**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://open-aims.github.io/data-platform/key-request)
+**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://open-AIMS.github.io/data-platform/key-request)
 
@@
 The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data.
-Documentation about available data sets can be found on the [AIMS Data Platform API](https://open-aims.github.io/data-platform).
+Documentation about available data sets can be found on the [AIMS Data Platform API](https://open-AIMS.github.io/data-platform).
 
@@
 
-Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://open-aims.github.io/dataaimsr).
+Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://open-AIMS.github.io/dataaimsr).
 

### 2021-02-11 tests/testthat/setup.R
added tests

@@ -1,0 +1,24 @@
+library(dataaimsr)
+
+add_attr <- function(x, ...) {
+  add_args <- list(...)
+  c(x, add_args)
+}
+
+weather_doi <- aims_data_doi("weather")
+ssts_doi <- aims_data_doi("temp_loggers")
+wrong_doi <- "string"
+my_api_key <- "dFpi9Qum8Q8cNAxnK4Q8Q4PoRrd7SBp9asHISDnI"
+w_filters <- list(series_id = 64, from_date = "2018-01-01",
+                  thru_date = "2018-01-10")
+w_filters_b <- add_attr(w_filters, size = 1e4)
+w_filters_c <- list(series = 64)
+w_filters_d <- list(series_id = 64, from_date = "1900-01-01",
+                    thru_date = "1900-01-10")
+
+s_filters <- list(series_id = 2687, from_date = "2005-01-01",
+                  thru_date = "2005-01-10", size = 300)
+s_filters_b <- s_filters[-4]
+s_filters_c <- list(series = 2687)
+s_filters_d <- list(series_id = 2687, from_date = "1900-01-01",
+                    thru_date = "1900-01-10")

### 2021-02-11 tests/testthat/test-aims_data.R

@@ -1,0 +1,60 @@
+library(dataaimsr)
+
+# default to 1000 returns next_page link
+check_wa <- aims_data(weather_doi, filters = w_filters, api_key = my_api_key)
+check_sa <- aims_data(ssts_doi, filters = s_filters, api_key = my_api_key)
+# larger size removed links from output
+check_wb <- aims_data(weather_doi, filters = w_filters_b, api_key = my_api_key)
+check_sb <- aims_data(ssts_doi, filters = s_filters_b, api_key = my_api_key)
+
+test_that("Correct structure", {
+  expect_is(check_wa, "list")
+  expect_length(check_wa, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_wa)))
+  expect_is(check_sa, "list")
+  expect_length(check_sa, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_sa)))
+  expect_is(check_wb, "list")
+  expect_length(check_wb, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_wb)))
+  expect_is(check_sb, "list")
+  expect_length(check_sb, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_sb)))
+})
+
+check_wc <- aims_data(weather_doi, filters = w_filters_c, api_key = my_api_key)
+check_wd <- aims_data(weather_doi, filters = w_filters_d, api_key = my_api_key)
+check_sc <- aims_data(ssts_doi, filters = s_filters_c, api_key = my_api_key)
+check_sd <- aims_data(ssts_doi, filters = s_filters_d, api_key = my_api_key)
+
+test_that("Wrong filters", {
+  expect_is(check_wc, "list")
+  expect_length(check_wc, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_wc)))
+  expect_null(nrow(check_wc$data))
+  expect_is(check_wd, "list")
+  expect_length(check_wd, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_wd)))
+  expect_null(nrow(check_wd$data))
+  expect_is(check_sc, "list")
+  expect_length(check_sc, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_sc)))
+  expect_null(nrow(check_sc$data))
+  expect_is(check_sd, "list")
+  expect_length(check_sd, 3)
[…]

### 2021-02-11 tests/testthat/test-aims_data_doi.R

@@ -1,0 +1,10 @@
+library(dataaimsr)
+
+test_that("Correct structure", {
+  expect_identical(aims_data_doi("weather"), "10.25845/5c09bf93f315d")
+  expect_identical(aims_data_doi("temp_loggers"), "10.25845/5b4eb0f9bb848")
+  expect_error(aims_data_doi(wrong_doi))
+  expect_error(aims_data_doi(FALSE))
+  expect_error(aims_data_doi(NA))
+  expect_error(aims_data_doi(NULL))
+})

### 2021-02-11 tests/testthat/test-expose_attributes.R

@@ -1,0 +1,11 @@
+library(dataaimsr)
+
+test_that("Correct structure", {
+  expect_is(expose_attributes(weather_doi), "list")
+  expect_is(expose_attributes(ssts_doi), "list")
+  expect_error(expose_attributes(wrong_doi))
+  expect_error(expose_attributes(10))
+  expect_error(expose_attributes(FALSE))
+  expect_error(expose_attributes(NA))
+  expect_error(expose_attributes(NULL))
+})

### 2021-02-11 tests/testthat/test-filter_values.R

@@ -1,0 +1,20 @@
+library(dataaimsr)
+
+test_that("Correct structure", {
+  expect_is(filter_values(weather_doi, filter_name = "site"), "character")
+  expect_is(filter_values(weather_doi, filter_name = "series"), "data.frame")
+  expect_is(filter_values(weather_doi, filter_name = "subsite"), "character")
+  expect_is(filter_values(weather_doi, filter_name = "parameter"), "character")
+  expect_is(filter_values(ssts_doi, filter_name = "site"), "character")
+  expect_identical(filter_values(ssts_doi, filter_name = "series"),
+                   filter_values(ssts_doi, filter_name = "subsite"))
+  expect_is(filter_values(ssts_doi, filter_name = "parameter"), "character")
+})
+
+test_that("Wrong inputs", {
+  expect_error(filter_values(wrong_doi, filter_name = "site"))
+  expect_error(filter_values(wrong_doi, filter_name = "series_id"))
+  expect_error(filter_values(wrong_doi, filter_name = "site-name"))
+  expect_error(filter_values(wrong_doi, filter_name = "site_name"))
+  expect_error(filter_values(ssts_doi))
+})

### 2021-02-11 tests/testthat/test-page_data.R

@@ -1,0 +1,60 @@
+library(dataaimsr)
+
+# default to 1000 returns next_page link
+check_wa <- page_data(weather_doi, filters = w_filters, api_key = my_api_key)
+check_sa <- page_data(ssts_doi, filters = s_filters, api_key = my_api_key)
+# larger size removed links from output
+check_wb <- page_data(weather_doi, filters = w_filters_b, api_key = my_api_key)
+check_sb <- page_data(ssts_doi, filters = s_filters_b, api_key = my_api_key)
+# next_page works
+check_wa_n <- next_page_data(check_wa$links$next_page, api_key = my_api_key)
+check_sa_n <- next_page_data(check_sa$links$next_page, api_key = my_api_key)
+final_nrow_wa <- nrow(check_wa$data) + nrow(check_wa_n$data)
+final_nrow_sa <- nrow(check_sa$data) + nrow(check_sa_n$data)
+
+test_that("Correct structure", {
+  expect_is(check_wa, "list")
+  expect_length(check_wa, 4)
+  expect_true("links" %in% names(check_wa))
+  expect_is(check_wa$links, "list")
+  expect_identical(names(check_wa$links), "next_page")
+  expect_is(check_sa, "list")
+  expect_length(check_sa, 5)
+  expect_true(all(c("cursor", "links") %in% names(check_sa)))
+  expect_is(check_sa$links, "list")
+  expect_identical(names(check_sa$links), "next_page")
+  expect_is(check_wb, "list")
+  expect_length(check_wb, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_wb)))
+  expect_is(check_sb, "list")
+  expect_length(check_sb, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_sb)))
+  expect_is(check_wa_n, "list")
+  expect_length(check_wa_n, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_wa_n)))
+  expect_is(check_sa_n, "list")
+  expect_length(check_sa_n, 3)
+  expect_true(all(c("metadata", "citation", "data") %in% names(check_sa_n)))
+  expect_identical(final_nrow_sa, nrow(check_sb$data))
+  expect_identical(final_nrow_wa, nrow(check_wb$data))
+})
+
+test_that("Wrong filters", {
+  expect_error(page_data(weather_doi, filters = w_filters_c,
+                         api_key = my_api_key))
[…]

### 2021-02-11 README.Rmd
removed warning from README
updated README main info about the package for rOpenSci submission

@@
 
-## Warning
-
-**This package and its API dependency are a work in progress. So we advise not installing this package just yet as many of the functionalities may change or simply become deprecated.**
-
 ## Overview
 
-`dataaimsr` is the **AIMS Data Platform R package**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-AIMS.github.io/data-platform).
+The Australian Institute of Marine Science (AIMS) has a long tradition in
+measuring and monitoring a series of environmental parameters along the
+tropical coast of Australia. These parameters include long-term record of sea
+surface temperature, wind characteristics, atmospheric temperature, pressure,
+chlorophyll-a data, among many others. The AIMS Data Centre team has recently
+developed the [AIMS Data Platform API][1] which is a *REST API* providing
+JSON-formatted data to users. `dataaimsr` is the an **R package** written to
+allow users to communicate with the AIMS Data Platform API using an API key
+and a few convenience functions to interrogate and understand the datasets
+that are available to download.
+
+[1]: https://open-aims.github.io/data-platform/
+
+Currently, there are two AIMS long-term monitoring datasets available to be
+downloaded through `dataaimsr`:
+
+## Northern Australia Automated Marine Weather And Oceanographic Stations
+
+Automatic weather stations have been deployed by AIMS since 1980. Most of the
+stations are along the Great Barrier Reef (GBR) including the Torres Strait in
+North-Eastern Australia but there is also a station in Darwin and one in
+Ningaloo Reef in Western Australia. Many of the stations are located on the
+reef itself either on poles located in the reef lagoon or on tourist pontoons
+or other structures. A list of the weather stations which have been deployed
+by AIMS and the period of time for which data may be available can be
+found on the [metadata][2] webpage. **NB:** Records may not be continuous for
+the time spans given.
+
+[2]: https://apps.aims.gov.au/metadata/view/0887cb5b-b443-4e08-a169-038208109466
+
+## AIMS Sea Water Temperature Observing System (AIMS Temperature Logger Program)
+
+The data provided here are from a number of sea water temperature monitoring
+programs conducted in tropical and subtropical coral reefs environments around
+Australia. Data are available from approximately 80 GBR sites, 16 Coral Sea
+sites, 7 sites in North West Western Australia (WA), 8 Queensland regional
+ports, 13 sites in the Solitary Islands, 4 sites in Papua New Guinea and 10
+sites in the Cocos (Keeling) Islands. Data are obtained from in-situ data
+loggers deployed on the reef. Temperature instruments sample water
+temperatures every 5-10 minutes (typically) and are exchanged and downloaded
+approximately every 12 months. Temperature loggers on the reef-flat are
+generally placed just below Lowest Astronomical Tide level. Reef-slope (or
+where specified as Upper reef-slope) generally refers to depths 5--9 m while
+Deep reef-slope refers to depths of ~20 m. For more information on the dataset
+and its usage, please visit the [metadata][3] webpage.
+
+[3]: https://apps.aims.gov.au/metadata/view/4a12a8c0-c573-11dc-b99b-00008a07204e
 
@@
 
-**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://open-AIMS.github.io/data-platform/key-request)
+**AIMS Data Platform** requires an API Key for data requests, [get a key here](https://open-AIMS.github.io/data-platform/key-request).
 
-The API Key can be passed to the package functions as an additional `api_key = "XXXX"` argument, however it is preferred that API Keys are not stored permanently in your machine.
-
-If the environment variable `AIMS_DATAPLATFORM_API_KEY` is stored in the user's `.Renviron` file then that will be loaded and used automatically.
-In that case the users `.Renviron` file might look like:
+The API Key can be passed to the package functions as an additional
+`api_key = "XXXX"` argument. alternatively, the environment variable
+`AIMS_DATAPLATFORM_API_KEY` can be stored in the user's `.Renviron` file for
+automatic loading at the start of an R session. In that case the users can 
+modify their `.Renviron` file by adding the following line:
 
@@
 
-The `.Renviron` file is usually stored in each users home directory.
+## Possible .Renviron file locations
 
-## Possible .Renviron file locations
+The `.Renviron` file is usually stored in each users home directory:
 
@@
 At this stage `dataaimsr` is not hosted on CRAN R package network.
-An alternative method of installation is to use the R `devtools` package.
+An alternative method of installation is to use the R `remotes` package.
 
-R `devtools` can be installed using the following command:
+R `remotes` can be installed using the following command:
 
 ```{r, eval = FALSE}
-install.packages("devtools")
+install.packages("remotes")
 ```
 
-After `devtools` has been installed `dataaimsr` can be installed directly from GitHub using the following command:
+After `remotes` has been installed `dataaimsr` can be installed directly from
+GitHub using the following command:
 
 ```{r, eval = FALSE}
-devtools::install_github("https://github.com/open-AIMS/dataaimsr")
+remotes::install_github("https://github.com/open-AIMS/dataaimsr")
 ```
 
-This command will also install 2 dependencies `httr` and `jsonlite`.
-
-## Available Data Sets
-
-The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data.
-Documentation about available data sets can be found on the [AIMS Data Platform API](https://open-AIMS.github.io/data-platform).
+This command will also install the three package dependencies: `httr`,
+`jsonlite` and `parsedate`.
 

### 2021-02-11 README.Rmd
adjustments to readme

@@
 developed the [AIMS Data Platform API][1] which is a *REST API* providing
-JSON-formatted data to users. `dataaimsr` is the an **R package** written to
+JSON-formatted data to users. `dataaimsr` is an **R package** written to
 allow users to communicate with the AIMS Data Platform API using an API key
@@
 
-## Northern Australia Automated Marine Weather And Oceanographic Stations
+### Northern Australia Automated Marine Weather And Oceanographic Stations
 
@@
 stations are along the Great Barrier Reef (GBR) including the Torres Strait in
-North-Eastern Australia but there is also a station in Darwin and one in
+North-Eastern Australia but there is also a station in Darwin and one at
 Ningaloo Reef in Western Australia. Many of the stations are located on the
@@
 
-## AIMS Sea Water Temperature Observing System (AIMS Temperature Logger Program)
+### AIMS Sea Water Temperature Observing System (AIMS Temperature Logger Program)
 
@@
 
-## Usage of AIMS Data Platform API Key
+## Requesting an AIMS Data Platform API Key
 
@@
 ```
-
-## Possible .Renviron file locations
 
@@
 
-## Further Information
+## Usage
 
-Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://open-AIMS.github.io/dataaimsr).
+Examples about how to navigate `dataaimsr` and interrogate the datasets can
+be found on our [online vignettes][4].
+
+[4]: https://open-AIMS.github.io/dataaimsr/articles
+
+## License
 

### 2021-02-11 paper/paper.Rmd
first draft of paper

@@
    index: 1
- - names: The Indian Ocean Marine Research Centre, The University of Western Australia, Crawley, WA 6009, Australia
+ - name: The Indian Ocean Marine Research Centre, The University of Western Australia, Crawley, WA 6009, Australia
    index: 2
@@
 
+`dataaimsr` is an **R package** written to provide open access to decades
+of field measurements of atmospheric and oceanographic parameters around the
+coast of Australia, conducted by the
+[Australian Institute of Marine Science][0] (AIMS). The package communicates
+with the recently-developed AIMS Data Platform API via an API key. Here we
+describe the available datasets as well as example usage cases.
+
+[0]: https://www.aims.gov.au/
+
 # Background and Statement of need
+
+The Australian Institute of Marine Science (AIMS) has a long tradition in
+measuring and monitoring a series of environmental parameters along the
+tropical coast of Australia. These parameters include long-term record of sea
+surface temperature, wind characteristics, atmospheric temperature, pressure,
+chlorophyll-a data, among many others. The AIMS Data Centre team has recently
+developed the [AIMS Data Platform API][1] which is a *REST API* providing
+JSON-formatted data to users. `dataaimsr` is an **R package** written to
+allow users to communicate with the AIMS Data Platform API using an API key
+and a few convenience functions to interrogate and understand the datasets
+that are available to download.
+
+[1]: https://open-aims.github.io/data-platform/
+
+Currently, there are two AIMS long-term monitoring datasets available to be
+downloaded through `dataaimsr`:
+
+### Northern Australia Automated Marine Weather And Oceanographic Stations
+
+Automatic weather stations have been deployed by AIMS since 1980. Most of the
+stations are along the Great Barrier Reef (GBR) including the Torres Strait in
+North-Eastern Australia but there is also a station in Darwin and one at
+Ningaloo Reef in Western Australia. Many of the stations are located on the
+reef itself either on poles located in the reef lagoon or on tourist pontoons
+or other structures. A list of the weather stations which have been deployed
+by AIMS and the period of time for which data may be available can be
+found on the [AIMS metadata][2] webpage. **NB:** Records may not be continuous
+for the time spans given.
+
+[2]: https://apps.aims.gov.au/metadata/view/0887cb5b-b443-4e08-a169-038208109466
+
+### AIMS Sea Water Temperature Observing System (AIMS Temperature Logger Program)
+
+The data provided here are from a number of sea water temperature monitoring
+programs conducted in tropical and subtropical coral reefs environments around
+Australia. Data are available from approximately 80 GBR sites, 16 Coral Sea
+sites, 7 sites in North West Western Australia (WA), 8 Queensland regional
+ports, 13 sites in the Solitary Islands, 4 sites in Papua New Guinea and 10
+sites in the Cocos (Keeling) Islands. Data are obtained from in-situ data
+loggers deployed on the reef. Temperature instruments sample water
+temperatures every 5-10 minutes (typically) and are exchanged and downloaded
+approximately every 12 months. Temperature loggers on the reef-flat are
+generally placed just below Lowest Astronomical Tide level. Reef-slope (or
+where specified as Upper reef-slope) generally refers to depths 5--9 m while
+Deep reef-slope refers to depths of ~20 m. For more information on the dataset
+and its usage, please visit the [AIMS metadata][3] webpage.
+
+[3]: https://apps.aims.gov.au/metadata/view/4a12a8c0-c573-11dc-b99b-00008a07204e
 
@@
 
-## Temperature-logger dataset
+Before loading the package, a user needs to download and store their personal
+[AIMS Data Platform API Key][4]---we recommend it storing it in `.Renviron`.
 
-### Summary methods
+[4]: https://open-aims.github.io/data-platform/key-request
 
-### Datasets
+The [Weather Station][2] and [Sea Water Temperature Loggers][3] datasets are
+very large (terabytes in size), and as such they are not locally stored.
+They are instead downloaded via the API and unique DOI identifiers. The 
+datasets are structured by sites, series and parameters. A series is a 
+continuing time-series, i.e. a collection of deployments measuring the 
+same parameter (e.g. Air Temperature, Air Pressure, Chlorophyll) at the 
+same subsite. So, for a given site and parameter, there might exist multiple
+subsites and therefore series, in which case they are most likely 
+distinguishable by depth.
 
-## Weather station datasets
+For the Sea Water Temperature Loggers dataset, series is synonymous 
+with the variable called subsite. For the Weather Station dataset, it 
+is the combination of subsite and parameter.
 
-### Summary methods
+## Discover a dataset
 
-### Datasets
+The [AIMS Data Platform API][1] points to the full metadata of each
+dataset. We are currently working on ways to facilitate the 
+visualisation of both datasets and their multiple features directly
+through the R package. At the moment though it is only possible
+to visualise summary information for the Sea Water Temperature Loggers
+dataset. A similar feature for the Weather Station dataset will be 
+implemented in the near future (likely late 2021)---so for now, please
+refer to the online metadata to discover from where (and when) one can 
+download data.
+
+### Data summaries
+
+The first step would be to visualise the dataset. We do this by
+mapping all available sites. First we need to store the DOI for the
+target dataset---this is done via the function `aims_data_doi`. We
+can then download the summary information for the Sea Water Temperature 
+Loggers dataset using the main function called `aims_data`:
+
+```{r, message = FALSE, warning = FALSE}
+library(dataaimsr)
+# see ?aims_data_doi for argument names
+ssts_doi <- aims_data_doi("temp_loggers")
+sdata <- aims_data(ssts_doi, api_key = NULL,
+                   summary = "summary-by-series")
+head(sdata)
+```
+
+Setting the argument `api_key = NULL` means that `dataaimsr` will
+automatically search for the user's API key stored in `.Renviron`.
+The `summary` argument here is key. It should only be flagged when the
+user wants an overview of the available data. Again, this currently
+implemented for the Sea Water Temperature Loggers dataset. One can
+visualise `summary-by-series` or `summary-by-deployment`. The output of
+`aims_data` when summary is `NA` (the default) is a `data.frame`.
+
+Notice that `sdata` contains a lot of information, most of which is
+related to site / series / parameter ID. Each row corresponds to a
+unique series, and a certain site may contain multiple series; in such
+cases, series generally differ from one another by depth. The columns 
+`time_coverage_start` and `time_coverage_end` are probably one of the most
+valuable pieces of information. They provide the user with the window of data
+collection for a particular series, which is probably crucial to decide
+whether that particular series is of relevance to the specific question in
+hand.
+
+Also note that there are three columns containing the total number of 
+observations in a series: `uncal_obs`, `cal_obs` and `qc_obs`, which 
+respectively stand for uncalibrated, calibrated, and quality-controlled 
+observations. **Mark, we need a few sentences explaining the quality control**
+**procdure**. One can visualise this data, for instance, by plotting them
+on a map of Australia, while colouring based on the total amount of calibrated
+observations (Fig. \@ref(fig:summary)).
+
+```{r echo = FALSE, eval = FALSE}
+library(tidyverse)
+library(ggmap)
+sdata <- sdata %>%
+  dplyr::mutate(cols = cal_obs * 1e-3) %>%
+  tidyr::drop_na(lon, lat)
+lab <- expression(atop("# Calibrated obs.",
+                       paste("(" %*% 10^3, ")")))
+ozmap <- ggmap::get_stamenmap(bbox = c(left = 94, bottom = -45,
+                                       right = 162, top = 0),
+                              zoom = 4, maptype = "watercolor")
+out <- ggmap::ggmap(ozmap) +
+  theme_void() +
+  geom_point(data = sdata,
+             mapping = aes(x = lon, y = lat,
+                           colour = cols,
+                           fill = cols),
+             shape = 16, alpha = 0.8) +
+  scale_colour_gradient(name = lab,
+                        low = "dodgerblue4",
+                        high = "darkred") +
+  scale_fill_gradient(name = lab,
+                      low = "dodgerblue4",
+                      high = "darkred")
+ggsave("paper/summary.png", out, width = 7, height = 4.36, units = "in",
+       device = "png", dpi = 300)
+```
+
+(ref:fig-summary) Distribution of all temperature logger series around Australian waters.
+
+```{r summary, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-summary)", cache = TRUE}
+knitr::include_graphics("summary.png")
+```
+
+In the case of the Weather Station dataset, the user can call a
+the `filter_values` function which allows one to query what
+sites, series and parameters are available for both datasets:
+
+```{r, message = FALSE, warning = FALSE}
+weather_doi <- aims_data_doi("weather")
+filter_values(weather_doi, filter_name = "series") %>%
+  head()
+```
+
+The downside is that one cannot know what time window is available
+for each one of those, nor how they are nested (i.e. series /
+parameter / site). In a way though the series name generally
+gives that information anyway (see code output above). If knowing the 
+available observation window is absolutely crucial, then as mentioned 
+above the user should refer to the [online metadata][3].
+
+## Download slices of datasets
+
+We recommend slicing the datasets because AIMS monitoring datasets are of very 
+high temporal resolution and if one tries to download an entire series
+it might take hours if not days. To slice the datasets properly, the user
+needs to apply filters to their query.
+
+### Data filters
+
+Filters are the last important information the user needs to know to 
+master the navigation and download of AIMS monitoring datasets. Each 
+dataset can filtered by attributes which can be exposed with the function `expose_attributes`:
+
+```{r, message = FALSE, warning = FALSE}
+expose_attributes(weather_doi)
+expose_attributes(ssts_doi)
+```
+
+The help file (see `?expose_attributes`) contains the details about what
+each filter targets. So, having an understanding of the summaries and what
+filters are available provide the user with a great head start.
+
+Downloading the data is achieved using the same `aims_data` function, 
+however now the `summary` argument is omitted, and instead 
+implement filters. For example, to download all the data collected at the
+[Yongala wreck][6] for a specific time window:
+
+[6]: https://en.wikipedia.org/wiki/SS_Yongala
+
+```{r, message = FALSE, warning = FALSE}
+wdata_a <- aims_data(weather_doi, api_key = NULL,
+                     filters = list(site = "Yongala",
+                                    from_date = "2018-01-01",
+                                    thru_date = "2018-01-02"))
+```
+
+The output of `aims_data` when summary is omitted (the default) is a list
+containing three elements:
+
+- `metadata` a doi link containing the metadata record for the data series
+
+- `citation` the citation information for the particular dataset
+
+- `data` an output `data.frame`
+
+```{r}
+wdata_a$metadata
+```
+
+```{r}
+wdata_a$citation
+```
+
+```{r}
+head(wdata_a$data)
+```
+
+Note that there are numerous parameters available for this site at the
+specified time:
+
+```{r}
+unique(wdata_a$data$parameter)
+```
+
+And the actual measurements are either raw or quality-controlled (Fig. \@ref(fig:wind)).
+
+```{r echo = FALSE, eval = FALSE}
+out <- wdata_a$data %>%
+  dplyr::filter(grepl("Wind Speed", parameter)) %>%
+  ggplot(data = .) +
+    geom_line(aes(x = time, y = qc_val, colour = parameter)) +
+    labs(x = "Date",
+         y = "Wind speed (km / h)",
+         colour = "Site",
+         title = "AIMS Weather stations",
+         subtitle = "Yongala (2018)") +
+    theme_bw()
+ggsave("paper/wind.png", out, width = 7.4, height = 5.2, units = "in",
+       device = "png", dpi = 300)
+```
+
+(ref:fig-wind) Yongala wreck wind speed profiles between the first and second of January 2018.
+
+```{r wind, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-wind)", cache = TRUE}
+knitr::include_graphics("wind.png")
+```
+
+The filters `from_date` and `thru_date` can be further refined by including a
+time window to download the data:
+
+```{r, message = FALSE, warning = FALSE}
+wdata_b <- aims_data(weather_doi,
+                     api_key = NULL,
+                     filters = list(series_id = 64,
+                                    from_date = "1991-10-18T06:00:00",
+                                    thru_date = "1991-10-18T12:00:00"))$data
+range(wdata_b$time)
+```
 

### 2021-02-11 paper/paper.Rmd
title

@@
 ---
-title: 'dataaimsr: A Client for the Australian Institute of Marine Science Data Platform API which provides easy access to AIMS Data Platform'
+title: 'dataaimsr: An R Client for the Australian Institute of Marine Science Data Platform API which provides easy access to AIMS Data Platform'
 tags:

### 2021-02-15 README.Rmd
added ropensci in review badge

@@
 <!-- badges: start -->
+[![](https://badges.ropensci.org/428_status.svg)](https://github.com/ropensci/software-review/issues/428)
 [![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)

### 2021-03-17 R/aims_data.R
addressing comment re: `aims_data_doi`: - renamed to data_doi and moved to R/helpers.R; - now it is no longer exported; - the target argument has been transferred to aims_data, filter_values and expose_attributes; - updated all documentation, vignettes and tests accordingly.

@@ -4,9 +4,9 @@
 #' the \href{https://open-aims.github.io/data-platform}{AIMS Data Platform}
 #' via the AIMS Data Platform API
 #'
-#' @param doi A \href{https://www.doi.org/}{Digital Object Identifier}
-#' for a chosen
-#' \href{https://open-aims.github.io/data-platform}{AIMS data series}
+#' @param target A \code{\link[base]{character}} vector of length 1 specifying
+#' the dataset. Only \code{weather} or \code{temp_loggers} are currently
+#' allowed.
 #' @param filters A \code{\link[base]{list}} containing a set of
 #' filters for the data query (see Details)
 #' @param ... Additional arguments to be passed to internal functions
@@ -27,9 +27,8 @@
 #' [AIMS Data Platform API](https://open-aims.github.io/data-platform):
 #' [Weather](https://weather.aims.gov.au/#/overview) and
 #' [Sea Water Temperature Loggers](https://tinyurl.com/h93mcojk).
-#' They are searched internally via unique DOI identifiers which
-#' can be obtained by the function \code{\link{aims_data_doi}} (see Examples).
-#' Only one DOI at a time can be passed to the argument \code{doi}.
+#' They are searched internally via unique DOI identifiers.
+#' Only one data type at a time can be passed to the argument \code{target}.
 #'
 #' A list of arguments for \code{filters} can be exposed for both
 #' [Weather](https://weather.aims.gov.au/#/overview) and
@@ -69,14 +68,11 @@
 #' # assumes that user already has API key saved to
 #' # .Renviron
 #'
-#' weather_doi <- aims_data_doi("weather")
-#' ssts_doi <- aims_data_doi("temp_loggers")
-#'
 #' # start downloads:
 #' # 1. downloads weather data from
 #' # site Yongala
 #' # within a defined date range
-#' wdf_a <- aims_data(weather_doi, api_key = NULL,
+#' wdf_a <- aims_data("weather", api_key = NULL,
 #'                    filters = list(site = "Yongala",
 #'                                   from_date = "2018-01-01",
 #'                                   thru_date = "2018-01-02"))$data
@@ -84,7 +80,7 @@
 #' # 2. downloads weather data from all sites
 #' # under series_id 64 from Davies Reef
 #' # within a defined date range
-#' wdf_b <- aims_data(weather_doi, api_key = NULL,
[…]

### 2021-03-17 R/aims_data_doi.R

@@ -1,28 +1,0 @@
-#' AIMS Dataset DOI retriever
-#'
-#' Returns DOI for a given dataset
-#'
-#' @param target A \code{\link[base]{character}} vector of length 1 specifying
-#' the dataset. Only \code{weather} or #' \code{temp_loggers} are currently
-#' allowed.
-#'
-#' @return A \code{\link[base]{character}} vector
-#' containing the dataset DOI string.
-#'
-#' @author AIMS Datacentre \email{adc@aims.gov.au}
-#'
-#' @examples
-#' \dontrun{
-#' library(dataaimsr)
-#' weather_doi <- aims_data_doi("weather")
-#' ssts_doi <- aims_data_doi("temp_loggers")
-#' }
-#'
-#' @export
-aims_data_doi <- function(target) {
-  if (!(target %in% c("weather", "temp_loggers"))) {
-    stop("Wrong type of data target, only \"weather\"",
-         "or \"temp_loggers\" are allowed")
-  }
-  getOption(paste0("dataaimsr.", target))
-}

### 2021-03-17 R/expose_attributes.R

@@ -66,26 +66,20 @@
 #' @examples
 #' \dontrun{
 #' library(dataaimsr)
-#' weather_doi <- aims_data_doi("weather")
-#' ssts_doi <- aims_data_doi("temp_loggers")
-#' expose_attributes(weather_doi)
-#' expose_attributes(ssts_doi)
+#' expose_attributes("weather")
+#' expose_attributes("temp_loggers")
 #' }
 #'
 #' @export
-expose_attributes <- function(doi) {
-  w_doi <- aims_data_doi("weather")
-  tl_doi <- aims_data_doi("temp_loggers")
-  if (!is.character(doi) | (is.character(doi) &&
-        !any(doi %in% c(w_doi, tl_doi)))) {
-    stop("Incorrect input doi. Please see ?aims_data_doi")
-  }
-  if (doi == tl_doi) {
+expose_attributes <- function(target) {
+  # used to evaluate input only
+  invisible(data_doi(target = target))
+  if (target == "temp_loggers") {
     list(summary = c("summary-by-series", "summary-by-deployment"),
          filters = c("site", "subsite", "series", "series_id", "parameter",
                      "size", "min_lat", "max_lat", "min_lon", "max_lon",
                      "from_date", "thru_date", "version", "cursor"))
-  } else if (doi == w_doi) {
+  } else if (target == "weather") {
     list(summary = NA,
          filters = c("site", "subsite", "series", "series_id", "parameter",
                      "size", "min_lat", "max_lat", "min_lon", "max_lon",

### 2021-03-17 R/filter_values.R

@@ -4,7 +4,7 @@
 #' to query about the existing possibilities of
 #' a given filter name
 #'
-#' @inheritParams page_data
+#' @inheritParams aims_data
 #'
 #' @param filter_name A \code{\link[base]{character}} string containing the
 #' name of the filter. Must be "site", "subsite", "series", or
@@ -29,20 +29,13 @@
 #' @examples
 #' \dontrun{
 #' library(dataaimsr)
-#' weather_doi <- aims_data_doi("weather")
-#' ssts_doi <- aims_data_doi("temp_loggers")
-#' filter_values(weather_doi, filter_name = "site")
-#' filter_values(weather_doi, filter_name = "subsite")
-#' filter_values(weather_doi, filter_name = "series")
-#' filter_values(weather_doi, filter_name = "parameter")
-#' filter_values(ssts_doi, filter_name = "site")
-#' filter_values(ssts_doi, filter_name = "subsite")
-#' filter_values(ssts_doi, filter_name = "series") # same as subsite
-#' filter_values(ssts_doi, filter_name = "parameter")
+#' filter_values("weather", filter_name = "site")
+#' filter_values("temp_loggers", filter_name = "subsite")
 #' }
 #'
 #' @export
-filter_values <- function(doi, filter_name) {
+filter_values <- function(target, filter_name) {
+  doi <- data_doi(target)
   if (length(filter_name) != 1) {
     stop("Argument \"filter_name\" should contain one single value")
   }

### 2021-03-17 R/helpers.R

@@ -92,7 +92,7 @@ make_base_end_pt <- function(doi, aims_version = NA) {
 #'
 #' When \code{\link[jsonlite]{fromJSON}} returns a list, format list names
 #'
-#' @inheritParams aims_data
+#' @inheritParams page_data
 #'
 #' @param results A \code{\link[jsonlite]{fromJSON}} list
 #' generated by \code{\link{json_results}}.
@@ -139,4 +139,31 @@ find_api_key <- function(api_key) {
   } else {
     api_key
   }
+}
+
+#' AIMS Dataset DOI retriever
+#'
+#' Returns DOI for a given dataset
+#'
+#' @param target A \code{\link[base]{character}} vector of length 1 specifying
+#' the dataset. Only \code{weather} or \code{temp_loggers} are currently
+#' allowed.
+#'
+#' @return A \code{\link[base]{character}} vector
+#' containing the dataset DOI string.
+#'
+#' @author AIMS Datacentre \email{adc@aims.gov.au}
+#'
+#' @examples
+#' \dontrun{
+#' library(dataaimsr)
+#' weather_doi <- data_doi("weather")
+#' ssts_doi <- data_doi("temp_loggers")
+#' }
+data_doi <- function(target) {
+  if (!(target %in% c("weather", "temp_loggers"))) {
+    stop("Wrong type of data target, only \"weather\"",
+         "or \"temp_loggers\" are allowed")
+  }
+  getOption(paste0("dataaimsr.", target))
 }

### 2021-03-17 R/page_data.R

@@ -6,6 +6,9 @@
 #'
 #' @inheritParams aims_data
 #'
+#' @param doi A \href{https://www.doi.org/}{Digital Object Identifier}
+#' for a chosen
+#' \href{https://open-aims.github.io/data-platform}{AIMS data series}
 #' @param api_key An AIMS Data Platform
 #' \href{https://open-aims.github.io/data-platform/key-request}{API Key}
 #' @param summary Should summary tables be printed instead of full data?

### 2021-03-17 tests/testthat/setup.R

@@ -5,10 +5,7 @@ add_attr <- function(x, ...) {
   c(x, add_args)
 }
 
-weather_doi <- aims_data_doi("weather")
-ssts_doi <- aims_data_doi("temp_loggers")
-wrong_doi <- "string"
-my_api_key <- "1NIik2HDo36shE3FG3MfFMLlNBfEOL945FIH7fX0"
+my_api_key <- find_api_key(NULL)
 w_filters <- list(series_id = 64, from_date = "2018-01-01",
                   thru_date = "2018-01-10")
 w_filters_b <- add_attr(w_filters, size = 1e4)

### 2021-03-17 tests/testthat/test-aims_data.R

@@ -1,11 +1,14 @@
 library(dataaimsr)
 
 # default to 1000 returns next_page link
-check_wa <- aims_data(weather_doi, filters = w_filters, api_key = my_api_key)
-check_sa <- aims_data(ssts_doi, filters = s_filters, api_key = my_api_key)
+check_wa <- aims_data("weather", filters = w_filters, api_key = my_api_key)
+check_sa <- aims_data("temp_loggers", filters = s_filters,
+                      api_key = my_api_key)
 # larger size removed links from output
-check_wb <- aims_data(weather_doi, filters = w_filters_b, api_key = my_api_key)
-check_sb <- aims_data(ssts_doi, filters = s_filters_b, api_key = my_api_key)
+check_wb <- aims_data("weather", filters = w_filters_b,
+                      api_key = my_api_key)
+check_sb <- aims_data("temp_loggers", filters = s_filters_b,
+                      api_key = my_api_key)
 
 test_that("Correct structure", {
   expect_is(check_wa, "list")
@@ -22,10 +25,10 @@ test_that("Correct structure", {
   expect_true(all(c("metadata", "citation", "data") %in% names(check_sb)))
 })
 
-check_wc <- aims_data(weather_doi, filters = w_filters_c, api_key = my_api_key)
-check_wd <- aims_data(weather_doi, filters = w_filters_d, api_key = my_api_key)
-check_sc <- aims_data(ssts_doi, filters = s_filters_c, api_key = my_api_key)
-check_sd <- aims_data(ssts_doi, filters = s_filters_d, api_key = my_api_key)
+check_wc <- aims_data("weather", filters = w_filters_c, api_key = my_api_key)
+check_wd <- aims_data("weather", filters = w_filters_d, api_key = my_api_key)
+check_sc <- aims_data("temp_loggers", filters = s_filters_c, api_key = my_api_key)
+check_sd <- aims_data("temp_loggers", filters = s_filters_d, api_key = my_api_key)
 
 test_that("Wrong filters", {
   expect_is(check_wc, "list")
@@ -47,14 +50,14 @@ test_that("Wrong filters", {
 })
 
 test_that("summary requests", {
-  expect_message(aims_data(weather_doi, api_key = my_api_key,
+  expect_message(aims_data("weather", api_key = my_api_key,
                            summary = "summary-by-series"))
-  expect_message(aims_data(weather_doi, api_key = my_api_key,
+  expect_message(aims_data("weather", api_key = my_api_key,
                            summary = "summary-by-deployment"))
[…]

### 2021-03-17 tests/testthat/test-aims_data_doi.R

@@ -1,10 +1,0 @@
-library(dataaimsr)
-
-test_that("Correct structure", {
-  expect_identical(aims_data_doi("weather"), "10.25845/5c09bf93f315d")
-  expect_identical(aims_data_doi("temp_loggers"), "10.25845/5b4eb0f9bb848")
-  expect_error(aims_data_doi(wrong_doi))
-  expect_error(aims_data_doi(FALSE))
-  expect_error(aims_data_doi(NA))
-  expect_error(aims_data_doi(NULL))
-})

### 2021-03-17 tests/testthat/test-expose_attributes.R

@@ -1,9 +1,9 @@
 library(dataaimsr)
 
 test_that("Correct structure", {
-  expect_is(expose_attributes(weather_doi), "list")
-  expect_is(expose_attributes(ssts_doi), "list")
-  expect_error(expose_attributes(wrong_doi))
+  expect_is(expose_attributes("weather"), "list")
+  expect_is(expose_attributes("temp_loggers"), "list")
+  expect_error(expose_attributes("string"))
   expect_error(expose_attributes(10))
   expect_error(expose_attributes(FALSE))
   expect_error(expose_attributes(NA))

### 2021-03-17 tests/testthat/test-filter_values.R

@@ -1,20 +1,21 @@
 library(dataaimsr)
 
 test_that("Correct structure", {
-  expect_is(filter_values(weather_doi, filter_name = "site"), "character")
-  expect_is(filter_values(weather_doi, filter_name = "series"), "data.frame")
-  expect_is(filter_values(weather_doi, filter_name = "subsite"), "character")
-  expect_is(filter_values(weather_doi, filter_name = "parameter"), "character")
-  expect_is(filter_values(ssts_doi, filter_name = "site"), "character")
-  expect_identical(filter_values(ssts_doi, filter_name = "series"),
-                   filter_values(ssts_doi, filter_name = "subsite"))
-  expect_is(filter_values(ssts_doi, filter_name = "parameter"), "character")
+  expect_is(filter_values("weather", filter_name = "site"), "character")
+  expect_is(filter_values("weather", filter_name = "series"), "data.frame")
+  expect_is(filter_values("weather", filter_name = "subsite"), "character")
+  expect_is(filter_values("weather", filter_name = "parameter"), "character")
+  expect_is(filter_values("temp_loggers", filter_name = "site"), "character")
+  expect_identical(filter_values("temp_loggers", filter_name = "series"),
+                   filter_values("temp_loggers", filter_name = "subsite"))
+  expect_is(filter_values("temp_loggers", filter_name = "parameter"),
+            "character")
 })
 
 test_that("Wrong inputs", {
-  expect_error(filter_values(wrong_doi, filter_name = "site"))
-  expect_error(filter_values(wrong_doi, filter_name = "series_id"))
-  expect_error(filter_values(wrong_doi, filter_name = "site-name"))
-  expect_error(filter_values(wrong_doi, filter_name = "site_name"))
-  expect_error(filter_values(ssts_doi))
+  expect_error(filter_values("string", filter_name = "site"))
+  expect_error(filter_values("string", filter_name = "series_id"))
+  expect_error(filter_values("string", filter_name = "site-name"))
+  expect_error(filter_values("string", filter_name = "site_name"))
+  expect_error(filter_values("temp_loggers"))
 })

### 2021-03-17 tests/testthat/test-helpers.R

@@ -1,5 +1,8 @@
 library(dataaimsr)
 
+weather_doi <- data_doi("weather")
+ssts_doi <- data_doi("temp_loggers")
+wrong_doi <- "string"
 base_end_pt <- make_base_end_pt(weather_doi, aims_version = NA)
 good_pt <- paste(base_end_pt, weather_doi, "data", sep = "/")
 bad_pt <- paste(base_end_pt, weather_doi, "wrong", sep = "/")
@@ -82,4 +85,13 @@ test_that("Correctly update request output format", {
   expect_identical(names(update_format(json_out)$links), "next_page")
   expect_identical(update_format(json_out)$links[[1]],
                    json_results(good_dt_req)$links[[1]])
+})
+
+test_that("Correct structure", {
+  expect_identical(data_doi("weather"), "10.25845/5c09bf93f315d")
+  expect_identical(data_doi("temp_loggers"), "10.25845/5b4eb0f9bb848")
+  expect_error(data_doi(wrong_doi))
+  expect_error(data_doi(FALSE))
+  expect_error(data_doi(NA))
+  expect_error(data_doi(NULL))
 })

### 2021-03-17 tests/testthat/test-page_data.R

@@ -1,5 +1,8 @@
 library(dataaimsr)
 
+weather_doi <- data_doi("weather")
+ssts_doi <- data_doi("temp_loggers")
+
 # default to 1000 returns next_page link
 check_wa <- page_data(weather_doi, filters = w_filters, api_key = my_api_key)
 check_sa <- page_data(ssts_doi, filters = s_filters, api_key = my_api_key)

### 2021-03-17 R/aims_data.R
added *aims_* to all existing exported functions

@@ -9,8 +9,8 @@
 #' allowed.
 #' @param filters A \code{\link[base]{list}} containing a set of
 #' filters for the data query (see Details)
-#' @param ... Additional arguments to be passed to internal functions
-#' \code{\link{page_data}} and \code{\link{next_page_data}}
+#' @param ... Additional arguments to be passed to non-exported internal
+#' functions \code{\link{page_data}} and \code{\link{next_page_data}}
 #'
 #' @details The AIMS Data Platform R Client provides easy access to
 #' data sets for R applications to the
@@ -33,7 +33,7 @@
 #' A list of arguments for \code{filters} can be exposed for both
 #' [Weather](https://weather.aims.gov.au/#/overview) and
 #' [Sea Water Temperature Loggers](https://weather.aims.gov.au/#/overview)
-#' using function \code{\link{expose_attributes}}.
+#' using function \code{\link{aims_expose_attributes}}.
 #'
 #' Note that at present the user can inspect the range of dates for
 #' the temperature loggers data only (see usage of argument \code{summary} in
@@ -155,26 +155,27 @@
 aims_data <- function(target, filters = NULL, ...) {
   doi <- data_doi(target = target)
   w_doi <- data_doi(target = "weather")
-  allowed <- expose_attributes(target = target)
+  allowed <- aims_expose_attributes(target = target)
   add_args <- list(...)
   if ("summary" %in% names(add_args)) {
     if (doi == w_doi) {
       message("Argument \"summary\" is currently only available",
               " for the temperature logger (\"temp_loggers\") dataset.\n",
-              " Ignoring \"summary\" entry. See details in ?expose_attributes")
+              " Ignoring \"summary\" entry. See details in",
+              " ?aims_expose_attributes")
       add_args$summary <- NA
     }
     if (!all(add_args$summary %in% allowed$summary)) {
       wrong_s <- setdiff(add_args$summary, allowed$summary)
       stop("summary string \"", paste(wrong_s, sep = "; "),
-           "\" not allowed; please check ?expose_attributes")
+           "\" not allowed; please check ?aims_expose_attributes")
     }
   }
   if (!is.null(filters)) {
     if (!all(names(filters) %in% allowed$filters)) {
       wrong_f <- setdiff(names(filters), allowed$filters)
       stop("filter string \"", paste(wrong_f, sep = "; "),
-           "\" not allowed; please check ?expose_attributes")
[…]

### 2021-03-17 R/aims_expose_attributes.R

@@ -66,12 +66,12 @@
 #' @examples
 #' \dontrun{
 #' library(dataaimsr)
-#' expose_attributes("weather")
-#' expose_attributes("temp_loggers")
+#' aims_expose_attributes("weather")
+#' aims_expose_attributes("temp_loggers")
 #' }
 #'
 #' @export
-expose_attributes <- function(target) {
+aims_expose_attributes <- function(target) {
   # used to evaluate input only
   invisible(data_doi(target = target))
   if (target == "temp_loggers") {

### 2021-03-17 R/aims_filter_values.R

@@ -11,7 +11,7 @@
 #' "parameter". See details.
 #'
 #' @details For a full description of each valid filter_name see
-#' ?\code{\link{expose_attributes}}. In the temperature logger dataset,
+#' ?\code{\link{aims_expose_attributes}}. In the temperature logger dataset,
 #' "subsite" is equivalent to "series"; moreover, note that there is only one
 #' parameter being measured (i.e. water temperature), so the "parameter" filter
 #' contains one single value.
@@ -20,7 +20,7 @@
 #' \code{filter_name = "series"}, else a \code{\link[base]{character}}
 #' vector.
 #'
-#' @seealso \code{\link{aims_data}}, \code{\link{expose_attributes}}
+#' @seealso \code{\link{aims_data}}, \code{\link{aims_expose_attributes}}
 #'
 #' @importFrom httr GET http_error
 #'
@@ -29,12 +29,12 @@
 #' @examples
 #' \dontrun{
 #' library(dataaimsr)
-#' filter_values("weather", filter_name = "site")
-#' filter_values("temp_loggers", filter_name = "subsite")
+#' aims_filter_values("weather", filter_name = "site")
+#' aims_filter_values("temp_loggers", filter_name = "subsite")
 #' }
 #'
 #' @export
-filter_values <- function(target, filter_name) {
+aims_filter_values <- function(target, filter_name) {
   doi <- data_doi(target)
   if (length(filter_name) != 1) {
     stop("Argument \"filter_name\" should contain one single value")

### 2021-03-17 R/page_data.R

@@ -12,7 +12,7 @@
 #' @param api_key An AIMS Data Platform
 #' \href{https://open-aims.github.io/data-platform/key-request}{API Key}
 #' @param summary Should summary tables be printed instead of full data?
-#' Details in ?\code{\link{expose_attributes}}
+#' Details in ?\code{\link{aims_expose_attributes}}
 #' @param aims_version A \code{\link[base]{character}} string
 #' defining the version of database. Must be "/v1.0" or "-v2.0".
 #' If none is provided, then "-v2.0" (the most recent) is used.
@@ -20,8 +20,8 @@
 #'
 #' @inherit aims_data details return
 #'
-#' @seealso \code{\link{expose_attributes}}, \code{\link{filter_values}},
-#' \code{\link{aims_data}}
+#' @seealso \code{\link{aims_expose_attributes}},
+#' \code{\link{aims_filter_values}}, \code{\link{aims_data}}
 #'
 #' @author AIMS Datacentre \email{adc@aims.gov.au}
 #'
@@ -63,7 +63,7 @@ page_data <- function(doi, filters = NULL, api_key = NULL,
 #'
 #' @inherit aims_data details return
 #'
-#' @seealso \code{\link{filter_values}}, \code{\link{page_data}},
+#' @seealso \code{\link{aims_filter_values}}, \code{\link{page_data}},
 #' \code{\link{aims_data}}
 #'
 #' @author AIMS Datacentre \email{adc@aims.gov.au}

### 2021-03-17 tests/testthat/test-aims_expose_attributes.R

@@ -1,0 +1,11 @@
+library(dataaimsr)
+
+test_that("Correct structure", {
+  expect_is(aims_expose_attributes("weather"), "list")
+  expect_is(aims_expose_attributes("temp_loggers"), "list")
+  expect_error(aims_expose_attributes("string"))
+  expect_error(aims_expose_attributes(10))
+  expect_error(aims_expose_attributes(FALSE))
+  expect_error(aims_expose_attributes(NA))
+  expect_error(aims_expose_attributes(NULL))
+})

### 2021-03-17 tests/testthat/test-aims_filter_values.R

@@ -1,0 +1,25 @@
+library(dataaimsr)
+
+test_that("Correct structure", {
+  expect_is(aims_filter_values("weather", filter_name = "site"), "character")
+  expect_is(aims_filter_values("weather", filter_name = "series"),
+            "data.frame")
+  expect_is(aims_filter_values("weather", filter_name = "subsite"),
+            "character")
+  expect_is(aims_filter_values("weather", filter_name = "parameter"),
+            "character")
+  expect_is(aims_filter_values("temp_loggers", filter_name = "site"),
+            "character")
+  expect_identical(aims_filter_values("temp_loggers", filter_name = "series"),
+                   aims_filter_values("temp_loggers", filter_name = "subsite"))
+  expect_is(aims_filter_values("temp_loggers", filter_name = "parameter"),
+            "character")
+})
+
+test_that("Wrong inputs", {
+  expect_error(aims_filter_values("string", filter_name = "site"))
+  expect_error(aims_filter_values("string", filter_name = "series_id"))
+  expect_error(aims_filter_values("string", filter_name = "site-name"))
+  expect_error(aims_filter_values("string", filter_name = "site_name"))
+  expect_error(aims_filter_values("temp_loggers"))
+})

### 2021-03-17 tests/testthat/test-expose_attributes.R

@@ -1,11 +1,0 @@
-library(dataaimsr)
-
-test_that("Correct structure", {
-  expect_is(expose_attributes("weather"), "list")
-  expect_is(expose_attributes("temp_loggers"), "list")
-  expect_error(expose_attributes("string"))
-  expect_error(expose_attributes(10))
-  expect_error(expose_attributes(FALSE))
-  expect_error(expose_attributes(NA))
-  expect_error(expose_attributes(NULL))
-})

### 2021-03-17 tests/testthat/test-filter_values.R

@@ -1,21 +1,0 @@
-library(dataaimsr)
-
-test_that("Correct structure", {
-  expect_is(filter_values("weather", filter_name = "site"), "character")
-  expect_is(filter_values("weather", filter_name = "series"), "data.frame")
-  expect_is(filter_values("weather", filter_name = "subsite"), "character")
-  expect_is(filter_values("weather", filter_name = "parameter"), "character")
-  expect_is(filter_values("temp_loggers", filter_name = "site"), "character")
-  expect_identical(filter_values("temp_loggers", filter_name = "series"),
-                   filter_values("temp_loggers", filter_name = "subsite"))
-  expect_is(filter_values("temp_loggers", filter_name = "parameter"),
-            "character")
-})
-
-test_that("Wrong inputs", {
-  expect_error(filter_values("string", filter_name = "site"))
-  expect_error(filter_values("string", filter_name = "series_id"))
-  expect_error(filter_values("string", filter_name = "site-name"))
-  expect_error(filter_values("string", filter_name = "site_name"))
-  expect_error(filter_values("temp_loggers"))
-})

### 2021-03-18 R/aims_data.R
restructured the output of aims_data, implemented new class, and allow it to fail gracefully

@@ -45,22 +45,35 @@
 #' time interval can yield massive datasets. The query will return and error
 #' if it reaches the system's memory capacity.
 #'
-#' @return If \code{summary} is passed as an additional argument (see code
-#' example below), \code{aims_data} returns a \code{\link[base]{data.frame}}
-#' containing the summary information for the dataset (NB: currently,
-#' \code{summary} only works for the temperature logger dataset).
+#' @return \code{aims_data} returns a \code{\link[base]{data.frame}} of class
+#' \code{\link{aimsdf}}.
 #'
-#' Otherwise, if actual data is downloaded, a \code{\link[jsonlite]{fromJSON}}
-#' \code{\link[base]{list}} containing three elements:
+#' If \code{summary} is passed as an additional argument,
+#' the output shows the summary information for the target dataset (i.e.
+#' weather or temperature loggers)
+#' (NB: currently, \code{summary} only works for the temperature logger
+#' database). If \code{summary} is *not* passed as an additional argument, then
+#' the output contains monitoring data.
+#' The output also contains five attributes (empty strings if
+#' \code{summary} is passed as an additional argument):
 #' \itemize{
 #'    \item{\code{metadata}}{a \href{https://www.doi.org/}{DOI} link
 #'          containing the metadata record for the data series.}
 #'    \item{\code{citation}}{the citation information for the particular
 #'          dataset.}
-#'    \item{\code{data}}{an output \code{\link[base]{data.frame}}.}
+#'    \item{\code{parameters}}{The measured parameters comprised in the
+#'          output.}
+#'    \item{\code{type}}{The type of dataset. Either "monitoring" if
+#'          \code{summary} is not specified, or a "summary-by-" otherwise.}
+#'    \item{\code{target}}{The input target.}
 #' }
 #'
 #' @author AIMS Datacentre \email{adc@aims.gov.au}
+#'
+#' @importFrom curl has_internet
+#'
+#' @seealso \code{\link{aims_citation}}, \code{\link{aims_metadata}},
+#' \code{\link{aims_parameters}}
 #'
 #' @examples
 #' \dontrun{
@@ -75,7 +88,7 @@
 #' wdf_a <- aims_data("weather", api_key = NULL,
 #'                    filters = list(site = "Yongala",
 #'                                   from_date = "2018-01-01",
-#'                                   thru_date = "2018-01-02"))$data
+#'                                   thru_date = "2018-01-02"))
 #'
 #' # 2. downloads weather data from all sites
[…]

### 2021-03-18 R/aimsdf-class.R

@@ -1,0 +1,25 @@
+#' Class \code{aimsdf} of data.frame downloaded by the \pkg{dataaimsr} package
+#'
+#' Datasets downloaded by the
+#' \code{\link[dataaimsr:dataaimsr-package]{dataaimsr}} package inherit
+#' the \code{aimsdf} class, which is data.frame with three attributes.
+#'
+#' @name aimsdf-class
+#' @aliases aimsdf
+#' @docType class
+#'
+#' @details
+#' See \code{methods(class = "aimsdf")} for an overview of available methods.
+#'
+#' @seealso \code{\link{aims_data}}
+#'
+NULL
+
+#' Checks if argument is a \code{aimsdf} object
+#'
+#' @param x An \R object
+#'
+#' @export
+is.aimsdf <- function(x) {
+  inherits(x, "aimsdf")
+}

### 2021-03-18 R/aims_citation.R
Added convenience functions to extract most important attributes from aims_data output

@@ -1,0 +1,20 @@
+#' Extracts citation attribute from object of class aimsdf
+#'
+#' Extracts citation attribute from object of class aimsdf
+#'
+#' @param df_ A data.frame of class \code{\link{aimsdf}} created by
+#' function \code{\link{aims_data}}
+#'
+#' @details This function retrieves the citation attribute from an
+#' \code{\link{aimsdf}} object. If the input \code{\link{aimsdf}} object is
+#' a summary data.frame (see ?\code{\link{aims_data}}), then output will be
+#' an empty string.
+#'
+#' @return A \code{\link[base]{character}} vector.
+#'
+#' @author AIMS Datacentre \email{adc@aims.gov.au}
+#'
+#' @export
+aims_citation <- function(df_) {
+  attr(df_, "citation")
+}

### 2021-03-18 R/aims_metadata.R

@@ -1,0 +1,20 @@
+#' Extracts metadata attribute from object of class aimsdf
+#'
+#' Extracts metadata attribute from object of class aimsdf
+#'
+#' @param df_ A data.frame of class \code{\link{aimsdf}} created by
+#' function \code{\link{aims_data}}
+#'
+#' @details This function retrieves the metadata attribute from an
+#' \code{\link{aimsdf}} object. If the input \code{\link{aimsdf}} object is
+#' a summary data.frame (see ?\code{\link{aims_data}}), then output will be
+#' an empty string.
+#'
+#' @return A \code{\link[base]{character}} vector.
+#'
+#' @author AIMS Datacentre \email{adc@aims.gov.au}
+#'
+#' @export
+aims_metadata <- function(df_) {
+  attr(df_, "metadata")
+}

### 2021-03-18 R/aims_parameters.R

@@ -1,0 +1,20 @@
+#' Extracts parameters attribute from object of class aimsdf
+#'
+#' Extracts parameters attribute from object of class aimsdf
+#'
+#' @param df_ A data.frame of class \code{\link{aimsdf}} created by
+#' function \code{\link{aims_data}}
+#'
+#' @details This function retrieves the parameters attribute from an
+#' \code{\link{aimsdf}} object. If the input \code{\link{aimsdf}} object is
+#' a summary data.frame (see ?\code{\link{aims_data}}), then output will be
+#' an empty string.
+#'
+#' @return A \code{\link[base]{character}} vector.
+#'
+#' @author AIMS Datacentre \email{adc@aims.gov.au}
+#'
+#' @export
+aims_parameters <- function(df_) {
+  attr(df_, "parameters")
+}

### 2021-03-18 R/aimsdf-methods.R
print, summary, plot, head, tail are now extended to aimsdf class

@@ -1,0 +1,248 @@
+#' summary.aimsdf
+#'
+#' @param object An object of class \code{\link{aimsdf}} as
+#' returned by \code{\link{aims_data}}.
+#' @param ... Unused.
+#'
+#' @return A list containing summary info from the input data.frame.
+#'
+#' @export
+summary.aimsdf <- function(object, ...) {
+  x <- list(
+    cit = aims_citation(object),
+    met = aims_metadata(object),
+    pars = aims_parameters(object),
+    dim = dim(object),
+    type = attr(object, "type"),
+    target = attr(object, "target"),
+    hdf = head(data.frame(object))
+  )
+  target <- make_pretty_data_label(x$target)
+  if (grepl("summary", x$type)) {
+    x$type <- capitalise(x$type)
+    cat(paste0(x$type, " from the ", target, " dataset"), sep = "")
+    target
+    cat("\n\n")
+    cat("A data.frame with ", x$dim[1], " observations and ", x$dim[2],
+        " variables:\n", sep = "")
+    print(x$hdf)
+    cat("...\n")
+  } else {
+    cat(paste0(target,
+               " ", x$type, " data containing the following attributes:\n"),
+        paste0("  - citation: ", x$cit, "\n"),
+        paste0("  - metadata: ", x$met, "\n"),
+        paste0("  - parameters: ", paste0(x$pars, collapse = "; ")),
+        sep = "")
+    cat("\n\n")
+    cat("A data.frame with ", x$dim[1], " observations and ", x$dim[2],
+        " variables:\n", sep = "")
+    print(x$hdf)
+    cat("...\n")
+  }
+  invisible(x)
+}
+
+#' print.aimsdf
+#'
+#' @param x An object of class \code{\link{aimsdf}} as
+#' returned by \code{\link{aims_data}}.
+#' @param ... Not used.
+#'
+#' @return A list containing a summary of the model fit as returned a
+#' brmsfit for each model.
+#'
+#' @export
+print.aimsdf <- function(x, ...) {
+  NextMethod()
+}
+
+#' head.aimsdf
+#'
+#' @param x An object of class \code{\link{aimsdf}} as
+#' returned by \code{\link{aims_data}}.
+#' @param ... Not used.
+#'
+#' @export
+head.aimsdf <- function(x, ...) {
+  NextMethod()
+}
+
+#' tail.aimsdf
+#'
+#' @param x An object of class \code{\link{aimsdf}} as
[…]

### 2021-03-18 tests/testthat/test-aims_data.R
updated tests for aims_data

@@ -11,42 +11,32 @@ check_sb <- aims_data("temp_loggers", filters = s_filters_b,
                       api_key = my_api_key)
 
 test_that("Correct structure", {
-  expect_is(check_wa, "list")
-  expect_length(check_wa, 3)
-  expect_true(all(c("metadata", "citation", "data") %in% names(check_wa)))
-  expect_is(check_sa, "list")
-  expect_length(check_sa, 3)
-  expect_true(all(c("metadata", "citation", "data") %in% names(check_sa)))
-  expect_is(check_wb, "list")
-  expect_length(check_wb, 3)
-  expect_true(all(c("metadata", "citation", "data") %in% names(check_wb)))
-  expect_is(check_sb, "list")
-  expect_length(check_sb, 3)
-  expect_true(all(c("metadata", "citation", "data") %in% names(check_sb)))
+  expect_is(check_wa, "data.frame")
+  expect_true(all(c("metadata", "citation", "parameters") %in%
+                      names(attributes(check_wa))))
+  expect_is(check_sa, "data.frame")
+  expect_true(all(c("metadata", "citation", "parameters") %in%
+                      names(attributes(check_sa))))
+  expect_is(check_wb, "data.frame")
+  expect_true(all(c("metadata", "citation", "parameters") %in%
+                      names(attributes(check_wb))))
+  expect_is(check_sb, "data.frame")
+  expect_true(all(c("metadata", "citation", "parameters") %in%
+                      names(attributes(check_sb))))
 })
 
 check_wc <- aims_data("weather", filters = w_filters_c, api_key = my_api_key)
 check_wd <- aims_data("weather", filters = w_filters_d, api_key = my_api_key)
-check_sc <- aims_data("temp_loggers", filters = s_filters_c, api_key = my_api_key)
-check_sd <- aims_data("temp_loggers", filters = s_filters_d, api_key = my_api_key)
+check_sc <- aims_data("temp_loggers", filters = s_filters_c,
+                      api_key = my_api_key)
+check_sd <- aims_data("temp_loggers", filters = s_filters_d,
+                      api_key = my_api_key)
 
 test_that("Wrong filters", {
-  expect_is(check_wc, "list")
-  expect_length(check_wc, 3)
-  expect_true(all(c("metadata", "citation", "data") %in% names(check_wc)))
-  expect_null(nrow(check_wc$data))
-  expect_is(check_wd, "list")
[…]

### 2021-03-18 R/aims_filter_values.R
allow filter_values to fail gracefully without proper internet connection

@@ -23,6 +23,7 @@
 #' @seealso \code{\link{aims_data}}, \code{\link{aims_expose_attributes}}
 #'
 #' @importFrom httr GET http_error
+#' @importFrom curl has_internet
 #'
 #' @author AIMS Datacentre \email{adc@aims.gov.au}
 #'
@@ -35,6 +36,11 @@
 #'
 #' @export
 aims_filter_values <- function(target, filter_name) {
+  if (!has_internet()) {
+    message("It seems that your internet connection is down. You need an ",
+            "internet connection to successfully download AIMS data.")
+    return(invisible())
+  }
   doi <- data_doi(target)
   if (length(filter_name) != 1) {
     stop("Argument \"filter_name\" should contain one single value")

### 2021-03-18 README.Rmd
moved API Key section inside the installation instruction

@@
 
-## Requesting an AIMS Data Platform API Key
+## Installation
+
+### Requesting an AIMS Data Platform API Key
 
@@
 The API Key can be passed to the package functions as an additional
-`api_key = "XXXX"` argument. alternatively, the environment variable
-`AIMS_DATAPLATFORM_API_KEY` can be stored in the user's `.Renviron` file for
-automatic loading at the start of an R session. In that case the users can 
-modify their `.Renviron` file by adding the following line:
+`api_key = "XXXX"` argument. **However**, we strongly encourage users to
+maintain their API key as a private locally hidden environment variable
+(`AIMS_DATAPLATFORM_API_KEY`) in the `.Renviron` file for
+automatic loading at the start of an R session. Please read this
+[article](https://CRAN.R-project.org/package=httr/vignettes/secrets.html)
+which details why keeping your API private is extremely important.
+
+Users can modify their `.Renviron` file by adding the following line:
 
@@
 
-## Installation
+### Package
 
-At this stage `dataaimsr` is not hosted on CRAN R package network.
-An alternative method of installation is to use the R `remotes` package.
-
-R `remotes` can be installed using the following command:
+At this stage `dataaimsr` is not hosted on CRAN R package network, although
+we re aiming to submit it there very soon. For the moment, an alternative
+method of installation is to use the R `remotes` package. R `remotes` can be
+installed using the following command:
 

### 2021-03-18 README.Rmd
added two examples for usage under README

@@
 
-Examples about how to navigate `dataaimsr` and interrogate the datasets can
-be found on our [online vignettes][4].
+```{r, eval = FALSE}
+# assumes that user already has API key saved to
+# .Renviron
+library(dataaimsr)
+
+# summarised by series
+# for all sites that contain data
+# within a defined date range
+sdf_b <- aims_data("temp_loggers", api_key = NULL,
+                   summary = "summary-by-series",
+                   filters = list("from_date" = "2018-01-01",
+                                  "thru_date" = "2018-12-31"))
+
+# downloads weather data from site Yongala
+# within a defined date range
+wdf_a <- aims_data("weather", api_key = NULL,
+                   filters = list(site = "Yongala",
+                                  from_date = "2018-01-01",
+                                  thru_date = "2018-01-02"))
+```
+
+More comprehensive examples about how to navigate `dataaimsr` and interrogate
+the datasets can be found on our [online vignettes][4].
 

### 2021-03-18 README.Rmd
tweaks to overview in readme

@@
 and a few convenience functions to interrogate and understand the datasets
-that are available to download.
+that are available to download. In doing so, it allows the user to
+fully explore these datasets in R in whichever capacity they want (e.g.
+data visualisation, statistical analyses, etc). The package itself contains
+a `plot` method which allows the user to plot summaries of the different types
+of dataset made available by the API. Below we provide a brief context about
+the existing [Datasets][#datasets] that can be explored through `dataaimsr`.
 
 [1]: https://open-aims.github.io/data-platform/
-
-Currently, there are two AIMS long-term monitoring datasets available to be
-downloaded through `dataaimsr`:
-
-### Northern Australia Automated Marine Weather And Oceanographic Stations
-
-Automatic weather stations have been deployed by AIMS since 1980. Most of the
-stations are along the Great Barrier Reef (GBR) including the Torres Strait in
-North-Eastern Australia but there is also a station in Darwin and one at
-Ningaloo Reef in Western Australia. Many of the stations are located on the
-reef itself either on poles located in the reef lagoon or on tourist pontoons
-or other structures. A list of the weather stations which have been deployed
-by AIMS and the period of time for which data may be available can be
-found on the [metadata][2] webpage. **NB:** Records may not be continuous for
-the time spans given.
-
-[2]: https://apps.aims.gov.au/metadata/view/0887cb5b-b443-4e08-a169-038208109466
-
-### AIMS Sea Water Temperature Observing System (AIMS Temperature Logger Program)
-
-The data provided here are from a number of sea water temperature monitoring
-programs conducted in tropical and subtropical coral reefs environments around
-Australia. Data are available from approximately 80 GBR sites, 16 Coral Sea
-sites, 7 sites in North West Western Australia (WA), 8 Queensland regional
-ports, 13 sites in the Solitary Islands, 4 sites in Papua New Guinea and 10
-sites in the Cocos (Keeling) Islands. Data are obtained from in-situ data
-loggers deployed on the reef. Temperature instruments sample water
-temperatures every 5-10 minutes (typically) and are exchanged and downloaded
-approximately every 12 months. Temperature loggers on the reef-flat are
-generally placed just below Lowest Astronomical Tide level. Reef-slope (or
-where specified as Upper reef-slope) generally refers to depths 5--9 m while
-Deep reef-slope refers to depths of ~20 m. For more information on the dataset
-and its usage, please visit the [metadata][3] webpage.
-
-[3]: https://apps.aims.gov.au/metadata/view/4a12a8c0-c573-11dc-b99b-00008a07204e
 
@@
 
+## Datasets
+
+Currently, there are two AIMS long-term monitoring datasets available to be
+downloaded through `dataaimsr`:
+
+### Northern Australia Automated Marine Weather And Oceanographic Stations
+
+Automatic weather stations have been deployed by AIMS since 1980. Most of the
+stations are along the Great Barrier Reef (GBR) including the Torres Strait in
+North-Eastern Australia but there is also a station in Darwin and one at
+Ningaloo Reef in Western Australia. Many of the stations are located on the
+reef itself either on poles located in the reef lagoon or on tourist pontoons
+or other structures. A list of the weather stations which have been deployed
+by AIMS and the period of time for which data may be available can be
+found on the [metadata][2] webpage. **NB:** Records may not be continuous for
+the time spans given.
+
+[2]: https://apps.aims.gov.au/metadata/view/0887cb5b-b443-4e08-a169-038208109466
+
+### AIMS Sea Water Temperature Observing System (AIMS Temperature Logger Program)
+
+The data provided here are from a number of sea water temperature monitoring
+programs conducted in tropical and subtropical coral reefs environments around
+Australia. Data are available from approximately 80 GBR sites, 16 Coral Sea
+sites, 7 sites in North West Western Australia (WA), 8 Queensland regional
+ports, 13 sites in the Solitary Islands, 4 sites in Papua New Guinea and 10
+sites in the Cocos (Keeling) Islands. Data are obtained from in-situ data
+loggers deployed on the reef. Temperature instruments sample water
+temperatures every 5-10 minutes (typically) and are exchanged and downloaded
+approximately every 12 months. Temperature loggers on the reef-flat are
+generally placed just below Lowest Astronomical Tide level. Reef-slope (or
+where specified as Upper reef-slope) generally refers to depths 5--9 m while
+Deep reef-slope refers to depths of ~20 m. For more information on the dataset
+and its usage, please visit the [metadata][3] webpage.
+
+[3]: https://apps.aims.gov.au/metadata/view/4a12a8c0-c573-11dc-b99b-00008a07204e
+
 ## License

### 2021-03-18 R/aimsdf-methods.R
sent helpers from methods to helpers files, updated test, added tests for methods

@@ -129,12 +129,12 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
               " instead")
     }
     map_bd <- ne_countries(continent = "oceania", returnclass = "sf") %>%
-      st_transform(crs = 4326)
+      st_transform(crs = 3112)
     y <- x %>%
       mutate(cols = cal_obs * 1e-3) %>%
       drop_na(lon, lat) %>%
       st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
-      st_transform(crs = 4326)
+      st_transform(crs = 3112)
     p_bkg <- make_pretty_colour("lightblue")
     name_leg <- "# Calibrated obs. (thousands)"
     ggplot(data = map_bd) +
@@ -173,7 +173,7 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
               axis.title.y = element_text(size = 12))
     } else if (ptype == "map") {
       map_bd <- ne_countries(continent = "oceania", returnclass = "sf") %>%
-        st_transform(crs = 4326)
+        st_transform(crs = 3112)
       y_l <- x %>%
         group_by(site) %>%
         summarise(n_obs = length(qc_val), lon = unique(lon),
@@ -183,7 +183,7 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
         drop_na(lon, lat)
       y_p <- y_l %>%
         st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
-        st_transform(crs = 4326)
+        st_transform(crs = 3112)
       y_l <- y_l %>%
         mutate(lon = extract_map_coord(y_p$geometry, 1),
                lat = extract_map_coord(y_p$geometry, 2))
@@ -204,49 +204,4 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
                                        label = par_l))
     }
   }
-}
-
-#' make_pretty_data_label
-#'
-#' Internal
-#'
-#' @param x A character
-#' @keywords internal
-make_pretty_data_label <- function(x) {
-  ifelse(x == "weather", "Weather Station", "Temperature loggers")
-}
-
-#' make_pretty_colour
-#'
-#' Internal
-#'
-#' @param x A character
-#' @param alpha_ A numeric
-#'
-#' @importFrom grDevices col2rgb rgb
-#' @keywords internal
-make_pretty_colour <- function(x, alpha_ = 0.55) {
[…]

### 2021-03-18 R/helpers.R

@@ -174,3 +174,48 @@ data_doi <- function(target) {
   }
   getOption(paste0("dataaimsr.", target))
 }
+
+#' make_pretty_data_label
+#'
+#' Internal
+#'
+#' @param x A character
+#' @keywords internal
+make_pretty_data_label <- function(x) {
+  ifelse(x == "weather", "Weather Station", "Temperature loggers")
+}
+
+#' make_pretty_colour
+#'
+#' Internal
+#'
+#' @param x A character
+#' @param alpha_ A numeric
+#'
+#' @importFrom grDevices col2rgb rgb
+#' @keywords internal
+make_pretty_colour <- function(x, alpha_ = 0.55) {
+  col <- col2rgb(x)
+  rgb(col[1], col[2], col[3], alpha = alpha_ * 255, maxColorValue = 255)
+}
+
+#' capitalise
+#'
+#' Internal
+#'
+#' @param x A character
+#' @keywords internal
+capitalise <- function(x) {
+  paste0(toupper(substr(x, 1, 1)), substr(x, 2, nchar(x)))
+}
+
+#' extract_map_coord
+#'
+#' Internal
+#'
+#' @param x An sfc_POINT
+#' @param ... Additional argument "pos" to internal function
+#' @keywords internal
+extract_map_coord <- function(x, ...) {
+  sapply(x, function(z, pos)z[[pos]], ...)
+}

### 2021-03-18 tests/testthat/test-aims_data.R

@@ -23,6 +23,10 @@ test_that("Correct structure", {
   expect_is(check_sb, "data.frame")
   expect_true(all(c("metadata", "citation", "parameters") %in%
                       names(attributes(check_sb))))
+  expect_s3_class(check_wa, "aimsdf")
+  expect_s3_class(check_sa, "aimsdf")
+  expect_s3_class(check_wb, "aimsdf")
+  expect_s3_class(check_sb, "aimsdf")
 })
 
 check_wc <- aims_data("weather", filters = w_filters_c, api_key = my_api_key)

### 2021-03-18 tests/testthat/test-aimsdf-methods.R

@@ -1,0 +1,69 @@
+library(dataaimsr)
+
+# regular monitoring data
+check_wa <- aims_data("weather", filters = w_filters, api_key = my_api_key)
+check_sa <- aims_data("temp_loggers", filters = s_filters,
+                      api_key = my_api_key)
+# summary data
+sdf_s <- aims_data("temp_loggers", api_key = my_api_key,
+                   summary = "summary-by-series")
+sdf_d <- aims_data("temp_loggers", api_key = my_api_key,
+                   summary = "summary-by-deployment")
+
+test_that("Correct structure", {
+  expect_output(expect_is(summary(check_wa), "list"))
+  expect_output(expect_is(summary(check_sa), "list"))
+  expect_output(expect_is(summary(sdf_s), "list"))
+  expect_output(expect_is(summary(sdf_d), "list"))
+})
+
+test_that("Correct structure", {
+  expect_output(print(check_wa))
+  expect_output(print(check_sa))
+  expect_output(print(sdf_s))
+  expect_output(print(sdf_d))
+  expect_s3_class(head(check_wa), "aimsdf")
+  expect_is(head(check_wa), "data.frame")
+  expect_s3_class(head(check_sa), "aimsdf")
+  expect_is(head(check_sa), "data.frame")
+  expect_s3_class(head(sdf_s), "aimsdf")
+  expect_is(head(sdf_s), "data.frame")
+  expect_s3_class(head(sdf_d), "aimsdf")
+  expect_is(head(sdf_d), "data.frame")
+  expect_s3_class(tail(check_wa), "aimsdf")
+  expect_is(tail(check_wa), "data.frame")
+  expect_s3_class(tail(check_sa), "aimsdf")
+  expect_is(tail(check_sa), "data.frame")
+  expect_s3_class(tail(sdf_s), "aimsdf")
+  expect_is(tail(sdf_s), "data.frame")
+  expect_s3_class(tail(sdf_d), "aimsdf")
+  expect_is(tail(sdf_d), "data.frame")
+})
+
+a_ <- plot(check_wa, ptype = "map")
+b_ <- plot(check_wa, ptype = "time_series")
+c_ <- plot(sdf_s, ptype = "map")
+d_ <- plot(sdf_d, ptype = "time_series")
+
+test_that("Correct structure", {
+  expect_error(plot(check_wa))
+  expect_error(plot(check_sa))
+  expect_error(plot(sdf_s))
+  expect_error(plot(sdf_d))
[…]

### 2021-03-18 tests/testthat/test-helpers.R

@@ -16,6 +16,7 @@ json_out <- json_results(good_dt_req)
 test_that("API key finder", {
   expect_error(find_api_key())
   expect_is(find_api_key(my_api_key), "character")
+  key_ <- Sys.getenv("AIMS_DATAPLATFORM_API_KEY")
   Sys.setenv(AIMS_DATAPLATFORM_API_KEY = "empty")
   expect_is(find_api_key(NULL), "character")
   expect_identical(find_api_key(NULL), "empty")
@@ -23,6 +24,7 @@ test_that("API key finder", {
   expect_identical(find_api_key(10), 10)
   expect_identical(find_api_key(NA), NA)
   expect_identical(find_api_key("something"), "something")
+  Sys.setenv(AIMS_DATAPLATFORM_API_KEY = key_)
 })
 
 test_that("http error handling", {
@@ -94,4 +96,36 @@ test_that("Correct structure", {
   expect_error(data_doi(FALSE))
   expect_error(data_doi(NA))
   expect_error(data_doi(NULL))
+})
+
+test_that("Correct structure", {
+  expect_identical(make_pretty_data_label("weather"), "Weather Station")
+  expect_identical(make_pretty_data_label("temp_loggers"),
+                   "Temperature loggers")
+  expect_identical(make_pretty_data_label(10),
+                   "Temperature loggers")
+  expect_identical(make_pretty_data_label(TRUE),
+                   "Temperature loggers")
+  expect_identical(make_pretty_data_label(NA), NA)
+  expect_vector(make_pretty_data_label(NULL))
+})
+
+test_that("Correct structure", {
+  expect_identical(make_pretty_colour("blue"), "#0000FF8C")
+  expect_identical(make_pretty_colour(NA), "#FFFFFF8C")
+  expect_error(make_pretty_colour(NA, NA))
+})
+
+test_that("Correct structure", {
+  expect_identical(capitalise("abc"), "Abc")
+  expect_identical(capitalise(NA), "NANA")
+  expect_vector(capitalise(NULL))
+})
+
+my_list <- list(a = list(k = 1, l = 2), b = list(k = "A", l = "b"))
+test_that("Correct structure", {
+  expect_identical(unname(extract_map_coord(my_list, 1)), c("1", "A"))
+  expect_identical(unname(extract_map_coord(my_list, 2)), c("2", "b"))
+  expect_is(extract_map_coord(my_list, NA), "list")
+  expect_null(extract_map_coord(my_list, NA)[[1]])
 })

### 2021-03-18 paper/paper.Rmd
updated paper text and map

@@
     affiliation: "3"
+  - name: Duncan Fermor
+    affiliation: "3"
+  - name: Eduardo Klein
+    affiliation: "3"
+  - name: Tobias Robinson
+    affiliation: "3"
+  - name: Jason Smith
+    affiliation: "3"
   - name: Jeffrey L. Sheehan
     affiliation: "3"
-  - name: Duncan Fermor
+  - name: Shannon Dowley
+    affiliation: "3"
+  - name: Dean Ditton
+    affiliation: "3"
+  - name: Kevin Gunn
+    affiliation: "3"
+  - name: Gavin Ericson
     affiliation: "3"
@@
 and a few convenience functions to interrogate and understand the datasets
-that are available to download.
+that are available to download. In doing so, it allows the user to
+fully explore these datasets in R in whichever capacity they want (e.g.
+data visualisation, statistical analyses, etc). The package itself contains
+a `plot` method which allows the user to plot summaries of the different types
+of dataset made available by the API.
 
@@
 Before loading the package, a user needs to download and store their personal
-[AIMS Data Platform API Key][4]---we recommend it storing it in `.Renviron`.
+[AIMS Data Platform API Key][4]---we strongly encourage users to
+maintain their API key as a private, locally hidden environment variable
+(`AIMS_DATAPLATFORM_API_KEY`) in the `.Renviron` file for
+automatic loading at the start of an R session.
 
 [4]: https://open-aims.github.io/data-platform/key-request
+
+`dataaimsr` imports the packages *httr* [@httrcit], *jsonlite* [@jsonlitecit],
+*parsedate* [@parsedatecit], *dplyr* [@dplyrcit], *tidyr* [@tidyrcit],
+*rnaturalearth* [@rnaturalearthcit], *sf* [@sfcit], *ggplot2* [@ggplot2cit],
+*ggrepel* [@ggrepelcit] and *curl* [@curlcit].
 
@@
 The first step would be to visualise the dataset. We do this by
-mapping all available sites. First we need to store the DOI for the
-target dataset---this is done via the function `aims_data_doi`. We
-can then download the summary information for the Sea Water Temperature 
-Loggers dataset using the main function called `aims_data`:
+mapping all available sites. For example, we download the summary information
+for the Sea Water Temperature Loggers dataset using the main function called
+`aims_data`:
 
@@
 library(dataaimsr)
-# see ?aims_data_doi for argument names
-ssts_doi <- aims_data_doi("temp_loggers")
-sdata <- aims_data(ssts_doi, api_key = NULL,
+sdata <- aims_data("temp_loggers", api_key = NULL,
                    summary = "summary-by-series")
@@
 visualise `summary-by-series` or `summary-by-deployment`. The output of
-`aims_data` when summary is `NA` (the default) is a `data.frame`.
+`aims_data` is a `data.frame` of class `aimsdf`.
 
@@
 respectively stand for uncalibrated, calibrated, and quality-controlled 
-observations. **Mark, we need a few sentences explaining the quality control**
-**procdure**. One can visualise this data, for instance, by plotting them
+observations. Calibrated and quality-controlled are generally the same.
+Instruments are routinely calibrated (mostly once a year) in a temperature-controlled water bath and corrections applied to the data. After
+calibration, all data records are quality controlled based on the following
+tests: 1) clip to in-water only data, using deployment's metadata, 2)
+impossible value check: data outside a fixed temperature range (14˚C – 40˚C)
+is flagged as bad data, 3) spike test: individual extreme values are flagged
+as probably bad according to the algorithm presented in @morelo2014methods and
+4) Excessive gradient test: pairs of data that present a sudden change in the
+slope are flagged as probably bad [@toma2016acta]. If any data record fails at
+least one of the tests, a QC flag equal to 2 is returned, otherwise, the QC
+flag is set to 1.
+
+One can visualise this data, for instance, by plotting them
 on a map of Australia, while colouring based on the total amount of calibrated
@@
 
+`aimsdf` objects can be plotted using the `plot` function. For summary data
+such as `sdata`, plot will always generate a map with the points around
+Australia and associated regions, coloured by the number of calibrated
+observations:
+
 ```{r echo = FALSE, eval = FALSE}
-library(tidyverse)
-library(ggmap)
-sdata <- sdata %>%
-  dplyr::mutate(cols = cal_obs * 1e-3) %>%
-  tidyr::drop_na(lon, lat)
-lab <- expression(atop("# Calibrated obs.",
-                       paste("(" %*% 10^3, ")")))
-ozmap <- ggmap::get_stamenmap(bbox = c(left = 94, bottom = -45,
-                                       right = 162, top = 0),
-                              zoom = 4, maptype = "watercolor")
-out <- ggmap::ggmap(ozmap) +
-  theme_void() +
-  geom_point(data = sdata,
-             mapping = aes(x = lon, y = lat,
-                           colour = cols,
-                           fill = cols),
-             shape = 16, alpha = 0.8) +
-  scale_colour_gradient(name = lab,
-                        low = "dodgerblue4",
-                        high = "darkred") +
-  scale_fill_gradient(name = lab,
-                      low = "dodgerblue4",
-                      high = "darkred")
+out <- plot(sdata, ptype = "map")
 ggsave("paper/summary.png", out, width = 7, height = 4.36, units = "in",
@@
 In the case of the Weather Station dataset, the user can call a
-the `filter_values` function which allows one to query what
+the `aims_filter_values` function which allows one to query what
 sites, series and parameters are available for both datasets:
@@
 ```{r, message = FALSE, warning = FALSE}
-weather_doi <- aims_data_doi("weather")
-filter_values(weather_doi, filter_name = "series") %>%
+aims_filter_values("weather", filter_name = "series") %>%
   head()
@@
 master the navigation and download of AIMS monitoring datasets. Each 
-dataset can filtered by attributes which can be exposed with the function `expose_attributes`:
+dataset can filtered by attributes which can be exposed with the function
+`aims_expose_attributes`:
 
 ```{r, message = FALSE, warning = FALSE}
-expose_attributes(weather_doi)
-expose_attributes(ssts_doi)
+aims_expose_attributes("weather")
+aims_expose_attributes("temp_loggers")
 ```
 
-The help file (see `?expose_attributes`) contains the details about what
+The help file (see `?aims_expose_attributes`) contains the details about what
 each filter targets. So, having an understanding of the summaries and what
@@
 ```{r, message = FALSE, warning = FALSE}
-wdata_a <- aims_data(weather_doi, api_key = NULL,
+wdata_a <- aims_data("weather", api_key = NULL,
                      filters = list(site = "Yongala",
@@
 
-The output of `aims_data` when summary is omitted (the default) is a list
-containing three elements:
+The returned `aimsdf` object in this case has attributes which give us
+summary crucial information:
 
@@
 
-- `data` an output `data.frame`
+- `parameters` an output `data.frame`
+
+These can be directly extracted using the convenience functions
+`aims_metadata`, `aims_citation` and `aims_parameters`, e.g.:
 
 ```{r}
-wdata_a$metadata
+aims_metadata(wdata_a)
 ```
 
-```{r}
-wdata_a$citation
-```
-
-```{r}
-head(wdata_a$data)
-```
-
-Note that there are numerous parameters available for this site at the
-specified time:
-
-```{r}
-unique(wdata_a$data$parameter)
-```
-
-And the actual measurements are either raw or quality-controlled (Fig. \@ref(fig:wind)).
+This example data contains multiple parameters available for this site at the
+specified time, and the actual measurements are either raw or
+quality-controlled. For monitoring data (i.e. when `summary = NA` in a
+`aims_data` call), we can either visualise the data as a time series broken
+down by parameter, or a map showing the sites with some summary info. If the
+parameters are not specified, then `dataaimsr` will plot a maximum of 4
+parameters chosen at random for a time series plot. Alternatively the user can
+specify which parameters are to be plotted (Fig. \@ref(fig:wind)).
 
 ```{r echo = FALSE, eval = FALSE}
-out <- wdata_a$data %>%
-  dplyr::filter(grepl("Wind Speed", parameter)) %>%
-  ggplot(data = .) +
-    geom_line(aes(x = time, y = qc_val, colour = parameter)) +
-    labs(x = "Date",
-         y = "Wind speed (km / h)",
-         colour = "Site",
-         title = "AIMS Weather stations",
-         subtitle = "Yongala (2018)") +
-    theme_bw()
-ggsave("paper/wind.png", out, width = 7.4, height = 5.2, units = "in",
+# check parameters with aims_parameters(wdata_a)
+out <- plot(wdata_a, ptype = "time_series",
+            pars = c("Water Pressure", "Chlorophyll"))
+ggsave("paper/wind.png", out, width = 8.5, height = 3.9, units = "in",
        device = "png", dpi = 300)
@@
 
-(ref:fig-wind) Yongala wreck wind speed profiles between the first and second of January 2018.
+(ref:fig-wind) Yongala wreck profiles for water pressure and chlorophyll-a between the first and second of January 2018.
 
@@
 ```{r, message = FALSE, warning = FALSE}
-wdata_b <- aims_data(weather_doi,
-                     api_key = NULL,
+wdata_b <- aims_data("weather", api_key = NULL,
                      filters = list(series_id = 64,
                                     from_date = "1991-10-18T06:00:00",
-                                    thru_date = "1991-10-18T12:00:00"))$data
+                                    thru_date = "1991-10-18T12:00:00"))
 range(wdata_b$time)
+```
+
+### Methods
+
+Objects of class `aimsdf` have associated `plot`, `print` and `summary`
+methods.
+
+### Data citation
+
+Whenever using `dataaimsr`, we ask the user to not only cite this paper, but
+also any data used in an eventual publication. Citation data can be extracted
+from a dataset using the function `aims_citation`:
+
+```{r, message = FALSE, warning = FALSE}
+aims_citation(wdata_b)
+```
+
+## Sister web tool
+
+The Time Series Explorer (https://apps.aims.gov.au/ts-explorer/) is an
+interactive web-based application that visualises large time series datasets.
+The application utilises the AIMS Data Platform API to dynamically query data
+according to user selection and visualise the data as line graphs. Series are
+able to be compared visually. For large series, data are aggregated to daily
+averages and displayed as minimum, maximum and mean. When the user 'zooms in'
+sufficiently, the data will be displayed as non-aggregate values
+(Fig. \@ref(fig:tssa)). This technique is being used to ensure the application
+performs well with large time series.
+
+(ref:fig-tssa) Interactive discovery and visualisation of data series.
+
+```{r tssa, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-tssa)", cache = TRUE}
+knitr::include_graphics("tssa.png")
+```
+
+The user can then download the displayed data as CSV or obtain a R code
+snippet that shows how to obtain the data using the dataaimsr package
+(Fig. \@ref(fig:tssb)). In this way, a user can easily explore and discover
+datasets and then quickly and easily have this data in their R environment for
+additional analysis.
+
+(ref:fig-tssb) Download/Export displayed data via R snippet.
+
+```{r tssb, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-tssb)", cache = TRUE}
+knitr::include_graphics("tssb.png")
 ```
@@
 
-# Acknowledgements
-
-The development of `dataimsr` was supported by ... Names to be added to the list.
+The API is still a work in progress. We are working on ways to better
+facilitate data visualisation and retrieval, and also we are trying to
+standardise the outputs from the different datasets as much as possible. In the
+future, we envision that `dataaimsr` will also provide access to other
+monitoring datasets collected by AIMS.
 

### 2021-03-29 README.Rmd
updated relevant links to ropensci

@@
 [![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
-[![R build status](https://github.com/open-AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/open-AIMS/dataaimsr/actions)
-[![Codecov test coverage](https://codecov.io/gh/open-AIMS/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/open-AIMS/dataaimsr?branch=master)
-![pkgdown](https://github.com/open-AIMS/dataaimsr/workflows/pkgdown/badge.svg)
+[![R build status](https://github.com/ropensci/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/dataaimsr/actions)
+[![Codecov test coverage](https://codecov.io/gh/ropensci/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/dataaimsr?branch=master)
+![pkgdown](https://github.com/ropensci/dataaimsr/workflows/pkgdown/badge.svg)
 [![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
@@
 [![Ask Us Anything
-\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/open-AIMS/dataaimsr/issues/new)
+\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/ropensci/dataaimsr/issues/new)
 ![Open Source
@@
 ```{r, eval = FALSE}
-remotes::install_github("https://github.com/open-AIMS/dataaimsr")
+remotes::install_github("https://github.com/ropensci/dataaimsr")
 ```
@@
 
-[4]: https://open-AIMS.github.io/dataaimsr/articles
+[4]: https://ropensci.github.io/dataaimsr/articles
 

### 2021-03-31 README.Rmd
new code of conduct on README
Installation instructions following pkg targets

@@
 
-At this stage `dataaimsr` is not hosted on CRAN R package network, although
-we re aiming to submit it there very soon. For the moment, an alternative
-method of installation is to use the R `remotes` package. R `remotes` can be
-installed using the following command:
-
-```{r, eval = FALSE}
-install.packages("remotes")
-```
-
-After `remotes` has been installed `dataaimsr` can be installed directly from
-GitHub using the following command:
-
-```{r, eval = FALSE}
-remotes::install_github("https://github.com/ropensci/dataaimsr")
-```
-
-This command will also install the three package dependencies: `httr`,
-`jsonlite` and `parsedate`.
+Type | Source | Command
+---|---|---
+Release | CRAN | Not yet available
+Development | GitHub | `remotes::install_github("ropensci/dataaimsr")`
+Development | rOpenSci | `install.packages("dataaimsr", repos = "https://dev.ropensci.org")`
 
@@
 
+## Code of Conduct
+
+Please note that this package is released with a
+[Contributor Code of Conduct](https://ropensci.org/code-of-conduct/).
+By contributing to this project, you agree to abide by its terms.
+
 ## AIMS R package logos

### 2021-05-24 paper/paper.Rmd
removed dplyr pipe from paper Rmd
renamed statement of need, and cut down on some parts of the paper in order to address openjournals/joss-reviews#3258

@@
 
-# Background and Statement of need
+# Statement of Need
 
@@
 Currently, there are two AIMS long-term monitoring datasets available to be
-downloaded through `dataaimsr`:
-
-### Northern Australia Automated Marine Weather And Oceanographic Stations
-
-Automatic weather stations have been deployed by AIMS since 1980. Most of the
-stations are along the Great Barrier Reef (GBR) including the Torres Strait in
-North-Eastern Australia but there is also a station in Darwin and one at
-Ningaloo Reef in Western Australia. Many of the stations are located on the
-reef itself either on poles located in the reef lagoon or on tourist pontoons
-or other structures. A list of the weather stations which have been deployed
-by AIMS and the period of time for which data may be available can be
-found on the [AIMS metadata][2] webpage. **NB:** Records may not be continuous
-for the time spans given.
+downloaded through `dataaimsr`: 1) the Northern Australia Automated Marine
+Weather And Oceanographic Stations---a list of the weather stations which have
+been deployed by AIMS and the period of time for which data may be available
+can be found on the [AIMS metadata][2] webpage; 2) AIMS Sea Water Temperature Observing System (AIMS Temperature Logger Program)---for more information on
+the dataset and its usage, please visit the [AIMS metadata][3] webpage.
 
 [2]: https://apps.aims.gov.au/metadata/view/0887cb5b-b443-4e08-a169-038208109466
-
-### AIMS Sea Water Temperature Observing System (AIMS Temperature Logger Program)
-
-The data provided here are from a number of sea water temperature monitoring
-programs conducted in tropical and subtropical coral reefs environments around
-Australia. Data are available from approximately 80 GBR sites, 16 Coral Sea
-sites, 7 sites in North West Western Australia (WA), 8 Queensland regional
-ports, 13 sites in the Solitary Islands, 4 sites in Papua New Guinea and 10
-sites in the Cocos (Keeling) Islands. Data are obtained from in-situ data
-loggers deployed on the reef. Temperature instruments sample water
-temperatures every 5-10 minutes (typically) and are exchanged and downloaded
-approximately every 12 months. Temperature loggers on the reef-flat are
-generally placed just below Lowest Astronomical Tide level. Reef-slope (or
-where specified as Upper reef-slope) generally refers to depths 5--9 m while
-Deep reef-slope refers to depths of ~20 m. For more information on the dataset
-and its usage, please visit the [AIMS metadata][3] webpage.
 
@@
 visualisation of both datasets and their multiple features directly
-through the R package. At the moment though it is only possible
-to visualise summary information for the Sea Water Temperature Loggers
-dataset. A similar feature for the Weather Station dataset will be 
-implemented in the near future (likely late 2021)---so for now, please
-refer to the online metadata to discover from where (and when) one can 
-download data.
+through the R package. So please consult our [on-line vignettes][35] to obtain
+the most up-to-date instructions on how to navigate the different datasets.
+Future versions of this package might even provide more of AIMS monitoring
+datasets.
+
+[35]: https://docs.ropensci.org/dataaimsr/articles/
 
@@
 for the Sea Water Temperature Loggers dataset using the main function called
-`aims_data`:
+`aims_data`. Setting the argument `api_key = NULL` means that `dataaimsr` will
+automatically search for the user's API key stored in `.Renviron`.
+The `summary` argument should only be used when the
+user wants an overview of the available data---this is currently
+implemented for the Sea Water Temperature Loggers dataset only. One can
+visualise `summary-by-series` or `summary-by-deployment`. The output of
+`aims_data` is a `data.frame` of class `aimsdf` with its own plotting
+method (Fig. \@ref(fig:summary)):
 
-```{r, message = FALSE, warning = FALSE}
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
 library(dataaimsr)
@@
                    summary = "summary-by-series")
-head(sdata)
 ```
 
-Setting the argument `api_key = NULL` means that `dataaimsr` will
-automatically search for the user's API key stored in `.Renviron`.
-The `summary` argument here is key. It should only be flagged when the
-user wants an overview of the available data. Again, this currently
-implemented for the Sea Water Temperature Loggers dataset. One can
-visualise `summary-by-series` or `summary-by-deployment`. The output of
-`aims_data` is a `data.frame` of class `aimsdf`.
-
-Notice that `sdata` contains a lot of information, most of which is
-related to site / series / parameter ID. Each row corresponds to a
-unique series, and a certain site may contain multiple series; in such
-cases, series generally differ from one another by depth. The columns 
-`time_coverage_start` and `time_coverage_end` are probably one of the most
-valuable pieces of information. They provide the user with the window of data
-collection for a particular series, which is probably crucial to decide
-whether that particular series is of relevance to the specific question in
-hand.
-
-Also note that there are three columns containing the total number of 
-observations in a series: `uncal_obs`, `cal_obs` and `qc_obs`, which 
-respectively stand for uncalibrated, calibrated, and quality-controlled 
-observations. Calibrated and quality-controlled are generally the same.
-Instruments are routinely calibrated (mostly once a year) in a temperature-controlled water bath and corrections applied to the data. After
-calibration, all data records are quality controlled based on the following
-tests: 1) clip to in-water only data, using deployment's metadata, 2)
-impossible value check: data outside a fixed temperature range (14˚C – 40˚C)
-is flagged as bad data, 3) spike test: individual extreme values are flagged
-as probably bad according to the algorithm presented in @morelo2014methods and
-4) Excessive gradient test: pairs of data that present a sudden change in the
-slope are flagged as probably bad [@toma2016acta]. If any data record fails at
-least one of the tests, a QC flag equal to 2 is returned, otherwise, the QC
-flag is set to 1.
-
-One can visualise this data, for instance, by plotting them
-on a map of Australia, while colouring based on the total amount of calibrated
-observations (Fig. \@ref(fig:summary)).
-
-`aimsdf` objects can be plotted using the `plot` function. For summary data
-such as `sdata`, plot will always generate a map with the points around
-Australia and associated regions, coloured by the number of calibrated
-observations:
-
 ```{r echo = FALSE, eval = FALSE}
+library(dataaimsr)
+sdata <- aims_data("temp_loggers", api_key = NULL,
+                   summary = "summary-by-series")
 out <- plot(sdata, ptype = "map")
@@
 
+For summary data such as `sdata`, plot will always generate a map with the
+points around Australia and associated regions, coloured by the number of
+calibrated observations.
+Observations in a series can be: `uncal_obs`, `cal_obs` and `qc_obs`, which 
+respectively stand for uncalibrated, calibrated, and quality-controlled 
+observations. Calibrated and quality-controlled are generally the same.
+Instruments are routinely calibrated (mostly once a year) in a
+temperature-controlled water bath and corrections applied to the data. After
+calibration, all data records are quality controlled based on the following
+tests: 1) clip to in-water only data, using deployment's metadata, 2)
+impossible value check: data outside a fixed temperature range (14˚C – 40˚C)
+is flagged as bad data, 3) spike test: individual extreme values are flagged
+as probably bad according to the algorithm presented in @morelo2014methods and
+4) Excessive gradient test: pairs of data that present a sudden change in the
+slope are flagged as probably bad [@toma2016acta]. If any data record fails at
+least one of the tests, a QC flag equal to 2 is returned, otherwise, the QC
+flag is set to 1. Please refer to our on-line [on-line vignettes][35] to learn
+details about the entire structure of an `aimsdf` object.
+
 In the case of the Weather Station dataset, the user can call a
@@
 ```{r, message = FALSE, warning = FALSE}
-aims_filter_values("weather", filter_name = "series") %>%
-  head()
+head(aims_filter_values("weather", filter_name = "series"))
 ```
@@
 available observation window is absolutely crucial, then as mentioned 
-above the user should refer to the [online metadata][3].
+above the user should refer to the [on-line metadata][3].
 
@@
 high temporal resolution and if one tries to download an entire series
-it might take hours if not days. To slice the datasets properly, the user
+it might take a few hours. To slice the datasets properly, the user
 needs to apply filters to their query.

### 2021-05-24 README.Rmd
added JOSS badge to README; openjournals/joss-reviews#3282

@@
 [![](https://badges.ropensci.org/428_status.svg)](https://github.com/ropensci/software-review/issues/428)
+[![status](https://joss.theoj.org/papers/7980fff63a54453a4e637f185764336d/status.svg)](https://joss.theoj.org/papers/7980fff63a54453a4e637f185764336d)
 [![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)

### 2021-06-01 paper/paper.Rmd
fixed figure referencing

@@
 `aims_data` is a `data.frame` of class `aimsdf` with its own plotting
-method (Fig. \@ref(fig:summary)):
+method \autoref{fig:summary}:
 
@@
 
-(ref:fig-summary) Distribution of all temperature logger series around Australian waters.
-
-```{r summary, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-summary)", cache = TRUE}
-knitr::include_graphics("summary.png")
-```
+![Distribution of all temperature logger series around Australian waters.\label{fig:summary}](summary.png)
 
@@
 parameters chosen at random for a time series plot. Alternatively the user can
-specify which parameters are to be plotted (Fig. \@ref(fig:wind)).
+specify which parameters are to be plotted \autoref{fig:wind}.
 
@@
 
-(ref:fig-wind) Yongala wreck profiles for water pressure and chlorophyll-a between the first and second of January 2018.
-
-```{r wind, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-wind)", cache = TRUE}
-knitr::include_graphics("wind.png")
-```
+![Yongala wreck profiles for water pressure and chlorophyll-a between the first and second of January 2018.\label{fig:wind}](wind.png)
 
@@
 sufficiently, the data will be displayed as non-aggregate values
-(Fig. \@ref(fig:tssa)). This technique is being used to ensure the application
+\autoref{fig:tssa}. This technique is being used to ensure the application
 performs well with large time series.
 
-(ref:fig-tssa) Interactive discovery and visualisation of data series.
-
-```{r tssa, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-tssa)", cache = TRUE}
-knitr::include_graphics("tssa.png")
-```
+![Interactive discovery and visualisation of data series.\label{fig:tssa}](tssa.png)
 
@@
 snippet that shows how to obtain the data using the dataaimsr package
-(Fig. \@ref(fig:tssb)). In this way, a user can easily explore and discover
+\autoref{fig:tssb}. In this way, a user can easily explore and discover
 datasets and then quickly and easily have this data in their R environment for
@@
 
-(ref:fig-tssb) Download/Export displayed data via R snippet.
-
-```{r tssb, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-tssb)", cache = TRUE}
-knitr::include_graphics("tssb.png")
-```
+![Download/Export displayed data via R snippet.\label{fig:tssb}](tssb.png)
 

### 2021-06-05 README.Rmd
added JOSS acceptance badge, and fixed link typo

--- 2021-03-31 README.Rmd
@@
 [![](https://badges.ropensci.org/428_status.svg)](https://github.com/ropensci/software-review/issues/428)
+[![DOI](https://joss.theoj.org/papers/10.21105/joss.03282/status.svg)](https://doi.org/10.21105/joss.03282)
 [![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
@@
 of dataset made available by the API. Below we provide a brief context about
-the existing [Datasets][#datasets] that can be explored through `dataaimsr`.
+the existing [Datasets](#datasets) that can be explored through `dataaimsr`.
 

### 2021-06-07 README.Rmd
updated package citation; added to README

@@
 <!-- badges: end -->
+
+**Barneche DR, Coleman G, Fermor D, Klein E, Robinson T, Smith J, Sheehan JL, Dowley S, Ditton D, Gunn K, Ericson G, Logan M, Rehbein M** (2021).
+dataaimsr: An R Client for the Australian Institute of Marine Science Data Platform API which provides easy access to AIMS Data Platform.
+*Journal of Open Source Software*, **6:** 3282.
+doi: [10.21105/joss.03282](https://doi.org/10.21105/joss.03282).
 

### 2021-10-29 R/aims_data.R
added compatibility wit "daily" method of temperature logger datasets

@@ -8,9 +8,12 @@
 #' the dataset. Only \code{weather} or \code{temp_loggers} are currently
 #' allowed.
 #' @param filters A \code{\link[base]{list}} containing a set of
-#' filters for the data query (see Details)
-#' @param ... Additional arguments to be passed to non-exported internal
-#' functions \code{\link{page_data}} and \code{\link{next_page_data}}
+#' filters for the data query (see Details).
+#' @param summary Should summary tables (\code{"summary-by-series"} or
+#' \code{"summary-by-deployment"}) or daily aggregated data ("daily") be
+#' returned instead of full data (see Details)?
+#' @param ... Currently unused. Additional arguments to be passed to
+#' non-exported internal functions.
 #'
 #' @details The AIMS Data Platform R Client provides easy access to
 #' data sets for R applications to the
@@ -37,23 +40,33 @@
 #'
 #' Note that at present the user can inspect the range of dates for
 #' the temperature loggers data only (see usage of argument \code{summary} in
-#' \code{\link{aims_data}}). Details about available dates for each dataset
-#' and time series can be accessed via Metadata on
+#' the examples below). For that, the argument \code{summary} must be either
+#' the string \code{"summary-by-series"} or \code{"summary-by-deployment"}.
+#' In those cases, time filters will be ignored.
+#' 
+#' Details about available dates for each dataset and time series can be
+#' accessed via Metadata on
 #' \href{https://open-aims.github.io/data-platform}{AIMS Data Platform API}.
 #' We raise this caveat here because these time boundaries are very important;
-#' data are collected at very small time intervals, so just a few days of
-#' time interval can yield massive datasets. The query will return and error
+#' data are collected at very small time intervals, a window of just a few days
+#' can yield very large datasets. The query will return and error
 #' if it reaches the system's memory capacity.
+#'
+#' For that same reason, from version 1.1.0 onwards, we are offering the
+#' possibility of downloading a mean daily aggregated version. For that, the
+#' user must set \code{summary = "daily"}. In this particular case, query filter
+#' will be taken into account.
 #'
 #' @return \code{aims_data} returns a \code{\link[base]{data.frame}} of class
 #' \code{\link{aimsdf}}.
 #'
-#' If \code{summary} is passed as an additional argument,
[…]

### 2021-10-29 R/aims_expose_attributes.R

@@ -10,7 +10,7 @@
 #'
 #' We are working on implementing summary visualisation methods for weather
 #' station data. So, for the moment, the options below are only available
-#' for temperature logger data. Two options are available:
+#' for temperature logger data. Three options are available:
 #'
 #' \itemize{
 #'    \item{summary-by-series}{Expose summary for all available series;
@@ -21,6 +21,7 @@
 #'          parameter.}
 #'    \item{summary-by-deployment}{Expose summary for all available
 #'          deployments.}
+#'    \item{daily}{Return mean daily aggregated monitoring data .}
 #' }
 #'
 #' We offer a list of valid filter names:
@@ -75,7 +76,7 @@ aims_expose_attributes <- function(target) {
   # used to evaluate input only
   invisible(data_doi(target = target))
   if (target == "temp_loggers") {
-    list(summary = c("summary-by-series", "summary-by-deployment"),
+    list(summary = c("summary-by-series", "summary-by-deployment", "daily"),
          filters = c("site", "subsite", "series", "series_id", "parameter",
                      "size", "min_lat", "max_lat", "min_lon", "max_lon",
                      "from_date", "thru_date", "version", "cursor"))

### 2021-10-29 R/aimsdf-methods.R

@@ -92,7 +92,7 @@ print.aimsdf <- function(x, ...) {
 #'                                 thru_date = "2018-01-02"))
 #' plot(wdf, ptype = "map")
 #' plot(wdf, ptype = "time_series")
-#' # summary datasets can only return maps
+#' # summary-by- datasets can only return maps
 #' sdf <- aims_data("temp_loggers", api_key = NULL,
 #'                  summary = "summary-by-deployment")
 #' plot(sdf, ptype = "map")

### 2021-10-29 R/page_data.R

@@ -11,8 +11,9 @@
 #' \href{https://open-aims.github.io/data-platform}{AIMS data series}
 #' @param api_key An AIMS Data Platform
 #' \href{https://open-aims.github.io/data-platform/key-request}{API Key}
-#' @param summary Should summary tables be printed instead of full data?
-#' Details in ?\code{\link{aims_expose_attributes}}
+#' @param summary Should summary tables (\code{"summary-by-series"} or
+#' \code{"summary-by-deployment"}) or daily aggregated data ("daily") be
+#' returned instead of full data (see Details)?
 #' @param aims_version A \code{\link[base]{character}} string
 #' defining the version of database. Must be "/v1.0" or "-v2.0".
 #' If none is provided, then "-v2.0" (the most recent) is used.

### 2021-10-29 tests/testthat/test-aims_data.R
updated tests using httptest

@@ -49,6 +49,8 @@ with_mock_api({
 
 with_mock_api({
   test_that("summary requests", {
+    expect_message(aims_data("temp_loggers", filters = s_filters,
+                             api_key = my_api_key, summary = "daily"))
     expect_message(aims_data("weather", api_key = my_api_key,
                              summary = "summary-by-series"))
     expect_message(aims_data("weather", api_key = my_api_key,

### 2021-10-29 README.Rmd
fixed/updted broken links, and updated tidyverse codign using rlang

@@
 [![DOI](https://joss.theoj.org/papers/10.21105/joss.03282/status.svg)](https://doi.org/10.21105/joss.03282)
-[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
 [![R build status](https://github.com/ropensci/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/dataaimsr/actions)
-[![Codecov test coverage](https://codecov.io/gh/ropensci/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/dataaimsr?branch=master)
+[![Codecov test coverage](https://codecov.io/gh/ropensci/dataaimsr/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ropensci/dataaimsr?branch=master)
 ![pkgdown](https://github.com/ropensci/dataaimsr/workflows/pkgdown/badge.svg)
@@
 
-[4]: https://ropensci.github.io/dataaimsr/articles
+[4]: https://ropensci.github.io/dataaimsr/articles/
 
@@
 
-`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](http://opensource.org/licenses/MIT)).
+`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](https://opensource.org/licenses/MIT)).
 
@@
 
-Our R package logos use a watercolour map of Australia, obtained with the [ggmap](https://CRAN.R-project.org/package=ggmap) R package, which downloads original map tiles provided by [Stamen Design](http://stamen.com), under [CC BY 3.0](http://creativecommons.org/licenses/by/3.0), with data from [OpenStreetMap](http://openstreetmap.org), under [CC BY SA](http://creativecommons.org/licenses/by-sa/3.0).
+Our R package logos use a watercolour map of Australia, obtained with the [ggmap](https://CRAN.R-project.org/package=ggmap) R package, which downloads original map tiles provided by [Stamen Design](https://stamen.com/), under [CC BY 3.0](https://creativecommons.org/licenses/by/3.0), with data from [OpenStreetMap](https://www.openstreetmap.org/), under [CC BY SA](https://creativecommons.org/licenses/by-sa/3.0).

### 2021-10-29 R/aims_data.R

@@ -1,7 +1,7 @@
 #' Request data via the AIMS Data Platform API
 #'
 #' A function that communicates with the
-#' the \href{https://open-aims.github.io/data-platform}{AIMS Data Platform}
+#' the \href{https://open-aims.github.io/data-platform/}{AIMS Data Platform}
 #' via the AIMS Data Platform API
 #'
 #' @param target A \code{\link[base]{character}} vector of length 1 specifying
@@ -17,7 +17,7 @@
 #'
 #' @details The AIMS Data Platform R Client provides easy access to
 #' data sets for R applications to the
-#' \href{https://open-aims.github.io/data-platform}{AIMS Data Platform API}.
+#' \href{https://open-aims.github.io/data-platform/}{AIMS Data Platform API}.
 #' The AIMS Data Platform requires an API Key for requests, which can
 #' be obtained at this
 #' \href{https://open-aims.github.io/data-platform/key-request}{link}.
@@ -27,7 +27,7 @@
 #' the API Key automatically.
 #'
 #' There are two types of data currently available through the
-#' [AIMS Data Platform API](https://open-aims.github.io/data-platform):
+#' [AIMS Data Platform API](https://open-aims.github.io/data-platform/):
 #' [Weather](https://weather.aims.gov.au/#/overview) and
 #' [Sea Water Temperature Loggers](https://tinyurl.com/h93mcojk).
 #' They are searched internally via unique DOI identifiers.
@@ -46,7 +46,7 @@
 #' 
 #' Details about available dates for each dataset and time series can be
 #' accessed via Metadata on
-#' \href{https://open-aims.github.io/data-platform}{AIMS Data Platform API}.
+#' \href{https://open-aims.github.io/data-platform/}{AIMS Data Platform API}.
 #' We raise this caveat here because these time boundaries are very important;
 #' data are collected at very small time intervals, a window of just a few days
 #' can yield very large datasets. The query will return and error

### 2021-10-29 R/aimsdf-methods.R

@@ -82,6 +82,7 @@ print.aimsdf <- function(x, ...) {
 #' @importFrom ggplot2 aes scale_colour_distiller guides guide_colourbar
 #' @importFrom ggplot2 geom_line theme_bw element_text facet_wrap
 #' @importFrom ggrepel geom_label_repel
+#' @importFrom rlang .data
 #'
 #' @examples
 #' \dontrun{
@@ -110,8 +111,8 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
     map_bd <- ne_countries(continent = "oceania", returnclass = "sf") %>%
       st_transform(crs = 3112)
     y <- x %>%
-      mutate(cols = cal_obs * 1e-3) %>%
-      drop_na(lon, lat) %>%
+      mutate(cols = .data$cal_obs * 1e-3) %>%
+      drop_na(.data$lon, .data$lat) %>%
       st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
       st_transform(crs = 3112)
     p_bkg <- make_pretty_colour("lightblue")
@@ -120,14 +121,12 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
       geom_sf(colour = "grey60", fill = "burlywood2",
               alpha = 0.8, lwd = 0.1) +
       theme_classic() +
-      theme(panel.background = element_rect(fill = p_bkg, colour = p_bkg,
+      theme(panel.background = element_rect(fill = .data$p_bkg,
+                                            colour = .data$p_bkg,
                                             linetype = "solid"),
             legend.position = "bottom") +
-      labs(x = "Longitude",
-           y = "Latitude",
-           title = target,
-           subtitle = d_type) +
-      geom_sf(data = y, mapping = aes(colour = cols)) +
+      labs(x = "Longitude", y = "Latitude", title = target, subtitle = d_type) +
+      geom_sf(data = y, mapping = aes(colour = .data$cols)) +
       scale_colour_distiller(name = name_leg, palette = 6) +
       guides(colour = guide_colourbar(title.position = "top",
                                       title.hjust = 0.5))
@@ -141,12 +140,13 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
         pars <- sample(d_pars)[seq_len(n_)]
       }
       y <- x %>%
-        filter(parameter %in% pars)
+        filter(.data$parameter %in% pars)
       ggplot(data = y) +
[…]

### 2021-10-29 R/page_data.R

@@ -1,14 +1,14 @@
 #' Request data via the AIMS Data Platform API
 #'
 #' A function that communicates with the
-#' the \href{https://open-aims.github.io/data-platform}{AIMS Data Platform}
+#' the \href{https://open-aims.github.io/data-platform/}{AIMS Data Platform}
 #' via the AIMS Data Platform API
 #'
 #' @inheritParams aims_data
 #'
 #' @param doi A \href{https://www.doi.org/}{Digital Object Identifier}
 #' for a chosen
-#' \href{https://open-aims.github.io/data-platform}{AIMS data series}
+#' \href{https://open-aims.github.io/data-platform/}{AIMS data series}
 #' @param api_key An AIMS Data Platform
 #' \href{https://open-aims.github.io/data-platform/key-request}{API Key}
 #' @param summary Should summary tables (\code{"summary-by-series"} or

### 2023-05-19 README.Rmd
remove old block of code setting default filter size; no longer required; updated README link

@@
 
-`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](https://opensource.org/licenses/MIT)).
+`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](https://opensource.org/license/mit/)).
 

### 2023-05-19 R/page_data.R

@@ -33,13 +33,6 @@ page_data <- function(doi, filters = NULL, api_key = NULL,
   end_pt <- paste(base_end_pt, doi, "data", sep = "/")
   if (!is.na(summary)) {
     end_pt <- paste(end_pt, summary, sep = "/")
-  } else {
-    # for now, this block is only triggered if summary is not queried
-    # because it is causing conflict with the summary-type endpoint
-    # behaviour; should be removed once API is fixed.
-    if (is.null(filters[["size"]])) {
-      filters[["size"]] <- 1000
-    }
   }
   dt_req <- GET(end_pt,
                 add_headers("X-Api-Key" = find_api_key(api_key),

### 2023-05-19 R/aimsdf-methods.R
updated tidyr and tidyselect changes to .data

@@ -75,7 +75,7 @@ print.aimsdf <- function(x, ...) {
 #' @return An object of class \code{\link[ggplot2]{ggplot}}.
 #'
 #' @importFrom rnaturalearth ne_countries
-#' @importFrom dplyr %>% mutate filter group_by summarise
+#' @importFrom dplyr %>% mutate filter group_by reframe
 #' @importFrom tidyr drop_na
 #' @importFrom sf st_transform st_as_sf
 #' @importFrom ggplot2 ggplot geom_sf theme_classic theme element_rect labs
@@ -112,7 +112,7 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
       st_transform(crs = 3112)
     y <- x %>%
       mutate(cols = .data$cal_obs * 1e-3) %>%
-      drop_na(.data$lon, .data$lat) %>%
+      drop_na("lon", "lat") %>%
       st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
       st_transform(crs = 3112)
     p_bkg <- make_pretty_colour("lightblue")
@@ -154,12 +154,12 @@ plot.aimsdf <- function(x, ..., ptype, pars) {
         st_transform(crs = 3112)
       y_l <- x %>%
         group_by(.data$site) %>%
-        summarise(n_obs = length(.data$qc_val), lon = unique(.data$lon),
-                  lat = unique(.data$lat),
-                  n_ser = length(unique(.data$series))) %>%
+        reframe(n_obs = length(.data$qc_val), lon = unique(.data$lon),
+                lat = unique(.data$lat),
+                n_ser = length(unique(.data$series))) %>%
         mutate(par_l = paste0(.data$site, ":\n", .data$n_ser, " series; ",
                               .data$n_obs, " obs.")) %>%
-        drop_na(.data$lon, .data$lat)
+        drop_na("lon", "lat")
       y_p <- y_l %>%
         st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
         st_transform(crs = 3112)

### 2023-05-19 test_running_updating.Rmd
updates to tests

# How to run or recreate tests

From `dataaimsr/`, run

```{r}
library(testthat)
library(roxygen2)
library(devtools)
system("rm -rf tests/api")
roxygen2::roxygenise()
devtools::install(build_vignettes = FALSE)
testthat::test_local(".")
all_mock_dirs <- dir("tests/api", full.names = TRUE, recursive = TRUE) |>
  dirname() |>
  unique()
new_mock_dirs <- gsub(
  "api.aims.gov.au/data-v2.0/10.25845", "a", all_mock_dirs, fixed = TRUE
)
for (i in seq_along(all_mock_dirs)) {
  system(paste0("mkdir -p ", new_mock_dirs[i]))
  system(paste0(
    "cp -R ", all_mock_dirs[i], "/* ", new_mock_dirs[i], "/" , collapse = ""
  ))
  to_rm <- dirname(all_mock_dirs[i]) |>
    dirname() |>
    dirname()
  system(paste0("rm -rf ", to_rm))
}
```

This will delete all existing mock files and regenerate them. Then return to root directory and check if it all passes:

```{r}
rm(list = ls())
rcmdcheck::rcmdcheck(
  args = c("--no-manual", "--as-cran"), build_args = "--resave-data=best",
  error_on = "warning", check_dir = "check"
)
```

### 2023-05-19 inst/httptest/request.R

@@ -1,8 +1,5 @@
 httptest::set_requester(function(request) {
-    httptest::gsub_request(
-        request,
-        "https://api.aims.gov.au/data-v2.0/10.25845/",
-        "a/",
-        fixed = TRUE
-    )
+  httptest::gsub_request(
+    request, "https://api.aims.gov.au/data-v2.0/10.25845/", "a/", fixed = TRUE
+  )
 })

### 2023-05-19 tests/api/Correctly-process-requests/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Mon, 10 Oct 2022 07:11:02 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:12 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "51c0bd3c-630d-4cb7-8130-38c1f910b01e", 
+        `x-amzn-requestid` = "fd777f58-dedd-4cd9-b280-aedfcee9b141", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "ZxvM_HWYSwMF-yA=", `x-amzn-trace-id` = "Root=1-6343c586-5168b7025765ddbd5a8991f0"), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJo6_FssSwMF-Ig="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:11:02 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:36:12 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "51c0bd3c-630d-4cb7-8130-38c1f910b01e", 
+            `x-amzn-requestid` = "fd777f58-dedd-4cd9-b280-aedfcee9b141", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "ZxvM_HWYSwMF-yA=", `x-amzn-trace-id` = "Root=1-6343c586-5168b7025765ddbd5a8991f0"), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJo6_FssSwMF-Ig="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
[…]

### 2023-05-19 tests/api/Correctly-update-request-output-format/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Mon, 10 Oct 2022 07:11:04 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:13 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "a2df4181-d53f-4480-aa26-39c39d40c12a", 
+        `x-amzn-requestid` = "ae56f5ca-ba75-4bd0-9b91-f38a371e413f", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "ZxvNSEgXywMFzHg=", `x-amzn-trace-id` = "Root=1-6343c588-428b53f247ca59f42c367fff"), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJo7JGKjSwMFesw="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:11:04 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:36:13 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "a2df4181-d53f-4480-aa26-39c39d40c12a", 
+            `x-amzn-requestid` = "ae56f5ca-ba75-4bd0-9b91-f38a371e413f", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "ZxvNSEgXywMFzHg=", `x-amzn-trace-id` = "Root=1-6343c588-428b53f247ca59f42c367fff"), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJo7JGKjSwMFesw="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
[…]

### 2023-05-19 tests/api/JSON-results-Correct-structure-helpers/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Mon, 10 Oct 2022 07:11:00 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:11 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "c023896f-a1c8-4377-9d1b-63eaca3645c4", 
+        `x-amzn-requestid` = "ef8928da-761e-44dd-b819-12b164e7d5c0", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "ZxvMuEc-SwMFrAA=", `x-amzn-trace-id` = "Root=1-6343c584-0ed48cfb6108b6d365d0d330"), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJo62ECJywMF7_A="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:11:00 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:36:11 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "c023896f-a1c8-4377-9d1b-63eaca3645c4", 
+            `x-amzn-requestid` = "ef8928da-761e-44dd-b819-12b164e7d5c0", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "ZxvMuEc-SwMFrAA=", `x-amzn-trace-id` = "Root=1-6343c584-0ed48cfb6108b6d365d0d330"), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJo62ECJywMF7_A="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
[…]

### 2023-05-19 tests/api/Wrong-filters-aimsdata/a/5b4eb0f9bb848/data-557113.R

@@ -1,20 +1,0 @@
-structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5b4eb0f9bb848/data?series=2687&size=1000", 
-    status_code = 500L, headers = structure(list(date = "Mon, 10 Oct 2022 07:10:20 GMT", 
-        `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-        `x-amzn-requestid` = "61f3d434-c16b-443f-b628-087db898e589", 
-        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "ZxvGcF02SwMFhcw=", 
-        `x-amzn-trace-id` = "Root=1-6343c55c-1d04472c524a77627e913f2b"), class = c("insensitive", 
-    "list")), all_headers = list(list(status = 500L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:10:20 GMT", 
-            `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-            `x-amzn-requestid` = "61f3d434-c16b-443f-b628-087db898e589", 
-            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "ZxvGcF02SwMFhcw=", 
-            `x-amzn-trace-id` = "Root=1-6343c55c-1d04472c524a77627e913f2b"), class = c("insensitive", 
-        "list")))), cookies = structure(list(domain = logical(0), 
-        flag = logical(0), path = logical(0), secure = logical(0), 
-        expiration = structure(numeric(0), class = c("POSIXct", 
-        "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
-    content = charToRaw("Internal Server Error"), date = structure(1665385820, class = c("POSIXct", 
-    "POSIXt"), tzone = "GMT"), times = c(redirect = 0, namelookup = 2.5e-05, 
-    connect = 2.6e-05, pretransfer = 0.000101, starttransfer = 0.30382, 
-    total = 0.303946)), class = "response")

### 2023-05-19 tests/api/Wrong-filters-aimsdata/a/5b4eb0f9bb848/data-9accd3.R

@@ -1,20 +1,0 @@
-structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5b4eb0f9bb848/data?series_id=2687&from_date=1900-01-01&thru_date=1900-01-10&size=1000", 
-    status_code = 500L, headers = structure(list(date = "Mon, 10 Oct 2022 07:10:20 GMT", 
-        `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-        `x-amzn-requestid` = "894faffd-0eb9-4e13-9921-3e5f49d66009", 
-        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "ZxvGfG2CSwMForQ=", 
-        `x-amzn-trace-id` = "Root=1-6343c55c-6d5980ff08dcce1760fe3ab5"), class = c("insensitive", 
-    "list")), all_headers = list(list(status = 500L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:10:20 GMT", 
-            `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-            `x-amzn-requestid` = "894faffd-0eb9-4e13-9921-3e5f49d66009", 
-            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "ZxvGfG2CSwMForQ=", 
-            `x-amzn-trace-id` = "Root=1-6343c55c-6d5980ff08dcce1760fe3ab5"), class = c("insensitive", 
-        "list")))), cookies = structure(list(domain = logical(0), 
-        flag = logical(0), path = logical(0), secure = logical(0), 
-        expiration = structure(numeric(0), class = c("POSIXct", 
-        "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
-    content = charToRaw("Internal Server Error"), date = structure(1665385820, class = c("POSIXct", 
-    "POSIXt"), tzone = "GMT"), times = c(redirect = 0, namelookup = 3.9e-05, 
-    connect = 4e-05, pretransfer = 0.000134, starttransfer = 0.300939, 
-    total = 0.301069)), class = "response")

### 2023-05-19 tests/api/Wrong-filters-aimsdata/a/5c09bf93f315d/data-3f57c4.R

@@ -1,0 +1,21 @@
+structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series=2687", 
+    status_code = 422L, headers = structure(list(date = "Fri, 19 May 2023 03:29:56 GMT", 
+        `content-type` = "application/json", `content-length` = "176", 
+        `x-amzn-requestid` = "eba48af2-71d5-4e55-8ef1-17d9dbf28e76", 
+        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJoAOG50SwMFaAA=", 
+        `x-amzn-trace-id` = "Root=1-6466ed34-1d9826083a1e73c64c3ef612;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+    "list")), all_headers = list(list(status = 422L, version = "HTTP/2", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:29:56 GMT", 
+            `content-type` = "application/json", `content-length` = "176", 
+            `x-amzn-requestid` = "eba48af2-71d5-4e55-8ef1-17d9dbf28e76", 
+            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJoAOG50SwMFaAA=", 
+            `x-amzn-trace-id` = "Root=1-6466ed34-1d9826083a1e73c64c3ef612;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        "list")))), cookies = structure(list(domain = logical(0), 
+        flag = logical(0), path = logical(0), secure = logical(0), 
+        expiration = structure(numeric(0), class = c("POSIXct", 
+        "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
+    content = charToRaw("{\"detail\":[{\"loc\":[\"query\",\"from_date\"],\"msg\":\"field required\",\"type\":\"value_error.missing\"},{\"loc\":[\"query\",\"thru_date\"],\"msg\":\"field required\",\"type\":\"value_error.missing\"}]}"), 
+    date = structure(1684466996, class = c("POSIXct", "POSIXt"
+    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 4.5e-05, 
+    connect = 0, pretransfer = 0.000135, starttransfer = 0.137363, 
+    total = 0.137447)), class = "response")

### 2023-05-19 tests/api/Wrong-filters-aimsdata/a/5c09bf93f315d/data-aa36ae.R

@@ -1,0 +1,20 @@
+structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series_id=2687&from_date=1900-01-01&thru_date=1900-01-10", 
+    status_code = 500L, headers = structure(list(date = "Fri, 19 May 2023 03:29:56 GMT", 
+        `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
+        `x-amzn-requestid` = "e7c91009-5e37-44bd-a441-80742ccfdf74", 
+        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJoAQFsDSwMFbnA=", 
+        `x-amzn-trace-id` = "Root=1-6466ed34-616fd7d016f61c3b72584f47;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+    "list")), all_headers = list(list(status = 500L, version = "HTTP/2", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:29:56 GMT", 
+            `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
+            `x-amzn-requestid` = "e7c91009-5e37-44bd-a441-80742ccfdf74", 
+            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJoAQFsDSwMFbnA=", 
+            `x-amzn-trace-id` = "Root=1-6466ed34-616fd7d016f61c3b72584f47;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        "list")))), cookies = structure(list(domain = logical(0), 
+        flag = logical(0), path = logical(0), secure = logical(0), 
+        expiration = structure(numeric(0), class = c("POSIXct", 
+        "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
+    content = charToRaw("Internal Server Error"), date = structure(1684466996, class = c("POSIXct", 
+    "POSIXt"), tzone = "GMT"), times = c(redirect = 0, namelookup = 0.000172, 
+    connect = 0, pretransfer = 0.000249, starttransfer = 0.151445, 
+    total = 0.151627)), class = "response")

### 2023-05-19 tests/api/Wrong-filters-aimsdata/a/5c09bf93f315d/data-eb62e6.R

@@ -1,21 +1,0 @@
-structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series=64&size=1000", 
-    status_code = 422L, headers = structure(list(date = "Mon, 10 Oct 2022 07:10:19 GMT", 
-        `content-type` = "application/json", `content-length` = "176", 
-        `x-amzn-requestid` = "6934f040-4471-4152-908a-dec3bdce8831", 
-        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "ZxvGUEUxywMFQXA=", 
-        `x-amzn-trace-id` = "Root=1-6343c55b-4d43236410966cef30fd961f"), class = c("insensitive", 
-    "list")), all_headers = list(list(status = 422L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:10:19 GMT", 
-            `content-type` = "application/json", `content-length` = "176", 
-            `x-amzn-requestid` = "6934f040-4471-4152-908a-dec3bdce8831", 
-            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "ZxvGUEUxywMFQXA=", 
-            `x-amzn-trace-id` = "Root=1-6343c55b-4d43236410966cef30fd961f"), class = c("insensitive", 
-        "list")))), cookies = structure(list(domain = logical(0), 
-        flag = logical(0), path = logical(0), secure = logical(0), 
-        expiration = structure(numeric(0), class = c("POSIXct", 
-        "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
-    content = charToRaw("{\"detail\":[{\"loc\":[\"query\",\"from_date\"],\"msg\":\"field required\",\"type\":\"value_error.missing\"},{\"loc\":[\"query\",\"thru_date\"],\"msg\":\"field required\",\"type\":\"value_error.missing\"}]}"), 
-    date = structure(1665385819, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 2.5e-05, 
-    connect = 2.6e-05, pretransfer = 9.4e-05, starttransfer = 0.405614, 
-    total = 0.40565)), class = "response")

### 2023-05-19 tests/api/Wrong-filters-pagedata/a/5c09bf93f315d/data-3f57c4.R

@@ -1,0 +1,21 @@
+structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series=2687", 
+    status_code = 422L, headers = structure(list(date = "Fri, 19 May 2023 03:36:19 GMT", 
+        `content-type` = "application/json", `content-length` = "176", 
+        `x-amzn-requestid` = "c248aa8a-df40-4fa1-8ba8-9e346d5f815f", 
+        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJo8FGv-ywMFYGg=", 
+        `x-amzn-trace-id` = "Root=1-6466eeb3-5eb001192634e611511939e6;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+    "list")), all_headers = list(list(status = 422L, version = "HTTP/2", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:36:19 GMT", 
+            `content-type` = "application/json", `content-length` = "176", 
+            `x-amzn-requestid` = "c248aa8a-df40-4fa1-8ba8-9e346d5f815f", 
+            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJo8FGv-ywMFYGg=", 
+            `x-amzn-trace-id` = "Root=1-6466eeb3-5eb001192634e611511939e6;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        "list")))), cookies = structure(list(domain = logical(0), 
+        flag = logical(0), path = logical(0), secure = logical(0), 
+        expiration = structure(numeric(0), class = c("POSIXct", 
+        "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
+    content = charToRaw("{\"detail\":[{\"loc\":[\"query\",\"from_date\"],\"msg\":\"field required\",\"type\":\"value_error.missing\"},{\"loc\":[\"query\",\"thru_date\"],\"msg\":\"field required\",\"type\":\"value_error.missing\"}]}"), 
+    date = structure(1684467379, class = c("POSIXct", "POSIXt"
+    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 2.6e-05, 
+    connect = 0, pretransfer = 0.000123, starttransfer = 0.165076, 
+    total = 0.165162)), class = "response")

### 2023-05-19 tests/api/Wrong-filters-pagedata/a/5c09bf93f315d/data-aa36ae.R

@@ -1,0 +1,20 @@
+structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series_id=2687&from_date=1900-01-01&thru_date=1900-01-10", 
+    status_code = 500L, headers = structure(list(date = "Fri, 19 May 2023 03:36:19 GMT", 
+        `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
+        `x-amzn-requestid` = "23273b1d-4a61-4815-b519-fe37a5576138", 
+        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJo8HE4JywMFaAA=", 
+        `x-amzn-trace-id` = "Root=1-6466eeb3-1dd3a891190586f664c8bc89;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+    "list")), all_headers = list(list(status = 500L, version = "HTTP/2", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:36:19 GMT", 
+            `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
+            `x-amzn-requestid` = "23273b1d-4a61-4815-b519-fe37a5576138", 
+            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJo8HE4JywMFaAA=", 
+            `x-amzn-trace-id` = "Root=1-6466eeb3-1dd3a891190586f664c8bc89;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        "list")))), cookies = structure(list(domain = logical(0), 
+        flag = logical(0), path = logical(0), secure = logical(0), 
+        expiration = structure(numeric(0), class = c("POSIXct", 
+        "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
+    content = charToRaw("Internal Server Error"), date = structure(1684467379, class = c("POSIXct", 
+    "POSIXt"), tzone = "GMT"), times = c(redirect = 0, namelookup = 5.5e-05, 
+    connect = 0, pretransfer = 0.000295, starttransfer = 0.1582, 
+    total = 0.158513)), class = "response")

### 2023-05-19 tests/api/Wrong-filters-pagedata/a/5c09bf93f315d/data-eb62e6.R

@@ -1,21 +1,0 @@
-structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series=64&size=1000", 
-    status_code = 422L, headers = structure(list(date = "Mon, 10 Oct 2022 07:11:10 GMT", 
-        `content-type` = "application/json", `content-length` = "176", 
-        `x-amzn-requestid` = "3483d0fd-9331-4a00-abdf-384aea820b52", 
-        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "ZxvORG22ywMFpnA=", 
-        `x-amzn-trace-id` = "Root=1-6343c58e-5760c2967b96684d08724d3f"), class = c("insensitive", 
-    "list")), all_headers = list(list(status = 422L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:11:10 GMT", 
-            `content-type` = "application/json", `content-length` = "176", 
-            `x-amzn-requestid` = "3483d0fd-9331-4a00-abdf-384aea820b52", 
-            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "ZxvORG22ywMFpnA=", 
-            `x-amzn-trace-id` = "Root=1-6343c58e-5760c2967b96684d08724d3f"), class = c("insensitive", 
-        "list")))), cookies = structure(list(domain = logical(0), 
-        flag = logical(0), path = logical(0), secure = logical(0), 
-        expiration = structure(numeric(0), class = c("POSIXct", 
-        "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
-    content = charToRaw("{\"detail\":[{\"loc\":[\"query\",\"from_date\"],\"msg\":\"field required\",\"type\":\"value_error.missing\"},{\"loc\":[\"query\",\"thru_date\"],\"msg\":\"field required\",\"type\":\"value_error.missing\"}]}"), 
-    date = structure(1665385870, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 2.3e-05, 
-    connect = 2.3e-05, pretransfer = 7.9e-05, starttransfer = 0.369347, 
-    total = 0.36942)), class = "response")

### 2023-05-19 tests/api/summary-requests-pagedata/a/5c09bf93f315d/data/summary-by-deployment.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data/summary-by-deployment", 
-    status_code = 403L, headers = structure(list(date = "Mon, 10 Oct 2022 07:11:11 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:20 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "17e7e49a-fce4-4b0e-90f8-78350b8a003d", 
+        `x-amzn-requestid` = "ba05b33a-9243-4b0c-be6a-d9020c6b3cae", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "ZxvOeEfaywMFecg=", `x-amzn-trace-id` = "Root=1-6343c58f-72237cea3a450d3150b2c74a"), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJo8LHzkSwMFWpQ="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:11:11 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:36:20 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "17e7e49a-fce4-4b0e-90f8-78350b8a003d", 
+            `x-amzn-requestid` = "ba05b33a-9243-4b0c-be6a-d9020c6b3cae", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "ZxvOeEfaywMFecg=", `x-amzn-trace-id` = "Root=1-6343c58f-72237cea3a450d3150b2c74a"), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJo8LHzkSwMFWpQ="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
[…]

### 2023-05-19 tests/api/summary-requests-pagedata/a/5c09bf93f315d/data/summary-by-series.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data/summary-by-series", 
-    status_code = 403L, headers = structure(list(date = "Mon, 10 Oct 2022 07:11:11 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:20 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "d91359c3-b1d5-4a3f-9aec-03311714794f", 
+        `x-amzn-requestid` = "6a90bd65-de39-4090-ad2e-4236ad02edcf", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "ZxvObH2QywMFVPw=", `x-amzn-trace-id` = "Root=1-6343c58f-76f2c7ec5ac72d7925318d08"), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJo8LEL8SwMFbkA="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Mon, 10 Oct 2022 07:11:11 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 03:36:20 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "d91359c3-b1d5-4a3f-9aec-03311714794f", 
+            `x-amzn-requestid` = "6a90bd65-de39-4090-ad2e-4236ad02edcf", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "ZxvObH2QywMFVPw=", `x-amzn-trace-id` = "Root=1-6343c58f-76f2c7ec5ac72d7925318d08"), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJo8LEL8SwMFbkA="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
[…]

### 2023-05-19 tests/testthat/test-aims_filter_values.R

@@ -4,11 +4,11 @@ with_mock_dir("Correct-structure-filtervalues", {
     expect_is(aims_filter_values("weather", filter_name = "series"),
               "data.frame")
     expect_is(aims_filter_values("temp_loggers", filter_name = "site"),
-              "character")
+              "data.frame")
     expect_is(aims_filter_values("temp_loggers", filter_name = "series"),
               "data.frame")
     expect_is(aims_filter_values("temp_loggers", filter_name = "parameter"),
-              "character")
+              "data.frame")
   })
 })
 

### 2023-05-19 tests/testthat/test-page_data.R

@@ -5,10 +5,12 @@ with_mock_dir("Correct-structure-pagedata", {
   test_that("Correct structure", {
     # default to 1000 returns next_page link
     wa <- page_data(weather_doi, filters = valid_weather_filters(), api_key = null_api_key())
+    # input to 300 returns next_page link
     sa <- page_data(ssts_doi, filters = valid_tlogger_filters(), api_key = null_api_key())
-    # larger size removed links from output
+    # larger size makes output fit in one go
     wb <- page_data(weather_doi, filters = weather_filters_larger_size(),
                     api_key = null_api_key())
+    # default to 1000 returns next_page link
     sb <- page_data(ssts_doi, filters = tlogger_filters_no_size(), api_key = null_api_key())
     # next_page works
     wa_n <- next_page_data(wa$links$next_page, api_key = null_api_key())
@@ -21,23 +23,39 @@ with_mock_dir("Correct-structure-pagedata", {
     expect_is(wa$links, "list")
     expect_identical(names(wa$links), "next_page")
     expect_is(sa, "list")
-    expect_length(sa, 5)
+    expect_length(sa, 6) # soon will revert back to 5
     expect_true(all(c("cursor", "links") %in% names(sa)))
     expect_is(sa$links, "list")
     expect_identical(names(sa$links), "next_page")
     expect_is(wb, "list")
-    expect_length(wb, 3)
-    expect_true(all(c("metadata", "citation", "data") %in% names(wb)))
+    expect_length(wb, 5)
+    expect_true(
+      all(
+        c("metadata", "citation", "links", "cursor", "data") %in% names(wb)
+      )
+    )
     expect_is(sb, "list")
-    expect_length(sb, 3)
-    expect_true(all(c("metadata", "citation", "data") %in% names(sb)))
+    expect_length(sb, 6) # soon will revert back to 5
+    expect_true(
+      all(
+        c("metadata", "citation", "links", "cursor", "data") %in% names(sb)
+      )
+    )
     expect_is(wa_n, "list")
-    expect_length(wa_n, 3)
-    expect_true(all(c("metadata", "citation", "data") %in% names(wa_n)))
+    expect_length(wa_n, 5)
+    expect_true(
+      all(
+        c("metadata", "citation", "links", "cursor", "data") %in% names(wa_n)
+      )
+    )
     expect_is(sa_n, "list")
-    expect_length(sa_n, 3)
[…]

### 2023-05-20 test_running_updating.Rmd
updated httptest and mock tests

@@
 ```{r}
+library(httptest) # installed from https://github.com/nealrichardson/httptest/commit/5fc2be9f8627fa36d04ee06de0291c1d7633d1a8
 library(testthat)
@@
 testthat::test_local(".")
-all_mock_dirs <- dir("tests/api", full.names = TRUE, recursive = TRUE) |>
-  dirname() |>
-  unique()
-new_mock_dirs <- gsub(
-  "api.aims.gov.au/data-v2.0/10.25845", "a", all_mock_dirs, fixed = TRUE
-)
-for (i in seq_along(all_mock_dirs)) {
-  system(paste0("mkdir -p ", new_mock_dirs[i]))
-  system(paste0(
-    "cp -R ", all_mock_dirs[i], "/* ", new_mock_dirs[i], "/" , collapse = ""
-  ))
-  to_rm <- dirname(all_mock_dirs[i]) |>
-    dirname() |>
-    dirname()
-  system(paste0("rm -rf ", to_rm))
-}
 ```
 
-This will delete all existing mock files and regenerate them. Then return to root directory and check if it all passes:
+The above block will delete all existing mock files and regenerate them. Then return to root directory and check if it all passes:
 

### 2023-05-20 tests/api/Correctly-process-requests/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:12 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:03 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "fd777f58-dedd-4cd9-b280-aedfcee9b141", 
+        `x-amzn-requestid` = "64a48c61-4f38-4100-b948-d50d1654c7c9", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJo6_FssSwMF-Ig="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJ9jhG4dSwMF13A="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:36:12 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:57:03 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "fd777f58-dedd-4cd9-b280-aedfcee9b141", 
+            `x-amzn-requestid` = "64a48c61-4f38-4100-b948-d50d1654c7c9", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJo6_FssSwMF-Ig="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJ9jhG4dSwMF13A="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684467372, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 5.4e-05, 
-    connect = 0, pretransfer = 0.000249, starttransfer = 0.060357, 
[…]

### 2023-05-20 tests/api/Correctly-update-request-output-format/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:13 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:04 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "ae56f5ca-ba75-4bd0-9b91-f38a371e413f", 
+        `x-amzn-requestid` = "23a99114-d55f-4f9c-9085-0ff6a9a83c49", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJo7JGKjSwMFesw="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJ9jrE56ywMFujQ="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:36:13 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:57:04 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "ae56f5ca-ba75-4bd0-9b91-f38a371e413f", 
+            `x-amzn-requestid` = "23a99114-d55f-4f9c-9085-0ff6a9a83c49", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJo7JGKjSwMFesw="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJ9jrE56ywMFujQ="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684467373, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 5.4e-05, 
[…]

### 2023-05-20 tests/api/JSON-results-Correct-structure-helpers/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:11 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:02 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "ef8928da-761e-44dd-b819-12b164e7d5c0", 
+        `x-amzn-requestid` = "2212242a-1cd6-4c5d-acb2-638375388e7a", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJo62ECJywMF7_A="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJ9jYH4mSwMFY9A="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:36:11 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:57:02 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "ef8928da-761e-44dd-b819-12b164e7d5c0", 
+            `x-amzn-requestid` = "2212242a-1cd6-4c5d-acb2-638375388e7a", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJo62ECJywMF7_A="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJ9jYH4mSwMFY9A="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684467371, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 5.4e-05, 
-    connect = 0, pretransfer = 0.000264, starttransfer = 0.060373, 
[…]

### 2023-05-20 tests/api/Wrong-filters-aimsdata/a/5c09bf93f315d/data-3f57c4.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series=2687", 
-    status_code = 422L, headers = structure(list(date = "Fri, 19 May 2023 03:29:56 GMT", 
+    status_code = 422L, headers = structure(list(date = "Fri, 19 May 2023 05:50:55 GMT", 
         `content-type` = "application/json", `content-length` = "176", 
-        `x-amzn-requestid` = "eba48af2-71d5-4e55-8ef1-17d9dbf28e76", 
-        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJoAOG50SwMFaAA=", 
-        `x-amzn-trace-id` = "Root=1-6466ed34-1d9826083a1e73c64c3ef612;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        `x-amzn-requestid` = "015f3bf8-c487-4e68-9fe3-1f319ab59b90", 
+        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJ8p-GW-ywMFSxg=", 
+        `x-amzn-trace-id` = "Root=1-64670e3f-0ebf2596038f2f42623d5b34;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
     "list")), all_headers = list(list(status = 422L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:29:56 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:50:55 GMT", 
             `content-type` = "application/json", `content-length` = "176", 
-            `x-amzn-requestid` = "eba48af2-71d5-4e55-8ef1-17d9dbf28e76", 
-            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJoAOG50SwMFaAA=", 
-            `x-amzn-trace-id` = "Root=1-6466ed34-1d9826083a1e73c64c3ef612;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+            `x-amzn-requestid` = "015f3bf8-c487-4e68-9fe3-1f319ab59b90", 
+            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJ8p-GW-ywMFSxg=", 
[…]

### 2023-05-20 tests/api/Wrong-filters-aimsdata/a/5c09bf93f315d/data-aa36ae.R

@@ -1,20 +1,20 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series_id=2687&from_date=1900-01-01&thru_date=1900-01-10", 
-    status_code = 500L, headers = structure(list(date = "Fri, 19 May 2023 03:29:56 GMT", 
+    status_code = 500L, headers = structure(list(date = "Fri, 19 May 2023 05:50:55 GMT", 
         `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-        `x-amzn-requestid` = "e7c91009-5e37-44bd-a441-80742ccfdf74", 
-        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJoAQFsDSwMFbnA=", 
-        `x-amzn-trace-id` = "Root=1-6466ed34-616fd7d016f61c3b72584f47;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        `x-amzn-requestid` = "a0190d2d-2115-4662-945b-6ae1567897fc", 
+        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJ8p_H84ywMFWIQ=", 
+        `x-amzn-trace-id` = "Root=1-64670e3f-0f303f32637c42770dde5b8a;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
     "list")), all_headers = list(list(status = 500L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:29:56 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:50:55 GMT", 
             `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-            `x-amzn-requestid` = "e7c91009-5e37-44bd-a441-80742ccfdf74", 
-            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJoAQFsDSwMFbnA=", 
-            `x-amzn-trace-id` = "Root=1-6466ed34-616fd7d016f61c3b72584f47;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+            `x-amzn-requestid` = "a0190d2d-2115-4662-945b-6ae1567897fc", 
+            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJ8p_H84ywMFWIQ=", 
[…]

### 2023-05-20 tests/api/Wrong-filters-pagedata/a/5c09bf93f315d/data-3f57c4.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series=2687", 
-    status_code = 422L, headers = structure(list(date = "Fri, 19 May 2023 03:36:19 GMT", 
+    status_code = 422L, headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
         `content-type` = "application/json", `content-length` = "176", 
-        `x-amzn-requestid` = "c248aa8a-df40-4fa1-8ba8-9e346d5f815f", 
-        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJo8FGv-ywMFYGg=", 
-        `x-amzn-trace-id` = "Root=1-6466eeb3-5eb001192634e611511939e6;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        `x-amzn-requestid` = "5f380260-8f5d-44da-8435-b1132a3ad633", 
+        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJ9ktETkSwMFcuQ=", 
+        `x-amzn-trace-id` = "Root=1-64670fb7-0e081065431dbe33401f0f0a;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
     "list")), all_headers = list(list(status = 422L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:36:19 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
             `content-type` = "application/json", `content-length` = "176", 
-            `x-amzn-requestid` = "c248aa8a-df40-4fa1-8ba8-9e346d5f815f", 
-            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJo8FGv-ywMFYGg=", 
-            `x-amzn-trace-id` = "Root=1-6466eeb3-5eb001192634e611511939e6;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+            `x-amzn-requestid` = "5f380260-8f5d-44da-8435-b1132a3ad633", 
+            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJ9ktETkSwMFcuQ=", 
+            `x-amzn-trace-id` = "Root=1-64670fb7-0e081065431dbe33401f0f0a;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
[…]

### 2023-05-20 tests/api/Wrong-filters-pagedata/a/5c09bf93f315d/data-aa36ae.R

@@ -1,20 +1,20 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series_id=2687&from_date=1900-01-01&thru_date=1900-01-10", 
-    status_code = 500L, headers = structure(list(date = "Fri, 19 May 2023 03:36:19 GMT", 
+    status_code = 500L, headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
         `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-        `x-amzn-requestid` = "23273b1d-4a61-4815-b519-fe37a5576138", 
-        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJo8HE4JywMFaAA=", 
-        `x-amzn-trace-id` = "Root=1-6466eeb3-1dd3a891190586f664c8bc89;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        `x-amzn-requestid` = "824b7281-c4e9-4173-a31d-ada3ef3e510c", 
+        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJ9kvHlzSwMF6zw=", 
+        `x-amzn-trace-id` = "Root=1-64670fb7-5daa8ec65c0afa4c66e243fa;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
     "list")), all_headers = list(list(status = 500L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:36:19 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
             `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-            `x-amzn-requestid` = "23273b1d-4a61-4815-b519-fe37a5576138", 
-            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJo8HE4JywMFaAA=", 
-            `x-amzn-trace-id` = "Root=1-6466eeb3-1dd3a891190586f664c8bc89;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+            `x-amzn-requestid` = "824b7281-c4e9-4173-a31d-ada3ef3e510c", 
+            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJ9kvHlzSwMF6zw=", 
[…]

### 2023-05-20 tests/api/summary-requests-pagedata/a/5c09bf93f315d/data/summary-by-deployment.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data/summary-by-deployment", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:20 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "ba05b33a-9243-4b0c-be6a-d9020c6b3cae", 
+        `x-amzn-requestid` = "bbdc7293-6804-4ddd-a699-b15ec7c5e6a9", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJo8LHzkSwMFWpQ="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJ9kyH44SwMFnAA="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:36:20 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "ba05b33a-9243-4b0c-be6a-d9020c6b3cae", 
+            `x-amzn-requestid` = "bbdc7293-6804-4ddd-a699-b15ec7c5e6a9", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJo8LHzkSwMFWpQ="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJ9kyH44SwMFnAA="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684467380, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 0.000112, 
[…]

### 2023-05-20 tests/api/summary-requests-pagedata/a/5c09bf93f315d/data/summary-by-series.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data/summary-by-series", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 03:36:20 GMT", 
+    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "6a90bd65-de39-4090-ad2e-4236ad02edcf", 
+        `x-amzn-requestid` = "74c4b9ef-3d4b-4c39-9b9d-6a3490427a2e", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJo8LEL8SwMFbkA="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FJ9kxG-BywMF9sA="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 03:36:20 GMT", 
+        headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "6a90bd65-de39-4090-ad2e-4236ad02edcf", 
+            `x-amzn-requestid` = "74c4b9ef-3d4b-4c39-9b9d-6a3490427a2e", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJo8LEL8SwMFbkA="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FJ9kxG-BywMF9sA="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684467380, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 2.8e-05, 
[…]

### 2023-05-31 test_running_updating.Rmd
updated tests following API update

@@
 ```{r}
-library(httptest) # installed from https://github.com/nealrichardson/httptest/commit/5fc2be9f8627fa36d04ee06de0291c1d7633d1a8
+library(httptest)
 library(testthat)

### 2023-05-31 tests/api/Correctly-process-requests/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:03 GMT", 
+    status_code = 403L, headers = structure(list(date = "Wed, 31 May 2023 05:25:01 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "64a48c61-4f38-4100-b948-d50d1654c7c9", 
+        `x-amzn-requestid` = "5948bd98-639c-4e1f-9992-3fdab234f821", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJ9jhG4dSwMF13A="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FxcHHH2uywMFrIQ="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:57:03 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:25:01 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "64a48c61-4f38-4100-b948-d50d1654c7c9", 
+            `x-amzn-requestid` = "5948bd98-639c-4e1f-9992-3fdab234f821", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJ9jhG4dSwMF13A="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FxcHHH2uywMFrIQ="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684475823, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 7.1e-05, 
-    connect = 0, pretransfer = 0.000223, starttransfer = 0.066316, 
[…]

### 2023-05-31 tests/api/Correctly-update-request-output-format/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:04 GMT", 
+    status_code = 403L, headers = structure(list(date = "Wed, 31 May 2023 05:25:02 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "23a99114-d55f-4f9c-9085-0ff6a9a83c49", 
+        `x-amzn-requestid` = "8ff58743-9899-440f-aba3-ccab58685337", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJ9jrE56ywMFujQ="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FxcHUEG9SwMFhNA="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:57:04 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:25:02 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "23a99114-d55f-4f9c-9085-0ff6a9a83c49", 
+            `x-amzn-requestid` = "8ff58743-9899-440f-aba3-ccab58685337", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJ9jrE56ywMFujQ="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FxcHUEG9SwMFhNA="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684475824, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 2.5e-05, 
-    connect = 0, pretransfer = 0.000111, starttransfer = 0.060877, 
[…]

### 2023-05-31 tests/api/JSON-results-Correct-structure-helpers/a/5c09bf93f315d/wrong.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/wrong", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:02 GMT", 
+    status_code = 403L, headers = structure(list(date = "Wed, 31 May 2023 05:24:59 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "2212242a-1cd6-4c5d-acb2-638375388e7a", 
+        `x-amzn-requestid` = "76e50709-3e44-41d3-8127-018745d57c21", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJ9jYH4mSwMFY9A="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FxcG6GoaSwMF1sw="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:57:02 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:24:59 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "2212242a-1cd6-4c5d-acb2-638375388e7a", 
+            `x-amzn-requestid` = "76e50709-3e44-41d3-8127-018745d57c21", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJ9jYH4mSwMFY9A="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FxcG6GoaSwMF1sw="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684475822, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 2.5e-05, 
-    connect = 0, pretransfer = 0.000103, starttransfer = 0.060823, 
[…]

### 2023-05-31 tests/api/Wrong-filters-aimsdata/a/5c09bf93f315d/data-3f57c4.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series=2687", 
-    status_code = 422L, headers = structure(list(date = "Fri, 19 May 2023 05:50:55 GMT", 
+    status_code = 422L, headers = structure(list(date = "Wed, 31 May 2023 05:16:56 GMT", 
         `content-type` = "application/json", `content-length` = "176", 
-        `x-amzn-requestid` = "015f3bf8-c487-4e68-9fe3-1f319ab59b90", 
-        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJ8p-GW-ywMFSxg=", 
-        `x-amzn-trace-id` = "Root=1-64670e3f-0ebf2596038f2f42623d5b34;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        `x-amzn-requestid` = "68ba1072-79cd-4c36-8e4f-f66ca1e91d49", 
+        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "Fxa7ZHkbSwMFVqA=", 
+        `x-amzn-trace-id` = "Root=1-6476d848-09e97c5c429a97672f125f9e;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
     "list")), all_headers = list(list(status = 422L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:50:55 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:16:56 GMT", 
             `content-type` = "application/json", `content-length` = "176", 
-            `x-amzn-requestid` = "015f3bf8-c487-4e68-9fe3-1f319ab59b90", 
-            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJ8p-GW-ywMFSxg=", 
-            `x-amzn-trace-id` = "Root=1-64670e3f-0ebf2596038f2f42623d5b34;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+            `x-amzn-requestid` = "68ba1072-79cd-4c36-8e4f-f66ca1e91d49", 
+            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "Fxa7ZHkbSwMFVqA=", 
[…]

### 2023-05-31 tests/api/Wrong-filters-aimsdata/a/5c09bf93f315d/data-aa36ae.R

@@ -1,20 +1,20 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series_id=2687&from_date=1900-01-01&thru_date=1900-01-10", 
-    status_code = 500L, headers = structure(list(date = "Fri, 19 May 2023 05:50:55 GMT", 
+    status_code = 500L, headers = structure(list(date = "Wed, 31 May 2023 05:16:56 GMT", 
         `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-        `x-amzn-requestid` = "a0190d2d-2115-4662-945b-6ae1567897fc", 
-        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJ8p_H84ywMFWIQ=", 
-        `x-amzn-trace-id` = "Root=1-64670e3f-0f303f32637c42770dde5b8a;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        `x-amzn-requestid` = "302b11a7-6e5f-4752-9980-5c3b305171f4", 
+        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "Fxa7bG_FywMF1jA=", 
+        `x-amzn-trace-id` = "Root=1-6476d848-4faf8f0b516b40e927aebe8f;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
     "list")), all_headers = list(list(status = 500L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:50:55 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:16:56 GMT", 
             `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-            `x-amzn-requestid` = "a0190d2d-2115-4662-945b-6ae1567897fc", 
-            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJ8p_H84ywMFWIQ=", 
-            `x-amzn-trace-id` = "Root=1-64670e3f-0f303f32637c42770dde5b8a;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+            `x-amzn-requestid` = "302b11a7-6e5f-4752-9980-5c3b305171f4", 
+            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "Fxa7bG_FywMF1jA=", 
[…]

### 2023-05-31 tests/api/Wrong-filters-pagedata/a/5c09bf93f315d/data-3f57c4.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series=2687", 
-    status_code = 422L, headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
+    status_code = 422L, headers = structure(list(date = "Wed, 31 May 2023 05:25:10 GMT", 
         `content-type` = "application/json", `content-length` = "176", 
-        `x-amzn-requestid` = "5f380260-8f5d-44da-8435-b1132a3ad633", 
-        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJ9ktETkSwMFcuQ=", 
-        `x-amzn-trace-id` = "Root=1-64670fb7-0e081065431dbe33401f0f0a;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        `x-amzn-requestid` = "a6354b92-4085-4546-82ec-a30208d228f6", 
+        `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FxcIgFsDSwMFiTw=", 
+        `x-amzn-trace-id` = "Root=1-6476da36-6f66c4776fd4fe0f196217f3;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
     "list")), all_headers = list(list(status = 422L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:25:10 GMT", 
             `content-type` = "application/json", `content-length` = "176", 
-            `x-amzn-requestid` = "5f380260-8f5d-44da-8435-b1132a3ad633", 
-            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FJ9ktETkSwMFcuQ=", 
-            `x-amzn-trace-id` = "Root=1-64670fb7-0e081065431dbe33401f0f0a;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+            `x-amzn-requestid` = "a6354b92-4085-4546-82ec-a30208d228f6", 
+            `x-amzn-remapped-content-length` = "176", `x-amz-apigw-id` = "FxcIgFsDSwMFiTw=", 
+            `x-amzn-trace-id` = "Root=1-6476da36-6f66c4776fd4fe0f196217f3;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
[…]

### 2023-05-31 tests/api/Wrong-filters-pagedata/a/5c09bf93f315d/data-aa36ae.R

@@ -1,20 +1,20 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data?series_id=2687&from_date=1900-01-01&thru_date=1900-01-10", 
-    status_code = 500L, headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
+    status_code = 500L, headers = structure(list(date = "Wed, 31 May 2023 05:25:10 GMT", 
         `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-        `x-amzn-requestid` = "824b7281-c4e9-4173-a31d-ada3ef3e510c", 
-        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJ9kvHlzSwMF6zw=", 
-        `x-amzn-trace-id` = "Root=1-64670fb7-5daa8ec65c0afa4c66e243fa;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+        `x-amzn-requestid` = "83609a85-c4ac-4bb1-b08d-f6cc93c45d63", 
+        `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FxcIiHBWywMFusw=", 
+        `x-amzn-trace-id` = "Root=1-6476da36-669c39487fa240d75e0801bc;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
     "list")), all_headers = list(list(status = 500L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:25:10 GMT", 
             `content-type` = "text/plain; charset=utf-8", `content-length` = "21", 
-            `x-amzn-requestid` = "824b7281-c4e9-4173-a31d-ada3ef3e510c", 
-            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FJ9kvHlzSwMF6zw=", 
-            `x-amzn-trace-id` = "Root=1-64670fb7-5daa8ec65c0afa4c66e243fa;Sampled=0;lineage=31aaf29f:0"), class = c("insensitive", 
+            `x-amzn-requestid` = "83609a85-c4ac-4bb1-b08d-f6cc93c45d63", 
+            `x-amzn-remapped-content-length` = "21", `x-amz-apigw-id` = "FxcIiHBWywMFusw=", 
[…]

### 2023-05-31 tests/api/summary-requests-pagedata/a/5c09bf93f315d/data/summary-by-deployment.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data/summary-by-deployment", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
+    status_code = 403L, headers = structure(list(date = "Wed, 31 May 2023 05:25:10 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "bbdc7293-6804-4ddd-a699-b15ec7c5e6a9", 
+        `x-amzn-requestid` = "acaa711c-2e40-42ac-95bf-28b7cfb9346e", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJ9kyH44SwMFnAA="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FxcImEW6ywMFZvQ="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:25:10 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "bbdc7293-6804-4ddd-a699-b15ec7c5e6a9", 
+            `x-amzn-requestid` = "acaa711c-2e40-42ac-95bf-28b7cfb9346e", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJ9kyH44SwMFnAA="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FxcImEW6ywMFZvQ="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684475831, class = c("POSIXct", "POSIXt"
+    date = structure(1685510710, class = c("POSIXct", "POSIXt"
[…]

### 2023-05-31 tests/api/summary-requests-pagedata/a/5c09bf93f315d/data/summary-by-series.R

@@ -1,21 +1,21 @@
 structure(list(url = "https://api.aims.gov.au/data-v2.0/10.25845/5c09bf93f315d/data/summary-by-series", 
-    status_code = 403L, headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
+    status_code = 403L, headers = structure(list(date = "Wed, 31 May 2023 05:25:10 GMT", 
         `content-type` = "application/json", `content-length` = "42", 
-        `x-amzn-requestid` = "74c4b9ef-3d4b-4c39-9b9d-6a3490427a2e", 
+        `x-amzn-requestid` = "6a201ef7-e7ec-4a1b-ad98-a8cdc77772c1", 
         `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-        `x-amz-apigw-id` = "FJ9kxG-BywMF9sA="), class = c("insensitive", 
+        `x-amz-apigw-id` = "FxcIlEQoSwMFu0w="), class = c("insensitive", 
     "list")), all_headers = list(list(status = 403L, version = "HTTP/2", 
-        headers = structure(list(date = "Fri, 19 May 2023 05:57:11 GMT", 
+        headers = structure(list(date = "Wed, 31 May 2023 05:25:10 GMT", 
             `content-type` = "application/json", `content-length` = "42", 
-            `x-amzn-requestid` = "74c4b9ef-3d4b-4c39-9b9d-6a3490427a2e", 
+            `x-amzn-requestid` = "6a201ef7-e7ec-4a1b-ad98-a8cdc77772c1", 
             `x-amzn-errortype` = "MissingAuthenticationTokenException", 
-            `x-amz-apigw-id` = "FJ9kxG-BywMF9sA="), class = c("insensitive", 
+            `x-amz-apigw-id` = "FxcIlEQoSwMFu0w="), class = c("insensitive", 
         "list")))), cookies = structure(list(domain = logical(0), 
         flag = logical(0), path = logical(0), secure = logical(0), 
         expiration = structure(numeric(0), class = c("POSIXct", 
         "POSIXt")), name = logical(0), value = logical(0)), row.names = integer(0), class = "data.frame"), 
     content = charToRaw("{\"message\":\"Missing Authentication Token\"}"), 
-    date = structure(1684475831, class = c("POSIXct", "POSIXt"
-    ), tzone = "GMT"), times = c(redirect = 0, namelookup = 2.7e-05, 
[…]

### 2023-05-31 tests/testthat/test-page_data.R

@@ -23,7 +23,7 @@ with_mock_dir("Correct-structure-pagedata", {
     expect_is(wa$links, "list")
     expect_identical(names(wa$links), "next_page")
     expect_is(sa, "list")
-    expect_length(sa, 6) # soon will revert back to 5
+    expect_length(sa, 5)
     expect_true(all(c("cursor", "links") %in% names(sa)))
     expect_is(sa$links, "list")
     expect_identical(names(sa$links), "next_page")
@@ -35,7 +35,7 @@ with_mock_dir("Correct-structure-pagedata", {
       )
     )
     expect_is(sb, "list")
-    expect_length(sb, 6) # soon will revert back to 5
+    expect_length(sb, 5)
     expect_true(
       all(
         c("metadata", "citation", "links", "cursor", "data") %in% names(sb)
@@ -49,7 +49,7 @@ with_mock_dir("Correct-structure-pagedata", {
       )
     )
     expect_is(sa_n, "list")
-    expect_length(sa_n, 6) # soon will revert back to 5
+    expect_length(sa_n, 5)
     expect_true(
       all(
         c("metadata", "citation", "links", "cursor", "data") %in% names(sa_n)
